```latex
\documentclass[12pt]{article}

% ----------------------------------------------------------------------
% PREAMBLE
% ----------------------------------------------------------------------
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url}      % For URL formatting
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage[utf8]{inputenc}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% --- Document Metadata ---
\title{Cybersecurity Posture Assessment Report \\ \large For: Opal Sky Media}
\author{Cybersecurity Analyst}
\date{\today}

% ----------------------------------------------------------------------
% DOCUMENT BODY
% ----------------------------------------------------------------------
\begin{document}

\maketitle
\hrule
\vspace{1cm}

\tableofcontents

\newpage

% ----------------------------------------------------------------------
% SECTION 1: EXECUTIVE SUMMARY
% ----------------------------------------------------------------------
\section{Executive Summary}

This report provides a cybersecurity posture assessment for Opal Sky Media. The analysis is based on organizational data provided via a security questionnaire, a review of pre-existing risks, and a technical network scan.

The assessment reveals several critical and high-risk security gaps originating from organizational policies and controls. The complete absence of Multi-Factor Authentication (MFA) across email, workstations, and sensitive systems represents a critical vulnerability. This significantly increases the risk of unauthorized access and account compromise. Furthermore, the lack of a formal Acceptable Use Policy and a mandatory annual security awareness training program for all staff indicates deficiencies in security governance and culture.

\textbf{Important Note on Data Integrity:} The provided technical scan data (\texttt{Input\_1\_Network\_Scan\_JSON}) and the list of current risks (\texttt{Input\_3\_Current\_Risks\_JSON}) were found to be corrupted and unparsable. Consequently, this report's findings are primarily based on the security questionnaire. A comprehensive understanding of the technical attack surface and existing vulnerabilities is not possible without valid data.

Based on the available information, Opal Sky Media's current security posture is considered high-risk. Immediate remediation of the identified control gaps is strongly recommended. A new technical vulnerability scan is required to complete the assessment.

% ----------------------------------------------------------------------
% SECTION 2: ORGANIZATIONAL INFORMATION
% ----------------------------------------------------------------------
\section{Organizational Information}

The following details were provided for the assessment:

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & Opal Sky Media \\
Email Domain & \seqsplit{\texttt{OpalSkyMedia.net}} \\
Website Domain & \url{www.OpalSkyMedia.net} \\
Primary External IP & \seqsplit{\texttt{124.72.75.55}} \\
\bottomrule
\end{tabular}

% ----------------------------------------------------------------------
% SECTION 3: SECURITY CONTROL REVIEW
% ----------------------------------------------------------------------
\section{Security Control Review (Questionnaire Analysis)}

The following table summarizes the responses from the security questionnaire. Each "No" response indicates a potential security gap that requires attention.

\begin{table}[h!]
\centering
\caption{Security Questionnaire Results}
\begin{tabular}{@{}p{8cm} c p{4cm}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \ding{55} & \textbf{Critical Gap.} Email is a primary target for phishing and account takeover. \\
\addlinespace
Do you require MFA to log into computers? & \ding{55} & \textbf{Critical Gap.} Lack of MFA on endpoints exposes the internal network. \\
\addlinespace
Do you require MFA to access sensitive data systems? & \ding{55} & \textbf{Critical Gap.} Failure to protect sensitive data with MFA is a severe risk. \\
\addlinespace
Does your organization have an employee acceptable use policy? & \ding{55} & \textbf{High Risk.} Without a policy, there are no clear rules for technology use, increasing insider risk. \\
\addlinespace
Does your organization do security awareness training for new employees? & \ding{51} & Foundational control is in place. \\
\addlinespace
Does your organization do security awareness training for all employees at least once per year? & \ding{55} & \textbf{High Risk.} Security knowledge degrades over time; ongoing training is essential. \\
\bottomrule
\end{tabular}
\end{table}

% ----------------------------------------------------------------------
% SECTION 4: TECHNICAL SCAN RESULTS
% ----------------------------------------------------------------------
\section{Technical Scan Results}

A technical network scan was intended to be performed against the organization's external infrastructure to identify open ports, running services, and potential vulnerabilities.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{[Target IP]}
    \item \textbf{Scan Date:} Not Available
    \item \textbf{Scan Status:} \textbf{Failed - Corrupted Data}
\end{itemize}

The data file provided for the network scan (\texttt{Input\_1\_Network\_Scan\_JSON}) was corrupted and could not be parsed. Therefore, no analysis of the external attack surface, including open ports, services, or software versions, could be conducted.

\textbf{A new external vulnerability scan is required to assess the technical security posture.}

% ----------------------------------------------------------------------
% SECTION 5: CURRENT RISK ASSESSMENT
% ----------------------------------------------------------------------
\section{Current Risk Assessment}

This section summarizes the key risks identified during this assessment. The input file containing pre-existing known risks (\texttt{Input\_3\_Current\_Risks\_JSON}) was also found to be corrupted. The risks below are derived solely from the Security Control Review.

\begin{table}[h!]
\centering
\caption{Identified Risks Summary}
\begin{tabular}{@{}lp{8cm}l@{}}
\toprule
\textbf{Risk ID} & \textbf{Description} & \textbf{Severity} \\
\midrule
RISK-001 & \textbf{Systemic Lack of Multi-Factor Authentication (MFA):} No MFA is enforced for email, endpoints, or sensitive data systems, creating a high probability of account compromise. & \textbf{Critical} \\
\addlinespace
RISK-002 & \textbf{Absence of Acceptable Use Policy (AUP):} Lack of a formal AUP leads to inconsistent security practices and a weakened ability to enforce security standards among employees. & \textbf{High} \\
\addlinespace
RISK-003 & \textbf{Incomplete Security Awareness Training Program:} While new hires receive training, the absence of an annual refresher for all staff allows security knowledge to become outdated, increasing susceptibility to social engineering. & \textbf{High} \\
\addlinespace
RISK-004 & \textbf{Lack of Technical Vulnerability Insight:} Due to corrupted scan data, there is zero visibility into the external technical attack surface, which may harbor critical vulnerabilities. & \textbf{Unknown} \\
\bottomrule
\end{tabular}
\end{table}

% ----------------------------------------------------------------------
% SECTION 6: RECOMMENDATIONS
% ----------------------------------------------------------------------
\section{Recommendations}

The following prioritized actions are recommended to mitigate the identified risks and improve the overall security posture of Opal Sky Media.

\begin{enumerate}
    \item \textbf{[Critical] Implement Multi-Factor Authentication (MFA) Immediately:}
    \begin{itemize}
        \item \textbf{Priority 1a:} Enforce MFA on all email accounts (e.g., Office 365, Google Workspace).
        \item \textbf{Priority 1b:} Enforce MFA for all remote access solutions (e.g., VPN) and access to sensitive data systems.
        \item \textbf{Priority 1c:} Deploy MFA for all workstation and server logins.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[High] Develop and Implement an Acceptable Use Policy (AUP):}
    \begin{itemize}
        \item Draft a formal AUP that clearly defines the rules for using company technology, data, and internet resources.
        \item Require all employees to read and acknowledge the policy upon hire and annually thereafter.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[High] Establish a Mandatory Annual Security Awareness Program:}
    \begin{itemize}
        \item Implement a formal, mandatory security awareness training program for all employees, to be completed at least once per year.
        \item The training should cover modern threats such as phishing, ransomware, and social engineering.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[Informational] Conduct a New Network Vulnerability Scan:}
    \begin{itemize}
        \item Commission a new, authenticated and unauthenticated, external vulnerability scan to replace the corrupted data set.
        \item This is essential for identifying and remediating technical vulnerabilities on internet-facing systems.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[Informational] Re-compile List of Known Risks:}
    \begin{itemize}
        \item The organization should provide a valid and complete list of its currently tracked risks to ensure they can be incorporated into a holistic security strategy.
    \end{itemize}
\end{enumerate}

\end{document}
```