```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and references
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % To split long strings in tt font
\usepackage{xcolor} % For colors
\usepackage{graphicx} % For images (e.g., logo)
\usepackage{datetime} % For formatting dates

% --- Document Metadata ---
\title{Cybersecurity Assessment Report \\ \large Prepared for Solaris Energy}
\author{Cybersecurity Analysis Division}
\date{\today}

% --- Hyperref Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report for Solaris Energy},
    pdfpagemode=FullScreen,
}

% --- Custom Commands ---
\newcommand{\yes}{\ding{51}}
\newcommand{\no}{\ding{55}}
\newcommand{\orgname}{\textbf{Solaris Energy}}
\newcommand{\orgdomain}{\texttt{SolarisEnergy.net}}
\newcommand{\orgip}{\texttt{25.225.250.45}}
\newcommand{\targetip}{\texttt{172.16.50.20}}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% ==============================================================================
% 1. EXECUTIVE SUMMARY
% ==============================================================================
\section{Executive Summary}

This report presents a cybersecurity assessment for \orgname, conducted on \today. The analysis combines a technical network scan, a review of organizational security controls, and an evaluation of pre-existing risks.

Our analysis identified several high-risk vulnerabilities that require immediate attention. The most critical findings include:

\begin{itemize}
    \item \textbf{Exposed and Outdated Database:} A MySQL database server on host \targetip{} is publicly accessible on port 3306. The running version, MySQL 5.7.33, is End-of-Life (EOL) as of October 2023 and no longer receives security patches, exposing it to numerous known exploits.
    \item \textbf{Insufficient Multi-Factor Authentication (MFA):} MFA is not enforced for accessing critical assets, including employee email and sensitive data systems. This significantly increases the risk of account compromise and subsequent data breaches through phishing or credential theft.
\end{itemize}

While the organization has implemented foundational security practices like employee security training and an acceptable use policy, the identified gaps in technical and access controls create a significant attack surface. We strongly recommend prioritizing the remediation actions outlined in Section \ref{sec:recommendations} to mitigate these risks and improve the overall security posture.

% ==============================================================================
% 2. ORGANIZATIONAL INFORMATION
% ==============================================================================
\section{Organizational Information}

The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \orgname \\
    Email Domain & \orgdomain \\
    Website Domain & \texttt{www.SolarisEnergy.net} \\
    Known External IP & \orgip \\
    \bottomrule
\end{tabular}

% ==============================================================================
% 3. SECURITY CONTROL REVIEW
% ==============================================================================
\section{Security Control Review}

This section evaluates the organization's security posture based on a questionnaire. "No" answers indicate potential gaps in security controls that can increase risk.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\begin{tabular}{@{}p{0.6\linewidth}cp{0.25\linewidth}@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} & \textbf{Analyst Notes} \\
    \midrule
    Do you require MFA to access email? & \textcolor{red}{\no} & \textbf{Critical Gap.} Email is a primary target for attackers. Lack of MFA increases the risk of business email compromise (BEC) and phishing attacks. \\
    \addlinespace
    Do you require MFA to log into computers? & \textcolor{green}{\yes} & Good practice for endpoint security. \\
    \addlinespace
    Do you require MFA to access sensitive data systems? & \textcolor{red}{\no} & \textbf{High Risk.} Direct access to sensitive data without a secondary authentication factor is a significant security weakness. \\
    \addlinespace
    Does your organization have an employee acceptable use policy? & \textcolor{green}{\yes} & Foundational policy for setting security expectations. \\
    \addlinespace
    Does your organization do security awareness training for new employees? & \textcolor{green}{\yes} & Excellent for establishing a security-conscious culture from the start. \\
    \addlinespace
    Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\yes} & Essential for maintaining security awareness. \\
    \bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% 4. TECHNICAL SCAN RESULTS
% ==============================================================================
\section{Technical Scan Results}

A network scan was performed on the specified target to identify open ports and running services.

\begin{itemize}
    \item \textbf{Target IP Address:} \targetip
    \item \textbf{Scan Date:} \today
\end{itemize}

\begin{table}[h!]
\centering
\caption{Open Ports and Services on \targetip}
\begin{tabular}{@{}llllll@{}}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} & \textbf{Analyst Notes} \\
    \midrule
    3306/tcp & Open & mysql & MySQL & 5.7.33 & \textbf{Critical Finding.} This version is End-of-Life (EOL) and no longer supported. Exposing a database directly to the network is highly discouraged. \\
    \bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% 5. RISK ASSESSMENT SUMMARY
% ==============================================================================
\section{Risk Assessment Summary}

The following table synthesizes findings from the technical scan, control review, and pre-existing risk data into a prioritized list.

\begin{table}[h!]
\centering
\caption{Aggregated Risk Summary}
\begin{tabular}{@{}p{0.1\linewidth}p{0.25\linewidth}p{0.1\linewidth}p{0.45\linewidth}@{}}
    \toprule
    \textbf{Risk ID} & \textbf{Risk Name} & \textbf{Severity} & \textbf{Description} \\
    \midrule
    RISK-001 & Exposed \& Outdated Database Software & \textbf{Critical} & MySQL v5.7.33 is EOL and exposed on port 3306. This allows attackers to exploit known, unpatched vulnerabilities to gain access to the database. \\
    \addlinespace
    RISK-002 & Insufficient MFA for Email Access & \textbf{High} & The lack of MFA on email accounts makes them vulnerable to takeover via credential stuffing or phishing, leading to data exfiltration or further internal attacks. \\
    \addlinespace
    RISK-003 & Insufficient MFA for Sensitive Systems & \textbf{High} & Sensitive data systems can be accessed with only a password, creating a single point of failure for protecting the organization's most valuable data. \\
    \addlinespace
    RISK-004 & Public Database Exposure & \textbf{High} & The MySQL port (3306) is open to a wide network, inviting brute-force attacks and unauthorized connection attempts, confirming a previously identified risk. \\
    \bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% 6. RECOMMENDATIONS
% ==============================================================================
\section{Recommendations}
\label{sec:recommendations}

The following actions are recommended to mitigate the identified risks. Recommendations are prioritized based on severity and potential impact.

\subsection{RISK-001: Exposed \& Outdated Database Software}
\begin{itemize}
    \item \textbf{Immediate Action:} Implement strict firewall rules to restrict all access to port 3306 on \targetip. Access should only be permitted from specific, trusted application server IP addresses.
    \item \textbf{Short-Term (1-3 Months):} Plan and execute an upgrade of the MySQL database from the EOL version 5.7 to a currently supported version (e.g., MySQL 8.x). This is critical for receiving security patches.
    \item \textbf{Long-Term Strategy:} Re-architect the network so that the database resides in a private, non-internet-facing subnet. Access should be managed through a secure bastion host or VPN.
\end{itemize}

\subsection{RISK-002 \& RISK-003: Insufficient MFA}
\begin{itemize}
    \item \textbf{Immediate Action:} Enable and enforce MFA for all user accounts on the organization's email platform (e.g., Microsoft 365, Google Workspace).
    \item \textbf{Short-Term (1-3 Months):} Conduct an inventory of all systems containing sensitive data. Implement and enforce MFA for access to these systems for all users, including administrators.
    \item \textbf{Long-Term Strategy:} Develop and enforce a comprehensive Identity and Access Management (IAM) policy that mandates MFA as a default for all systems and applications.
\end{itemize}

\end{document}
```