```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long monospaced text
\usepackage{graphicx} % For potential logos/images
\usepackage{xcolor} % For colors

% Document Information
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analyst}
\date{\today}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}
This report provides a cybersecurity posture assessment for \textbf{Aventine Research}, based on a review of organizational security controls, an external network scan, and an analysis of current risks. The assessment was conducted to identify key vulnerabilities and provide actionable recommendations to enhance the organization's security.

The analysis revealed several critical and high-risk security gaps that require immediate attention. The most significant findings include:
\begin{itemize}
    \item \textbf{Critical - Widespread Lack of Multi-Factor Authentication (MFA):} The organization does not enforce MFA for accessing email, computers, or sensitive data systems. This represents a critical vulnerability, as compromised credentials could lead to a significant data breach with minimal effort from an attacker.
    \item \textbf{High - Insecure Web Service Configuration:} The network scan identified a web server operating over unencrypted HTTP (Port 80). This exposes all transmitted data, including potential credentials or sensitive information, to interception and eavesdropping.
    \item \textbf{High - Missing Governance Policy:} The organization lacks a formal employee Acceptable Use Policy (AUP). This absence of documented rules creates ambiguity and increases the risk of insider threats, whether malicious or accidental.
\end{itemize}

Immediate remediation of these issues is strongly recommended to reduce the organization's attack surface and mitigate the risk of a security incident. Detailed findings and corrective actions are outlined in the subsequent sections of this report.

% --- 2. Organizational Information ---
\section{Organizational Information}
The following information was provided for the assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & \textbf{Aventine Research} \\
Email Domain & \seqsplit{\texttt{AventineResearch.net}} \\
Website Domain & \seqsplit{\url{www.AventineResearch.net}} \\
External IP Address & \seqsplit{\texttt{141.143.247.100}} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details}
\end{table}

% --- 3. Security Control Review ---
\section{Security Control Review}
A review of self-reported security controls was conducted via a questionnaire. The results highlight significant gaps in access control and governance policies. A summary of the responses is provided in Table \ref{tab:controls}.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Results}
\label{tab:controls}
\begin{tabular}{@{}lc@{}}
\toprule
\textbf{Control Question} & \textbf{Status} \\ \midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{55} \\
Do you require MFA to access sensitive data systems? & \ding{55} \\
Does your organization have an employee acceptable use policy? & \ding{55} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
Does your organization do security awareness training for all employees annually? & \ding{51} \\ \bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The lack of MFA for email, computer logins, and sensitive systems is a critical weakness. While security awareness training is in place, it is not a substitute for technical enforcement controls. The absence of an Acceptable Use Policy further weakens the organization's security governance.

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}
A network scan was performed on the target IP address \texttt{172.16.0.1} to identify open ports and exposed services.

\subsection*{Scan Details}
\begin{itemize}
    \item \textbf{Target IP:} \texttt{172.16.0.1}
    \item \textbf{Host Status:} Up
\end{itemize}

\subsection*{Open Ports}
The scan identified the following open port.

\begin{table}[h!]
\centering
\caption{Open Ports Detected on \texttt{172.16.0.1}}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service (Common)} & \textbf{Finding} \\ \midrule
80/tcp & Open & HTTP & \textbf{High Risk} - Unencrypted Web Traffic \\ \bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The presence of an open port 80 (HTTP) indicates that a web server is running and is not enforcing encrypted connections. Any data sent to or from this server, including login credentials or user data, is transmitted in cleartext. This makes the communication vulnerable to man-in-the-middle (MitM) attacks, where an attacker can intercept, read, and modify the traffic.

% --- 5. Risk Assessment Summary ---
\section{Risk Assessment Summary}
The following table synthesizes findings from the security control review and the technical scan into a prioritized list of risks.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{@{}p{0.3\linewidth}p{0.15\linewidth}p{0.45\linewidth}@{}}
\toprule
\textbf{Risk Name} & \textbf{Severity} & \textbf{Overview} \\ \midrule
\textbf{Lack of Multi-Factor Authentication (MFA)} & \textbf{Critical} & The absence of MFA on critical systems allows an attacker with valid credentials (e.g., from a phishing attack) to gain unauthorized access to email, endpoints, and sensitive data. \\
\addlinespace
\textbf{Unencrypted Web Communication} & \textbf{High} & The web server at \texttt{172.16.0.1} uses HTTP, exposing all data to interception. This could lead to credential theft and data leakage. \\
\addlinespace
\textbf{Missing Acceptable Use Policy (AUP)} & \textbf{High} & Without a formal AUP, there are no clear rules for employees regarding the use of company systems, increasing the likelihood of unintentional data exposure or system misuse. \\ \bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
Based on the identified risks, the following actions are recommended to improve the security posture of \textbf{Aventine Research}.

\subsection*{Immediate Actions (Critical Priority)}
\begin{enumerate}
    \item \textbf{Implement MFA Across All Critical Systems:}
    \begin{itemize}
        \item Enforce MFA for email access (e.g., via Office 365 or Google Workspace policies).
        \item Require MFA for all remote access solutions (e.g., VPN).
        \item Deploy MFA for logging into company computers and accessing all systems that store or process sensitive data.
    \end{itemize}
\end{enumerate}

\subsection*{High Priority Actions}
\begin{enumerate}
    \setcounter{enumi}{1}
    \item \textbf{Secure Web Server Communication:}
    \begin{itemize}
        \item Obtain and install a TLS/SSL certificate for the web server at \texttt{172.16.0.1}.
        \item Reconfigure the web server to enforce HTTPS (Port 443) for all connections.
        \item Implement a redirect from HTTP to HTTPS to ensure all users are on an encrypted channel.
    \end{itemize}
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP):}
    \begin{itemize}
        \item Draft a formal AUP that defines the rules for using company IT assets, data handling, and internet usage.
        \item Communicate the policy to all employees and require them to formally acknowledge it.
        \item Integrate the AUP into the existing security awareness training program.
    \end{itemize}
\end{enumerate}

\subsection*{Further Steps}
\begin{enumerate}
    \setcounter{enumi}{3}
    \item \textbf{Conduct Comprehensive Vulnerability Scanning:} Perform an in-depth, credentialed vulnerability scan of internal and external assets to identify specific software vulnerabilities, misconfigurations, and missing patches that were not visible in the initial network scan.
\end{enumerate}

\end{document}
```