```latex
\documentclass[12pt]{article}

% Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont}                 % For symbols like checkmarks (\ding{51}) and crosses (\ding{55})
\usepackage{booktabs}               % For professional-looking tables (\toprule, \midrule, \bottomrule)
\usepackage[hidelinks]{hyperref}    % For clickable links without boxes
\usepackage{url}                    % For formatting URLs
\usepackage{seqsplit}               % To split long strings without breaking words
\usepackage{xcolor}                 % For colored text

% Custom Commands for Report
\newcommand{\yes}{\ding{51}}
\newcommand{\no}{\ding{55}}
\newcommand{\riskhigh}[1]{\textcolor{red}{\textbf{#1}}}
\newcommand{\riskmedium}[1]{\textcolor{orange}{\textbf{#1}}}
\newcommand{\risklow}[1]{\textcolor{blue}{\textbf{#1}}}
\newcommand{\riskinformational}[1]{\textcolor{gray}{\textbf{#1}}}
\newcommand{\riskremediated}[1]{\textcolor{green}{\textbf{#1}}}

% Document Metadata
\title{Cybersecurity Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage
\tableofcontents
\newpage

\section{Executive Summary}
This report summarizes the cybersecurity posture of \textbf{Grizzly Peak}. The assessment combines a review of organizational security controls, a technical network scan, and an analysis of pre-existing risks.

While the technical scan of the target host \texttt{192.168.0.5} revealed a strong posture with no open ports, significant gaps were identified in organizational security controls. Critical deficiencies include the lack of multi-factor authentication (MFA) for email and sensitive data systems, and the absence of an employee acceptable use policy. These gaps present a high risk of account compromise and unauthorized data access.

The previously identified risk of an "Unencrypted Web Server" on port 80 appears to have been remediated, as our scan found the port to be closed. Immediate action is recommended to implement MFA across all critical systems and to develop foundational security policies to strengthen the organization's overall security posture.

\section{Organizational Information}
The following information was provided for the assessment.

\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & Grizzly Peak \\
Email Domain & \texttt{GrizzlyPeak.net} \\
Website Domain & \url{www.GrizzlyPeak.net} \\
External IP Address & \texttt{107.176.41.69} \\
\bottomrule
\end{tabular}
\end{center}

\section{Security Control Review}
This section evaluates the organization's security posture based on a standardized questionnaire. Responses marked with \no\ indicate a deviation from security best practices and represent a potential risk.

\begin{center}
\begin{tabular}{@{}p{0.6\linewidth}cc@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \no & \riskhigh{High Risk} \\
Do you require MFA to log into computers? & \yes & Good Practice \\
Do you require MFA to access sensitive data systems? & \no & \riskhigh{High Risk} \\
Does your organization have an employee acceptable use policy? & \no & \riskmedium{Critical Gap} \\
Does your organization do security awareness training for new employees? & \yes & Good Practice \\
Does your organization do security awareness training for all employees at least once per year? & \yes & Good Practice \\
\bottomrule
\end{tabular}
\end{center}

\section{Technical Scan Results}
A network scan was performed to identify open ports and services on the specified target system.

\subsection{Scan Summary}
\begin{itemize}
    \item \textbf{Target IP:} \texttt{192.168.0.5}
    \item \textbf{Status:} Host is Up
    \item \textbf{Findings:} No open ports were discovered on the target system. This indicates a strong network perimeter for this specific host.
\end{itemize}

\subsection{Detailed Port Information}
The scan confirmed that all probed ports were in a 'closed' state. This is a positive security finding.
\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} \\
\midrule
80/tcp & closed & http \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Risk Correlation Note}
The pre-existing risk list (Input 3) indicated that port 80 was open. This scan shows the port is now closed. This suggests that the previously identified risk, "Unencrypted Web Server," has been successfully remediated. This should be verified and the risk formally closed in the organization's risk register.

\section{Consolidated Risk Assessment}
The following table summarizes the identified risks, combining organizational gaps, technical findings, and pre-existing data.

\begin{center}
\begin{tabular}{@{}p{0.3\linewidth}p{0.5\linewidth}l@{}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{No MFA for Email Access} & The lack of MFA on email accounts significantly increases the risk of business email compromise (BEC), phishing success, and subsequent data breaches. & \riskhigh{High} \\
\addlinespace
\textbf{No MFA for Sensitive Systems} & Sensitive data systems without MFA are vulnerable to unauthorized access via compromised credentials, posing a direct threat to confidential information. & \riskhigh{High} \\
\addlinespace
\textbf{Missing Acceptable Use Policy} & Without a formal policy, there are no clear guidelines for employees on the acceptable use of company assets, increasing the risk of insider threat and misuse. & \riskmedium{Medium} \\
\addlinespace
Unencrypted Web Server & A pre-existing risk noted that port 80 was open. Our scan found this port to be closed. & \riskremediated{Remediated} \\
\bottomrule
\end{tabular}
\end{center}

\section{Recommendations}
Based on the assessment, we provide the following prioritized recommendations to mitigate the identified risks.

\begin{enumerate}
    \item \textbf{Implement MFA for Email (Priority: Critical):} Immediately enforce MFA for all user access to the \texttt{GrizzlyPeak.net} email system. This is the single most effective control to prevent business email compromise and unauthorized account access.
    
    \item \textbf{Implement MFA for Sensitive Data Systems (Priority: Critical):} Deploy MFA on all systems identified as containing sensitive or critical business data. This should be prioritized based on data sensitivity and regulatory requirements.
    
    \item \textbf{Develop and Implement an Acceptable Use Policy (Priority: High):} Create a formal Acceptable Use Policy (AUP) that outlines the rules and responsibilities for all employees when using company IT assets. Ensure all employees read and acknowledge the policy as part of their onboarding and annual training.
    
    \item \textbf{Validate and Close Old Risks (Priority: Low):} Formally confirm that the "Unencrypted Web Server" risk associated with port 80 is fully resolved and update the internal risk register to reflect its closed status. This ensures accurate tracking of the current security posture.
\end{enumerate}

\end{document}
```