```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and ToC
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % To split long strings without breaking
\usepackage{xcolor} % For custom colors
\usepackage{graphicx} % For potential logos or diagrams
\usepackage{fancyhdr} % For headers and footers

% --- Document Setup ---

% Hyperref settings
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfauthor={Cybersecurity Analyst},
    pdfsubject={Security Analysis},
    pdfkeywords={Security, Report, Analysis},
    bookmarks=true
}

% Define colors for severity ratings
\definecolor{criticalred}{HTML}{D7263D}
\definecolor{highorange}{HTML}{F49D40}
\definecolor{mediumyellow}{HTML}{F4D440}
\definecolor{lowblue}{HTML}{40A8F4}

% Define a command for severity labels
\newcommand{\severity}[2]{\colorbox{#1}{\textcolor{white}{\textbf{\sffamily\small #2}}}}

% Header and Footer
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Cybersecurity Assessment Report}
\fancyhead[R]{Atlas Mapping}
\fancyfoot[C]{\thepage}

% --- Document Start ---

\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge{\textbf{Cybersecurity Assessment Report}}
    \vspace{0.5cm}
    \Large{Prepared for: \textbf{Atlas Mapping}}
    \vspace{1.5cm}
    \rule{\linewidth}{0.5mm}
    \vspace{0.5cm}
    \begin{minipage}{0.4\textwidth}
        \begin{flushleft} \large
            \emph{Author:}\\
            Cybersecurity Analyst
        \end{flushleft}
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
        \begin{flushright} \large
            \emph{Date:}\\
            \today
        \end{flushright}
    \end{minipage}
    \vfill
    \begin{center}
        \large
        \textbf{CONFIDENTIAL}
        \vspace{0.5cm}
        
        This document contains sensitive information. Access, distribution, and use are restricted to authorized personnel only.
    \end{center}
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report details the findings of a cybersecurity assessment conducted for \textbf{Atlas Mapping}. The evaluation combined a review of organizational security controls, an automated network scan of key infrastructure, and an analysis of pre-existing risk documentation.

The assessment identified several high-priority risks that require immediate attention. Key findings include:
\begin{itemize}
    \item \textbf{Critical Gaps in Access Control:} Multi-Factor Authentication (MFA) is not enforced for employee email or computer access. This represents a significant vulnerability, as compromised credentials could lead to widespread system access and data breaches.
    \item \textbf{Exposed and Outdated Database:} A MySQL database server on the internal network (\texttt{172.16.50.20}) is directly accessible via port 3306. Furthermore, the database is running MySQL version 5.7.33, which reached its official End-of-Life (EOL) in October 2023 and no longer receives security updates. This exposes the organization to numerous known vulnerabilities.
    \item \textbf{Positive Security Practices:} The organization has established an acceptable use policy and conducts regular security awareness training, which are commendable foundational controls.
\end{itemize}

Immediate remediation should focus on implementing MFA across all critical systems and securing the exposed database by applying network access controls and planning an urgent software upgrade.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment. This information establishes the context and scope of the review.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Atlas Mapping} \\
Email Domain & \texttt{AtlasMapping.com} \\
Website Domain & \url{www.AtlasMapping.com} \\
External IP Address & \texttt{103.70.139.3} \\
\bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A questionnaire was completed to evaluate the current state of administrative and technical security controls. The results are summarized below. "No" answers indicate significant gaps in the organization's security posture.

\begin{tabular}{@{}p{0.6\linewidth} c p{0.25\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Status} & \textbf{Analyst Note} \\
\midrule
Do you require MFA to access email? & \ding{55} & \severity{criticalred}{Critical Gap} \\
Do you require MFA to log into computers? & \ding{55} & \severity{highorange}{High Risk} \\
Do you require MFA to access sensitive data systems? & \ding{51} & Good Practice \\
Does your organization have an employee acceptable use policy? & \ding{51} & Good Practice \\
Does your organization do security awareness training for new employees? & \ding{51} & Good Practice \\
Does your organization do security awareness training for all employees at least once per year? & \ding{51} & Good Practice \\
\bottomrule
\end{tabular}

\vspace{1em}
\noindent \textbf{Note:} \ding{51} indicates "Yes" (control in place). \ding{55} indicates "No" (control is missing).

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An Nmap scan was performed on the specified target to identify open ports and running services.

\subsection{Target: \texttt{172.16.50.20}}
The scan revealed one open port on the target host.

\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & Open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}

\vspace{1em}
\noindent\textbf{Critical Finding:} The detected MySQL version, \textbf{5.7.33}, is an End-of-Life (EOL) product. It no longer receives security patches from the vendor, making it highly susceptible to exploitation from publicly known vulnerabilities. The open port allows direct network access to this vulnerable service.

% --- Section 5: Risk Assessment ---
\section{Risk Assessment}
The following table synthesizes findings from the security control review, technical scan, and pre-existing risk documentation into a prioritized list.

\begin{tabular}{@{}lp{0.3\linewidth}p{0.15\linewidth}p{0.4\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Name} & \textbf{Severity} & \textbf{Description} \\
\midrule
R-01 & End-of-Life Database Software & \severity{criticalred}{Critical} & The MySQL server is running version 5.7.33, which is unsupported and has known vulnerabilities. \\
\addlinespace
R-02 & Lack of MFA for Email Access & \severity{criticalred}{Critical} & Absence of MFA on email accounts greatly increases the risk of account takeover via phishing or credential stuffing. \\
\addlinespace
R-03 & Publicly Exposed Database Service & \severity{highorange}{High} & MySQL port 3306 is open to the network, exposing it to unauthorized access attempts and exploits. This finding confirms a previously identified risk. \\
\addlinespace
R-04 & Lack of MFA for Endpoint Access & \severity{highorange}{High} & The absence of MFA on computer logins allows an attacker with valid credentials to gain direct access to an endpoint and the network. \\
\bottomrule
\end{tabular}

% --- Section 6: Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks. Recommendations are prioritized based on severity.

\subsection{R-01: Remediate End-of-Life Database Software (Critical)}
The use of unsupported software is a critical risk. An attacker can exploit known vulnerabilities to compromise the database, leading to data theft, modification, or destruction.
\begin{itemize}
    \item \textbf{Immediate Action:} Develop a migration plan to upgrade the MySQL database from version 5.7 to a currently supported version (e.g., MySQL 8.x).
    \item \textbf{Long-Term Strategy:} Implement a formal patch and vulnerability management program to ensure all software and systems are kept up-to-date.
\end{itemize}

\subsection{R-02: Implement MFA for Email Access (Critical)}
Email is a primary target for attackers. Securing it is paramount.
\begin{itemize}
    \item \textbf{Immediate Action:} Enforce mandatory MFA for all user accounts on the \texttt{AtlasMapping.com} email system.
    \item \textbf{Supporting Action:} Conduct a follow-up awareness campaign to ensure all employees understand how to use the new MFA system.
\end{itemize}

\subsection{R-03: Secure Exposed Database Service (High)}
Direct access to a database from the general network is a severe security flaw.
\begin{itemize}
    \item \textbf{Immediate Action (Easy Fix):} Implement strict firewall rules to ensure that only authorized application servers and administrative hosts can connect to port 3306 on \texttt{172.16.50.20}. All other traffic should be denied.
    \item \textbf{Long-Term Strategy (Best Practice):} Require all database administration to be performed over a secure, authenticated channel, such as a Virtual Private Network (VPN) with MFA.
\end{itemize}

\subsection{R-04: Implement MFA for Endpoint Access (High)}
Endpoints are the gateway to the corporate network.
\begin{itemize}
    \item \textbf{Immediate Action:} Deploy an MFA solution for all Windows, macOS, and Linux computer logins, prioritizing users with access to sensitive data.
\end{itemize}

\end{document}
```