```latex
\documentclass[12pt]{article}

% --- PACKAGE IMPORTS ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url}      % For URL formatting
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{graphicx} % For logo (placeholder)
\usepackage{fancyhdr} % For headers and footers

% --- DOCUMENT METADATA ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment},
    pdfauthor={Cybersecurity Analyst},
    pdfkeywords={Security, Assessment, Report},
}

% --- HEADER & FOOTER ---
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyhead[L]{Cybersecurity Posture Assessment}
\fancyhead[R]{Midnight Oil Studios}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- HELPER COMMANDS ---
\newcommand{\yes}{\ding{51}}
\newcommand{\no}{\ding{55}}

% --- DOCUMENT START ---
\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    \Huge
    \textbf{Cybersecurity Posture Assessment Report}
    
    \vspace{1.5cm}
    
    \Large
    Prepared for: \\
    \vspace{0.5cm}
    \textbf{Midnight Oil Studios}
    
    \vspace{2cm}
    
    \large
    \textbf{Date of Report:} \today \\
    \textbf{Author:} Cybersecurity Analyst
    
    \vfill
    
    \normalsize
    \textit{This report is confidential and intended solely for the use of Midnight Oil Studios. It contains a summary of findings based on data provided and limited-scope technical scanning.}
    
\end{titlepage}

\tableofcontents
\newpage

% --- SECTION 1: EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report details the findings of a cybersecurity posture assessment for \textbf{Midnight Oil Studios}. The analysis is based on a review of organizational security controls via a questionnaire, a network scan of a designated target, and a review of pre-existing risk data.

The assessment identified several critical and high-risk security gaps that require immediate attention. Key findings include:
\begin{itemize}
    \item \textbf{Critical Gap in Access Control:} Multi-Factor Authentication (MFA) is not enforced for accessing sensitive data systems. This significantly increases the risk of unauthorized access and data breach.
    \item \textbf{High Risk from Inadequate Training:} The organization does not conduct mandatory annual security awareness training for all employees. This leaves the organization vulnerable to social engineering and phishing attacks.
    \item \textbf{High Risk from Insecure Service:} The network scan revealed an open port 80 (HTTP) on the target host \texttt{172.16.0.1}. This service transmits data in cleartext, exposing it to interception and manipulation.
\end{itemize}

These findings, when correlated, indicate a security posture that could be exploited by threat actors. This report provides specific, actionable recommendations to mitigate these risks and strengthen the overall security of the organization.

% --- SECTION 2: ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following details were provided for the assessment.
\begin{itemize}
    \item \textbf{Organization Name:} Midnight Oil Studios
    \item \textbf{Primary Email Domain:} \seqsplit{\texttt{MidnightOilStudios.net}}
    \item \textbf{External IP Address:} \texttt{60.159.122.50}
\end{itemize}

% --- SECTION 3: SECURITY CONTROL REVIEW ---
\section{Security Control Review}
A review of the organization's security controls was conducted based on a standardized questionnaire. The responses indicate a solid foundation in some areas but reveal critical gaps in others.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\label{tab:controls}
\begin{tabular}{p{8cm} c p{4cm}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \yes & Meets best practice. \\
\addlinespace
Do you require MFA to log into computers? & \yes & Meets best practice. \\
\addlinespace
Do you require MFA to access sensitive data systems? & \no & \textbf{Critical Gap Identified.} \\
\addlinespace
Does your organization have an employee acceptable use policy? & \yes & Meets best practice. \\
\addlinespace
Does your organization do security awareness training for new employees? & \yes & Good baseline practice. \\
\addlinespace
Does your organization do security awareness training for all employees at least once per year? & \no & \textbf{High-Risk Gap Identified.} \\
\bottomrule
\end{tabular}
\end{table}

% --- SECTION 4: TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
A network scan was performed on the specified target to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.0.1}
    \item \textbf{Target Status:} Up
\end{itemize}

The following table details the open ports discovered during the scan.

\begin{table}[h!]
\centering
\caption{Open Port Analysis}
\label{tab:ports}
\begin{tabular}{c c l p{7cm}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Finding / Analysis} \\
\midrule
80/tcp & Open & HTTP & The presence of an open HTTP port is a significant finding. This protocol is unencrypted, meaning any data transmitted (including potential credentials or sensitive information) can be intercepted. Standard practice is to use HTTPS (port 443) for all web traffic. \\
\bottomrule
\end{tabular}
\end{table}

% --- SECTION 5: RISK ASSESSMENT SUMMARY ---
\section{Risk Assessment Summary}
This section correlates the findings from the security control review and the technical scan to provide a consolidated view of the primary risks facing the organization. The provided list of current risks was reviewed and found to contain no actionable intelligence for this report.

\begin{table}[h!]
\centering
\caption{Consolidated Risk Register}
\label{tab:risks}
\begin{tabular}{p{2cm} p{6cm} p{3cm} c}
\toprule
\textbf{Risk ID} & \textbf{Description} & \textbf{Source} & \textbf{Severity} \\
\midrule
RISK-001 & Lack of MFA on sensitive data systems allows for single-factor authentication, making unauthorized access significantly easier if credentials are compromised. & Questionnaire & \textbf{Critical} \\
\addlinespace
RISK-002 & Unencrypted web service (HTTP) is exposed, allowing for potential eavesdropping, session hijacking, and man-in-the-middle attacks. & Network Scan & \textbf{High} \\
\addlinespace
RISK-003 & Absence of annual security training for all staff increases susceptibility to phishing, social engineering, and other human-centric attacks. & Questionnaire & \textbf{High} \\
\bottomrule
\end{tabular}
\end{table}

% --- SECTION 6: RECOMMENDATIONS ---
\section{Recommendations}
Based on the analysis, the following actions are recommended to mitigate the identified risks and improve the overall security posture of \textbf{Midnight Oil Studios}.

\begin{enumerate}
    \item \textbf{Implement MFA for Sensitive Systems (RISK-001):}
    \begin{itemize}
        \item \textbf{Priority:} Immediate.
        \item \textbf{Action:} Enforce MFA across all systems classified as containing sensitive data. This includes databases, file shares, and administrative portals. This is the single most effective control to prevent unauthorized access.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{Secure Web Traffic (RISK-002):}
    \begin{itemize}
        \item \textbf{Priority:} High.
        \item \textbf{Action:} Immediately migrate the service on port 80 to HTTPS on port 443 using a valid TLS certificate. Configure the server to automatically redirect all HTTP requests to HTTPS. If the HTTP service is not required, it should be disabled and the port closed at the firewall.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{Establish Annual Security Training (RISK-003):}
    \begin{itemize}
        \item \textbf{Priority:} High.
        \item \textbf{Action:} Develop and implement a mandatory security awareness training program for all employees, to be conducted at least annually. The training should cover key topics such as phishing identification, password hygiene, and acceptable use policies.
    \end{itemize}
\end{enumerate}

% --- SECTION 7: CONCLUSION ---
\section{Conclusion}
The assessment reveals that while \textbf{Midnight Oil Studios} has implemented some foundational security controls, there are critical deficiencies that expose the organization to significant risk. The lack of MFA on sensitive systems, coupled with an insecure web service and insufficient employee training, creates a vulnerable environment.

By implementing the recommendations outlined in this report, the organization can substantially reduce its attack surface, protect its critical assets, and foster a more resilient security culture. We advise prioritizing these remediation efforts to ensure the confidentiality, integrity, and availability of your data and systems.

\end{document}
```