```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url}      % For URL formatting
\usepackage{seqsplit} % For splitting long strings
\usepackage{graphicx} % For potential logos
\usepackage{xcolor}   % For colors

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% Define custom colors for severity
\definecolor{criticalred}{HTML}{D7263D}
\definecolor{highorange}{HTML}{F49D40}
\definecolor{mediumyellow}{HTML}{F4D440}
\definecolor{lowblue}{HTML}{5C9EAD}

% Document Start
\begin{document}

% Title Page
\title{
    \vspace{2cm}
    \textbf{Cybersecurity Posture Assessment Report} \\
    \large Prepared for: Infinity Loop
    \vspace{1.5cm}
}
\author{Cybersecurity Analyst}
\date{November 22, 2025}
\maketitle
\thispagestyle{empty}
\newpage

% Table of Contents
\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}

This report provides a comprehensive cybersecurity assessment for Infinity Loop, conducted on November 22, 2025. The analysis is based on a network scan, a review of organizational security controls, and an evaluation of known risks.

The assessment reveals several critical and high-risk security gaps that expose the organization to significant threats, including business email compromise, ransomware, and data breaches. Key findings include:

\begin{itemize}
    \item \textbf{Critical Control Gaps:} The absence of Multi-Factor Authentication (MFA) for email and computer access is a critical vulnerability. Furthermore, the lack of a formal security awareness training program and an acceptable use policy leaves the organization highly susceptible to social engineering and insider threats.
    
    \item \textbf{External Vulnerabilities:} The external-facing web server at \texttt{192.168.10.5} is running an outdated version of nginx (1.18.0), which has known vulnerabilities. This presents a direct pathway for external attackers to compromise the system.
    
    \item \textbf{Configuration Issues:} The SSL certificate on the web server is misconfigured, showing a common name for a different organization (\texttt{www.acme-corp.com}), which can erode user trust and may indicate improper server setup.
\end{itemize}

Immediate and decisive action is required to remediate these findings. Recommendations focus on implementing foundational security controls, patching vulnerable systems, and establishing a robust security culture. Addressing these issues will significantly improve the organization's resilience against cyberattacks.

% --- Section 2: Organizational Information ---
\section{Organizational Information}

The following details were provided by the client and used as a baseline for this assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & Infinity Loop \\
Email Domain & \texttt{InfinityLoop.org} \\
Website Domain & \url{www.InfinityLoop.org} \\
External IP Address & \texttt{43.118.94.16} \\ \bottomrule
\end{tabular}
\caption{Client-Provided Organizational Data}
\label{tab:org_data}
\end{table}

% --- Section 3: Security Control Review ---
\section{Security Control Review}

A review of administrative and technical security controls was conducted via a standardized questionnaire. The responses highlight significant gaps in the organization's defensive posture. A "No" response indicates a missing control and a potential area of high risk.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.8\textwidth}c@{}}
\toprule
\textbf{Control Question} & \textbf{Response} \\ \midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{55} \\
Do you require MFA to access sensitive data systems? & \ding{51} \\
Does your organization have an employee acceptable use policy? & \ding{55} \\
Does your organization do security awareness training for new employees? & \ding{55} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results (\ding{51}=Yes, \ding{55}=No)}
\label{tab:controls}
\end{table}

\subsection*{Analysis of Control Gaps}
The lack of MFA on email and computer logins represents a critical failure in access control. A single compromised password could grant an attacker widespread access. The complete absence of a security awareness training program or an acceptable use policy indicates a low level of security maturity, making employees the primary target for phishing and other social engineering attacks.

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}

An Nmap scan was performed against the target host \texttt{192.168.10.5} on November 22, 2025. The scan identified the following open ports and services.

\begin{table}[h!]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product / Version} \\ \midrule
443/TCP & open & https & nginx 1.18.0 \\ \bottomrule
\end{tabular}
\caption{Open Ports on Target: \texttt{192.168.10.5}}
\label{tab:scan_results}
\end{table}

\subsection*{Key Technical Findings}
\begin{itemize}
    \item \textbf{Outdated Software:} The web server is running \textbf{nginx version 1.18.0}, which was released in April 2020. This version is outdated and is affected by multiple publicly disclosed vulnerabilities (e.g., CVE-2021-23017). Running unpatched, internet-facing software poses a high risk of compromise.
    
    \item \textbf{SSL Certificate Mismatch:} The SSL certificate presented by the server has a Common Name of \texttt{www.acme-corp.com}. This does not match the organization's domain (\texttt{InfinityLoop.org}). This misconfiguration can lead to browser trust errors and may indicate that the server is not correctly configured for its intended purpose.
\end{itemize}

% --- Section 5: Risk Assessment Summary ---
\section{Risk Assessment Summary}

The following table synthesizes findings from the control review and technical scan into a prioritized list of identified risks.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.15\textwidth}p{0.65\textwidth}p{0.15\textwidth}@{}}
\toprule
\textbf{Risk ID} & \textbf{Description} & \textbf{Severity} \\ \midrule
RISK-001 & \textbf{Lack of MFA:} No MFA on email or computer logins drastically increases the likelihood of account takeover and unauthorized access from a single stolen credential. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
RISK-002 & \textbf{Inadequate Security Awareness:} The absence of any security training program leaves employees unable to recognize or respond to phishing and social engineering attacks. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
RISK-003 & \textbf{Outdated Web Server:} The internet-facing nginx server is running a vulnerable version, making it a prime target for automated exploits that could lead to a system compromise. & \textcolor{highorange}{\textbf{High}} \\
\addlinespace
RISK-004 & \textbf{Missing Acceptable Use Policy:} Without a formal policy, there is no clear guidance for employees on safe technology use, creating legal and operational risks. & \textcolor{mediumyellow}{\textbf{Medium}} \\
\addlinespace
RISK-005 & \textbf{SSL Certificate Misconfiguration:} The certificate mismatch erodes trust and could be exploited in sophisticated phishing attacks. & \textcolor{lowblue}{\textbf{Low}} \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\label{tab:risks}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}

To mitigate the identified risks and improve the overall security posture of Infinity Loop, we recommend the following actions, prioritized by severity.

\begin{enumerate}
    \item \textbf{[Critical] Implement Multi-Factor Authentication:} Immediately enforce MFA for all user accounts across all critical systems, starting with email (e.g., Office 365, Google Workspace) and all workstation/server logins. This is the single most effective control to prevent account takeovers.
    
    \item \textbf{[Critical] Establish a Security Awareness Program:} Develop and deploy a mandatory security awareness training program for all employees. The program should be conducted upon hiring and at least annually thereafter. It must cover key topics like phishing, password security, and safe browsing.
    
    \item \textbf{[High] Remediate Vulnerable Software:} Upgrade the nginx server on host \texttt{192.168.10.5} from version 1.18.0 to the latest stable version. Implement a formal patch management process to ensure all internet-facing systems are updated in a timely manner.
    
    \item \textbf{[Medium] Develop and Enforce an Acceptable Use Policy (AUP):} Create a formal AUP that clearly defines the rules and responsibilities for employees when using company technology and data. This policy should be reviewed and signed by all employees.
    
    \item \textbf{[Low] Correct SSL Certificate Configuration:} Replace the incorrect SSL certificate on the web server with a valid certificate that matches the organization's domain (\texttt{www.InfinityLoop.org}).
\end{enumerate}

\end{document}
```