```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long strings without breaking
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr} % For header/footer

% --- Document Setup ---

% Define colors for severity levels
\definecolor{sev_critical}{HTML}{990000}
\definecolor{sev_high}{HTML}{D14302}
\definecolor{sev_medium}{HTML}{E89802}
\definecolor{sev_low}{HTML}{3A7A2A}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyhead[L]{Cybersecurity Posture Assessment}
\fancyhead[R]{Verve \& Vigor}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Document Start ---

\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    \Huge
    \textbf{Cybersecurity Posture Assessment Report}
    
    \vspace{1.5cm}
    
    \Large
    Prepared For: \\
    \vspace{0.5cm}
    \textbf{Verve \& Vigor}
    
    \vspace{2cm}
    
    \normalsize
    Report Date: \today \\
    Scan Date: 2025-11-22
    
    \vfill
    
    \normalsize
    \textit{This document contains sensitive information. Access is restricted to authorized personnel only. Do not distribute without explicit permission.}
    
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}

This report provides a comprehensive assessment of the cybersecurity posture for \textbf{Verve \& Vigor}. The analysis is based on a technical network scan, a review of organizational security controls, and an evaluation of known risks.

The assessment identified several critical and high-risk vulnerabilities that require immediate attention. The most significant findings include:
\begin{itemize}
    \item \textbf{Critical Gaps in Access Control:} Multi-Factor Authentication (MFA) is not enforced for accessing email or other sensitive data systems. This exposes the organization to a high risk of account compromise and subsequent data breaches.
    \item \textbf{Vulnerable External Services:} The external-facing web server is running an outdated version of Nginx (\texttt{1.18.0}), which has multiple known public vulnerabilities. This presents a direct and exploitable vector for attackers.
    \item \textbf{Insufficient Employee Onboarding:} New employees do not receive mandatory security awareness training, making them highly susceptible to social engineering attacks like phishing, which could bypass other security controls.
\end{itemize}

The overall security posture is considered weak due to these fundamental control failures. Immediate remediation of the identified risks is strongly recommended to protect organizational assets and reduce the likelihood of a significant security incident.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \textbf{Verve \& Vigor} \\
    Email Domain & \texttt{VerveVigor.org} \\
    External IP Address & \texttt{188.175.254.208} \\
    \bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of administrative and organizational security controls was conducted via a questionnaire. The responses highlight significant gaps in the current security framework.

\begin{table}[h!]
\centering
\caption{Organizational Security Controls Questionnaire}
\begin{tabular}{@{}p{0.75\linewidth}c@{}}
\toprule
\textbf{Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{51} \\
Do you require MFA to access sensitive data systems? & \ding{55} \\
Does your organization have an employee acceptable use policy? & \ding{51} \\
Does your organization do security awareness training for new employees? & \ding{55} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{51} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis of Control Gaps}
The responses marked with a cross (\ding{55}) indicate critical weaknesses:
\begin{itemize}
    \item \textbf{No MFA for Email and Sensitive Data:} The lack of MFA on these critical systems is a severe vulnerability. Email is a primary target for attackers seeking to perform Business Email Compromise (BEC) or pivot to other internal systems. Protecting sensitive data systems with only a password is insufficient against modern credential-based attacks.
    \item \textbf{No Security Training for New Hires:} New employees are a prime target for social engineering. Failing to provide immediate security training upon hiring leaves a window of high vulnerability where an employee may unknowingly violate policy or fall victim to a phishing attack.
\end{itemize}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{192.168.10.5}
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

\begin{table}[h!]
\centering
\caption{Open Ports and Services Detected}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
443/tcp & open & https & nginx & \texttt{1.18.0} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis of Technical Findings}
The scan identified one open port, which is hosting a web server.
\begin{itemize}
    \item \textbf{Outdated Nginx Version:} The web server is running Nginx version \texttt{1.18.0}, which was released in April 2020. This version is significantly outdated and has numerous publicly disclosed vulnerabilities, including high-severity issues. Running unsupported and unpatched software on an internet-facing system presents a high risk of compromise.
\end{itemize}

% --- Section 5: Risk Assessment ---
\section{Risk Assessment}
Based on the correlation of organizational and technical findings, the following risks have been identified and prioritized.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{@{}p{0.1\linewidth}p{0.25\linewidth}p{0.45\linewidth}p{0.1\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
RISK-001 & Inadequate Access Control & The absence of MFA on email and sensitive data systems exposes the organization to account takeovers, data breaches, and financial fraud. & \textcolor{sev_critical}{\textbf{Critical}} \\
\addlinespace
RISK-002 & Vulnerable Web Server Software & The public-facing web server runs an outdated version of Nginx (\texttt{1.18.0}) with known, exploitable vulnerabilities, risking server compromise and data exfiltration. & \textcolor{sev_high}{\textbf{High}} \\
\addlinespace
RISK-003 & Insufficient Security Awareness Program & New employees do not receive security training, making them vulnerable to phishing and other social engineering attacks that could compromise credentials or introduce malware. & \textcolor{sev_high}{\textbf{High}} \\
\bottomrule
\end{tabular}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks. Recommendations are prioritized based on severity and potential impact.

\begin{description}
    \item[\textbf{REC-001 (Priority: Critical)}] \hfill \\
    \textbf{Action:} Implement and enforce Multi-Factor Authentication (MFA) across all critical systems. \\
    \textbf{Details:} Prioritize the deployment of MFA for all user accounts on the email system (\texttt{VerveVigor.org}) and all systems identified as containing sensitive data. This is the single most effective control to prevent unauthorized access.
    
    \item[\textbf{REC-002 (Priority: High)}] \hfill \\
    \textbf{Action:} Upgrade the Nginx web server and implement a patch management process. \\
    \textbf{Details:} The Nginx instance on server \texttt{192.168.10.5} must be upgraded to the latest stable version immediately. Furthermore, a formal patch management policy should be established to ensure all internet-facing systems are regularly updated to protect against known vulnerabilities.
    
    \item[\textbf{REC-003 (Priority: High)}] \hfill \\
    \textbf{Action:} Develop and mandate a security awareness training program for new hires. \\
    \textbf{Details:} Institute a mandatory security awareness training module as part of the employee onboarding process. This training should cover key topics such as phishing identification, acceptable use policies, and password hygiene.
\end{description}

\end{document}
```