```latex
\documentclass[12pt]{article}

% Preamble: Required Packages and Document Setup
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage[T1]{fontenc}

% Document Metadata
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{November 22, 2025}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\thispagestyle{empty}
\newpage

\setcounter{page}{1}

% ==============================================================================
% Section 1: Executive Summary
% ==============================================================================
\section{Executive Summary}

This report provides a comprehensive cybersecurity assessment for \textbf{Symmetry Architecture}, conducted on November 22, 2025. The analysis combines a review of organizational security controls, an external network scan, and a review of pre-existing risks.

The assessment identified several critical and high-risk gaps in the organization's security posture. Most notably, the lack of Multi-Factor Authentication (MFA) on email services presents a critical vulnerability to account compromise and subsequent business email compromise (BEC) attacks. This is compounded by significant deficiencies in security governance, including the absence of an employee acceptable use policy and a formal security awareness training program.

From a technical perspective, the external-facing web server at \texttt{192.168.10.5} is running an outdated version of Nginx (1.18.0), which is known to have security vulnerabilities. Furthermore, a critical SSL certificate mismatch was discovered, where the certificate is issued for \texttt{www.acme-corp.com} instead of the organization's domain, which severely erodes user trust and may indicate a serious server misconfiguration.

Immediate remediation is recommended, focusing on implementing MFA for email, upgrading the web server software, correcting the SSL certificate configuration, and establishing foundational security policies and training programs.

% ==============================================================================
% Section 2: Organizational Information
% ==============================================================================
\section{Organizational Information}

The following information was provided by the client and used as a baseline for this assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Symmetry Architecture} \\
Email Domain & \texttt{SymmetryArchitecture.org} \\
Website Domain & \url{www.SymmetryArchitecture.org} \\
External IP Address & \texttt{174.0.39.114} \\
\bottomrule
\end{tabular}

% ==============================================================================
% Section 3: Security Control Review
% ==============================================================================
\section{Security Control Review}

A review of administrative and organizational security controls was conducted via a standardized questionnaire. The responses reveal significant gaps in foundational security practices. A "No" response indicates a missing control and a direct increase in organizational risk.

\begin{table}[h!]
\centering
\caption{Organizational Security Control Questionnaire}
\begin{tabular}{@{}p{0.6\linewidth} c p{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \ding{55} & \textbf{Critical Gap} \\
Do you require MFA to log into computers? & \ding{51} & Best Practice Met \\
Do you require MFA to access sensitive data systems? & \ding{51} & Best Practice Met \\
Does your organization have an employee acceptable use policy? & \ding{55} & \textbf{High Risk} \\
Does your organization do security awareness training for new employees? & \ding{55} & \textbf{High Risk} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} & \textbf{High Risk} \\
\bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% Section 4: Technical Scan Results
% ==============================================================================
\section{Technical Scan Results}

An external network scan was performed on \texttt{192.168.10.5} to identify open ports, running services, and potential vulnerabilities visible from the internet.

\subsection{Host Status}
The target host was found to be online and responsive during the scan.
\begin{itemize}
    \item \textbf{Target IP:} \texttt{192.168.10.5}
    \item \textbf{Status:} Up
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

\subsection{Open Port Analysis}
The following table details the ports and services discovered on the target host.

\begin{table}[h!]
\centering
\caption{Discovered Open Ports and Services}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
443/tcp & https & nginx & 1.18.0 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Key Technical Findings}
Two significant issues were identified during the technical scan:

\begin{enumerate}
    \item \textbf{Outdated Web Server Software:} The server is running \textbf{Nginx version 1.18.0}, which was released in April 2020. This version is no longer supported and has multiple documented vulnerabilities (e.g., CVE-2021-23017). Running outdated software exposes the organization to publicly known exploits.
    
    \item \textbf{SSL Certificate Mismatch:} The SSL certificate presented by the server on port 443 is for the common name \texttt{www.acme-corp.com}. This does not match the organization's domain (\texttt{www.SymmetryArchitecture.org}). This misconfiguration will cause browser trust errors, can be an indicator of a phishing attempt, and suggests a flawed deployment process.
\end{enumerate}

% ==============================================================================
% Section 5: Consolidated Risk Assessment
% ==============================================================================
\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security control review and technical scan into a prioritized list of risks. No pre-existing vulnerabilities were reported.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{@{}p{0.1\linewidth} p{0.25\linewidth} p{0.45\linewidth} p{0.1\linewidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
RISK-001 & Lack of MFA on Email & The absence of MFA on email accounts makes them highly susceptible to phishing and credential stuffing, leading to potential data breaches and BEC. & \textbf{Critical} \\
\addlinespace
RISK-002 & Outdated Web Server Software & The public-facing Nginx server is running an old version with known vulnerabilities, making it a prime target for automated exploitation. & High \\
\addlinespace
RISK-003 & Missing Security Policies and Training & The lack of an acceptable use policy and security awareness training means employees are likely unaware of security best practices, increasing the risk of human error. & High \\
\addlinespace
RISK-004 & SSL Certificate Mismatch & The incorrect SSL certificate erodes user trust, can disrupt service, and indicates a critical misconfiguration of the web server. & Medium \\
\bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% Section 6: Recommendations
% ==============================================================================
\section{Recommendations}

The following actions are recommended to mitigate the identified risks and improve the overall security posture of \textbf{Symmetry Architecture}.

\begin{description}
    \item[\textbf{For RISK-001 (Lack of MFA on Email):}]
    \begin{itemize}
        \item \textbf{Immediate Action:} Enforce mandatory MFA for all user accounts on the email platform (\texttt{SymmetryArchitecture.org}). Prioritize administrator and executive accounts.
        \item \textbf{Policy:} Update IT policy to require MFA for all externally accessible services.
    \end{itemize}

    \item[\textbf{For RISK-002 (Outdated Web Server Software):}]
    \begin{itemize}
        \item \textbf{Immediate Action:} Plan and execute an upgrade of the Nginx server at \texttt{192.168.10.5} to the latest stable version.
        \item \textbf{Process:} Establish a patch management process to ensure all internet-facing systems are regularly updated.
    \end{itemize}

    \item[\textbf{For RISK-003 (Missing Policies and Training):}]
    \begin{itemize}
        \item \textbf{Short-Term:} Develop and implement a formal Acceptable Use Policy (AUP) that all employees must read and acknowledge.
        \item \textbf{Mid-Term:} Institute a mandatory security awareness training program for all new hires and conduct annual refresher training for all staff. Focus on phishing, password hygiene, and data handling.
    \end{itemize}

    \item[\textbf{For RISK-004 (SSL Certificate Mismatch):}]
    \begin{itemize}
        \item \textbf{Immediate Action:} Procure and correctly install a valid SSL/TLS certificate for the domain \texttt{www.SymmetryArchitecture.org} on the Nginx server.
        \item \textbf{Process:} Implement a certificate lifecycle management process to track expiration dates and ensure proper configuration during deployment.
    \end{itemize}
\end{description}

\end{document}
```