```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For hyperlinks
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long strings in tt font
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Document Metadata
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% Define colors for severity
\definecolor{criticalred}{HTML}{D73B3E}
\definecolor{highorange}{HTML}{F58425}
\definecolor{mediumyellow}{HTML}{FFC425}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{Swift Current Labs}
\rhead{Confidential}
\cfoot{\thepage}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}

This report provides a cybersecurity posture assessment for \textbf{Swift Current Labs}, based on an analysis of organizational security controls, network scan data, and pre-existing risk information.

The assessment reveals a mixed security posture. While foundational controls such as an acceptable use policy and security training for new hires are in place, there are critical deficiencies in the implementation of Multi-Factor Authentication (MFA) and the provision of ongoing security awareness training. These gaps significantly elevate the risk of unauthorized access through credential compromise and social engineering attacks.

Technical analysis of the target host \texttt{172.16.0.1} identified an open port (80/HTTP), indicating the presence of an unencrypted web service. This service exposes data to interception and requires immediate investigation to identify the running software and assess it for vulnerabilities.

Immediate remediation should focus on implementing MFA for sensitive systems and computer access, establishing a mandatory annual security training program for all employees, and securing the exposed web service by enforcing encryption (HTTPS).

% --- 2. Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment.

\begin{itemize}
    \item \textbf{Organization Name:} Swift Current Labs
    \item \textbf{Email Domain:} \texttt{SwiftCurrentLabs.net}
    \item \textbf{Website Domain:} \url{www.SwiftCurrentLabs.net}
    \item \textbf{External IP Address:} \texttt{24.125.112.37}
\end{itemize}

% --- 3. Security Control Review ---
\section{Security Control Review}
The following table summarizes the organization's responses to a security controls questionnaire. Items marked with \ding{55} represent significant gaps in the current security posture.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Results}
\begin{tabular}{p{0.8\linewidth} c}
\toprule
\textbf{Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \ding{51} \\
\textbf{Do you require MFA to log into computers?} & \textbf{\color{criticalred}\ding{55}} \\
\textbf{Do you require MFA to access sensitive data systems?} & \textbf{\color{criticalred}\ding{55}} \\
Does your organization have an employee acceptable use policy? & \ding{51} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
\textbf{Does your organization do security awareness training for all employees at least once per year?} & \textbf{\color{highorange}\ding{55}} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The questionnaire highlights two critical areas of concern:
\begin{enumerate}
    \item \textbf{Lack of Multi-Factor Authentication (MFA):} The absence of MFA for computer logins and access to sensitive data systems is a critical vulnerability. Should an employee's credentials be compromised, an attacker could gain direct access to company resources and data without needing a second authentication factor.
    \item \textbf{Insufficient Security Training:} While new employees receive training, the lack of an annual refresher course for all staff is a high-risk gap. The threat landscape evolves continuously, and without ongoing training, employees are more likely to fall victim to modern phishing and social engineering tactics.
\end{enumerate}

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}
A network scan was performed on the specified target to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.0.1}
\end{itemize}

\begin{table}[h!]
\centering
\caption{Open Port Analysis}
\begin{tabular}{l l l p{0.5\linewidth}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Notes} \\
\midrule
80/tcp & open & HTTP (Assumed) & The service is transmitting data in cleartext. This exposes information, including potential login credentials, to interception. The specific product and version were not identified in this scan. \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The presence of an open HTTP port is a medium-severity finding. Unencrypted web traffic is a significant privacy and security risk. Furthermore, without knowing the specific web server software and version, it is impossible to determine if it is vulnerable to known exploits.

% --- 5. Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes findings from the security control review and technical scan into a prioritized list of risks. The risk presented in the input data regarding system overrides has been disregarded as a data anomaly and is not a valid finding.

\begin{table}[h!]
\centering
\caption{Identified Risks}
\begin{tabular}{p{0.2\linewidth} p{0.6\linewidth} l}
\toprule
\textbf{Risk Title} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Lack of MFA on Endpoints and Systems} & The absence of MFA on computer logins and sensitive systems exposes the organization to account takeover and unauthorized access if a single password is compromised. & \textbf{\color{criticalred}Critical} \\
\addlinespace
\textbf{Inadequate Security Awareness Training} & Without mandatory annual training, employees' ability to recognize and respond to evolving threats like phishing and social engineering diminishes over time. & \textbf{\color{highorange}High} \\
\addlinespace
\textbf{Unencrypted Web Service Exposure} & An open HTTP port (80) exposes web traffic to eavesdropping. The underlying service is a potential attack vector if it is outdated or misconfigured. & \textbf{\color{mediumyellow}Medium} \\
\bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks and improve the overall security posture of \textbf{Swift Current Labs}.

\subsection{Critical Priority}
\begin{itemize}
    \item \textbf{Implement MFA for Sensitive Systems and Endpoints:}
    \begin{itemize}
        \item \textbf{Immediate Action:} Prioritize and deploy a robust MFA solution for all systems containing sensitive data. This is the single most effective control to prevent unauthorized access.
        \item \textbf{Long-Term Action:} Enforce MFA for all user endpoint logins (desktops and laptops) to protect against lateral movement within the network.
    \end{itemize}
\end{itemize}

\subsection{High Priority}
\begin{itemize}
    \item \textbf{Establish a Continuous Security Training Program:}
    \begin{itemize}
        \item \textbf{Immediate Action:} Schedule and mandate a security awareness training session for all current employees within the next quarter.
        \item \textbf{Long-Term Action:} Develop a formal program that includes annual refresher courses and periodic phishing simulation exercises to keep security top-of-mind.
    \end{itemize}
\end{itemize}

\subsection{Medium Priority}
\begin{itemize}
    \item \textbf{Secure or Decommission Exposed Web Service:}
    \begin{itemize}
        \item \textbf{Immediate Action:} Identify the service running on port 80 on host \texttt{172.16.0.1}. If it is a necessary web server, immediately implement TLS/SSL to enforce HTTPS (port 443) and encrypt all traffic.
        \item \textbf{Long-Term Action:} Conduct a vulnerability scan against the service to identify its software version and patch any known vulnerabilities. If the service is not business-critical, it should be disabled and the port closed.
    \end{itemize}
\end{itemize}

\end{document}
```