```latex
\documentclass[12pt]{article}

% --- PACKAGE IMPORTS ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% --- DOCUMENT METADATA & STYLING ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfpagemode=FullScreen,
}

\pagestyle{fancy}
\fancyhf{}
\lhead{Cybersecurity Assessment Report}
\rhead{Borealis Tech}
\cfoot{\thepage}

\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge\textbf{Cybersecurity Assessment Report}
    \vspace{1.5cm}
    \Large
    \textbf{Prepared for:}\\
    Borealis Tech
    \vspace{2cm}
    \large
    \textbf{Date of Report:}\\
    \today
    \vfill
    \large
    \textbf{CONFIDENTIAL}
    \vspace{0.8cm}
    \normalsize
    This document contains sensitive information. Distribution is restricted to authorized personnel only.
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report details the findings of a cybersecurity assessment conducted for Borealis Tech. The assessment combined a review of organizational security controls, a technical network scan, and an analysis of pre-existing risk data.

The analysis revealed several critical and high-risk findings that require immediate attention. A key technical vulnerability is the direct network exposure of a MySQL database service (version 5.7.33) on host \texttt{172.16.50.20}. This finding is exacerbated by the fact that this version of MySQL is approaching its end-of-life, potentially leaving it unsupported against new threats.

Furthermore, significant gaps were identified in administrative and access controls. The lack of mandatory Multi-Factor Authentication (MFA) for email and computer access, combined with the absence of an employee Acceptable Use Policy, substantially increases the risk of unauthorized access and data breaches.

This report provides a detailed breakdown of these findings and offers actionable recommendations to mitigate the identified risks and improve the overall security posture of Borealis Tech.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following information was provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & Borealis Tech \\
    Email Domain & \texttt{BorealisTech.com} \\
    Website Domain & \url{www.BorealisTech.com} \\
    External IP Address & \texttt{62.46.102.163} \\
    \bottomrule
\end{tabular}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}
A review of administrative and security controls was conducted based on a standardized questionnaire. The results highlight critical gaps in access control and policy enforcement.

\begin{tabular}{@{}p{0.6\linewidth}ccp{0.2\linewidth}@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
    \midrule
    Do you require MFA to access email? & \ding{55} & \textcolor{red}{\textbf{Critical Gap}} \\
    Do you require MFA to log into computers? & \ding{55} & \textcolor{red}{\textbf{Critical Gap}} \\
    Do you require MFA to access sensitive data systems? & \ding{51} & Met \\
    Does your organization have an employee acceptable use policy? & \ding{55} & \textcolor{orange}{\textbf{High Risk}} \\
    Does your organization do security awareness training for new employees? & \ding{51} & Met \\
    Does your organization do security awareness training for all employees at least once per year? & \ding{51} & Met \\
    \bottomrule
\end{tabular}
\\
\vspace{1em}
\textit{Note: \ding{51} indicates "Yes", \ding{55} indicates "No".}

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
An external network scan was performed on the specified target to identify open ports and exposed services.

\subsection{Scan Details}
\begin{itemize}
    \item \textbf{Target IP:} \texttt{172.16.50.20}
    \item \textbf{Scan Tool:} Nmap
\end{itemize}

\subsection{Open Ports and Services}
A single open port was discovered, exposing a critical database service.

\begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Port} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
    \midrule
    3306/tcp & mysql & MySQL & 5.7.33 \\
    \bottomrule
\end{tabular}

\subsection{Technical Analysis}
The scan confirms that a MySQL database on port \texttt{3306} is directly accessible from the network. Exposing a database service in this manner is a significant security risk, as it allows attackers to directly target the database for brute-force attacks, credential stuffing, or exploitation of known vulnerabilities.

The identified version, MySQL 5.7.33, was released in January 2021. The MySQL 5.7 branch reached its official End of Life (EOL) in October 2023, meaning it no longer receives security patches from the vendor. Running unsupported software, especially for a critical database, is a high-risk practice.

% --- RISK ASSESSMENT ---
\section{Risk Assessment}
The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a consolidated list of identified risks.

\begin{tabular}{@{}p{0.25\linewidth}p{0.5\linewidth}p{0.15\linewidth}@{}}
    \toprule
    \textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\
    \midrule
    \textbf{Database Exposure} & The MySQL database on port 3306 is open to the network, allowing direct connection attempts from potentially malicious actors. This correlates with pre-existing risk data. & \textcolor{red}{\textbf{Critical (9.8)}} \\
    \addlinespace
    \textbf{Lack of MFA on Critical Systems} & Email and computer logins are secured with passwords only. This significantly increases the risk of account compromise via phishing or credential theft. & \textcolor{red}{\textbf{Critical (9.1)}} \\
    \addlinespace
    \textbf{Unsupported Database Software} & The MySQL version (5.7.33) is past its End of Life and no longer receives security updates, leaving it vulnerable to newly discovered exploits. & \textcolor{orange}{\textbf{High (8.8)}} \\
    \addlinespace
    \textbf{Missing Acceptable Use Policy} & The absence of a formal policy defining acceptable use of company assets creates ambiguity and legal/compliance risks. & \textcolor{yellow!80!black}{\textbf{Medium (5.3)}} \\
    \bottomrule
\end{tabular}

% --- RECOMMENDATIONS ---
\section{Recommendations}
Based on the findings, the following actions are recommended to mitigate the identified risks. Recommendations are prioritized by severity.

\begin{enumerate}
    \item \textbf{Immediately Remediate Database Exposure (Critical):}
    \begin{itemize}
        \item \textbf{Short-Term:} Implement strict firewall rules to deny all public access to TCP port 3306 on host \texttt{172.16.50.20}. Access should be restricted to trusted internal IP addresses only.
        \item \textbf{Long-Term:} Establish a secure access method, such as a Virtual Private Network (VPN), for all administrative access to database servers.
    \end{itemize}
    
    \item \textbf{Implement Multi-Factor Authentication (MFA) (Critical):}
    \begin{itemize}
        \item Enforce MFA for all user accounts for accessing email (e.g., Office 365, Google Workspace) and for logging into company computers (e.g., via Windows Hello, Duo).
    \end{itemize}
    
    \item \textbf{Upgrade Unsupported Software (High):}
    \begin{itemize}
        \item Plan and execute the migration of the MySQL 5.7.33 database to a currently supported version (e.g., MySQL 8.x). This will ensure the system receives timely security patches.
    \end{itemize}
    
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP) (Medium):}
    \begin{itemize}
        \item Create a formal AUP that clearly outlines the rules and responsibilities for all employees when using company technology and data. Ensure all employees read and acknowledge the policy.
    \end{itemize}
\end{enumerate}

\end{document}
```