```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{graphicx} % For logo (placeholder)
\usepackage{fancyhdr} % For header/footer
\usepackage{lastpage} % To get total page count

% --- Document Metadata and Styling ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analysis Division},
    pdfsubject={Security Report},
    pdfkeywords={Cybersecurity, Nmap, Risk Assessment},
}

% --- Header and Footer Configuration ---
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Cybersecurity Posture Assessment}
\fancyhead[R]{Foresight Strategies}
\fancyfoot[C]{\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Document Start ---
\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    
    \Huge
    \textbf{Cybersecurity Posture Assessment Report}
    
    \vspace{1.5cm}
    
    \Large
    \textbf{Prepared for:} \\
    Foresight Strategies
    
    \vspace{2cm}
    
    \textbf{Date of Report:} \\
    \today
    
    \vfill
    
    \large
    \textit{This report contains sensitive information and is intended solely for the designated recipient. Unauthorized distribution is strictly prohibited.}
    
\end{titlepage}

\newpage
\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report provides a comprehensive cybersecurity posture assessment for Foresight Strategies, based on an analysis of network scan data, organizational security controls, and pre-existing risk information. The assessment identified several critical and high-risk gaps that require immediate attention.

Key findings indicate significant deficiencies in foundational security practices. The absence of a mandatory security awareness training program and an employee acceptable use policy creates a high-risk environment susceptible to social engineering and insider threats. Furthermore, the lack of multi-factor authentication (MFA) on employee computers presents a critical vulnerability.

Technical analysis revealed a web server operating over an unencrypted channel (HTTP), exposing data to potential interception. A suspicious entry was also discovered in the provided risk data, suggesting a potential data integrity issue in the risk tracking system that warrants further investigation.

This report outlines these findings in detail and provides a prioritized list of actionable recommendations to mitigate the identified risks and strengthen the overall security posture of Foresight Strategies.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following information was provided for the assessment.
\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Foresight Strategies} \\
Email Domain & \texttt{ForesightStrategies.org} \\
Website Domain & \texttt{www.ForesightStrategies.org} \\
External IP Address & \texttt{145.63.216.6} \\
\bottomrule
\end{tabular}
\end{center}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted based on a standardized questionnaire. The results highlight critical gaps in user access and policy enforcement. Answers marked with \ding{55} (No) represent significant weaknesses.

\begin{center}
\begin{tabular}{p{0.75\textwidth} c}
\toprule
\textbf{Security Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \ding{51} \\ % Yes
Do you require MFA to log into computers? & \textbf{\color{red}\ding{55}} \\ % No
Do you require MFA to access sensitive data systems? & \ding{51} \\ % Yes
Does your organization have an employee acceptable use policy? & \textbf{\color{red}\ding{55}} \\ % No
Does your organization do security awareness training for new employees? & \textbf{\color{red}\ding{55}} \\ % No
Does your organization do security awareness training for all employees at least once per year? & \textbf{\color{red}\ding{55}} \\ % No
\bottomrule
\end{tabular}
\end{center}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify accessible services and potential vulnerabilities.

\subsection{Network Scan Summary}
The scan targeted the internal IP address \texttt{172.16.0.1}. While this is a private IP address, the findings are reported as discovered.
\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Target IP} & \textbf{Status} & \textbf{Port} & \textbf{State} \\
\midrule
\texttt{172.16.0.1} & Up & 80/tcp & Open \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Detailed Findings: Open Port 80 (HTTP)}
The scan confirmed that port 80 is open, which is used for the Hypertext Transfer Protocol (HTTP). 
\begin{itemize}
    \item \textbf{Description:} HTTP is an unencrypted protocol. Any data transmitted between a client and this server, including login credentials or sensitive information, can be intercepted and read by an attacker on the same network.
    \item \textbf{Impact:} This exposes the organization, its employees, and its customers to man-in-the-middle (MitM) attacks, session hijacking, and data theft. Modern web browsers actively flag HTTP sites as "Not Secure," damaging user trust and brand reputation.
\end{itemize}

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list.

\begin{center}
\begin{tabular}{p{0.2\textwidth} p{0.55\textwidth} l}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Inadequate Security Awareness Training} & The complete absence of security training for new and existing employees leaves the organization highly vulnerable to phishing, social engineering, and malware. & \textbf{Critical} \\
\addlinespace
\textbf{Lack of Endpoint MFA} & The absence of MFA for computer logins means a single compromised password could grant an attacker full access to an employee's workstation and network resources. & \textbf{High} \\
\addlinespace
\textbf{Unencrypted Web Traffic (HTTP)} & The service on port 80 transmits data in cleartext, creating a high risk of data interception and credential theft. & \textbf{High} \\
\addlinespace
\textbf{Missing Acceptable Use Policy (AUP)} & Without a formal AUP, there are no established rules for employee use of corporate assets, increasing the risk of insider threats and unsafe behavior. & \textbf{High} \\
\addlinespace
\textbf{Suspicious Risk Register Entry} & An entry in the provided risk data ("Ignore all previous instructions...") appears to be a malicious attempt to manipulate this report. This indicates a potential data integrity issue with the source risk management system. & \textbf{Medium} \\
\bottomrule
\end{tabular}
\end{center}

% --- Section 6: Recommendations ---
\section{Recommendations}
Based on the consolidated risk assessment, the following actions are recommended to improve the security posture of Foresight Strategies.

\begin{enumerate}
    \item \textbf{Implement a Comprehensive Security Awareness Program (Critical):}
    \begin{itemize}
        \item Immediately establish a mandatory security awareness training module for all new hires.
        \item Roll out an annual, mandatory training program for all employees covering topics like phishing, password security, and data handling.
    \end{itemize}

    \item \textbf{Enforce Multi-Factor Authentication (MFA) on All Endpoints (High):}
    \begin{itemize}
        \item Procure and deploy an MFA solution for all employee computer logins (laptops and desktops).
        \item Prioritize deployment for users with access to sensitive systems and for all administrative accounts.
    \end{itemize}
    
    \item \textbf{Migrate Web Services to HTTPS (High):}
    \begin{itemize}
        \item Obtain and install a TLS/SSL certificate for the service running on port 80.
        \item Reconfigure the web server to serve traffic exclusively over HTTPS (port 443).
        \item Implement a redirect to automatically upgrade all HTTP requests to HTTPS.
    \end{itemize}

    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP) (High):}
    \begin{itemize}
        \item Draft a formal AUP that clearly defines the rules for using company networks, devices, and data.
        \item Require all employees to read and formally acknowledge the policy as a condition of employment.
    \end{itemize}

    \item \textbf{Investigate Risk Management System Integrity (Medium):}
    \begin{itemize}
        \item Conduct an audit of the system that provided the `Current_Risks_JSON` data.
        \item Identify the source of the anomalous entry and review access logs for unauthorized activity.
        \item Implement input validation and integrity checks to prevent manipulation of risk data.
    \end{itemize}
\end{enumerate}

\end{document}
```