```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings to prevent overflow

% Document Metadata
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analyst}
\date{November 22, 2025}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage
\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}
This report provides a comprehensive cybersecurity assessment for \textbf{Binary Star}, based on an analysis of network scan data, organizational security controls, and pre-existing risk information. The assessment was conducted on November 22, 2025.

The analysis revealed several areas of significant concern that require immediate attention. A critical vulnerability exists due to the lack of Multi-Factor Authentication (MFA) on email systems, exposing the organization to a high risk of Business Email Compromise (BEC) and account takeovers.

Furthermore, technical scans identified a web server running an outdated version of Nginx (\texttt{1.18.0}), which is susceptible to multiple known vulnerabilities. This technical risk is compounded by high-risk organizational gaps, including the absence of an employee Acceptable Use Policy and a formal security awareness training program. These deficiencies collectively weaken the organization's defense against common cyber threats such as phishing and malware.

This report details these findings and provides actionable recommendations to mitigate the identified risks and improve the overall security posture of \textbf{Binary Star}.

% --- 2. Organizational Information ---
\section{Organizational Information}
The following information was provided for the assessment.

\begin{itemize}
    \item \textbf{Organization Name:} Binary Star
    \item \textbf{Email Domain:} \texttt{BinaryStar.net}
    \item \textbf{Website Domain:} \url{www.BinaryStar.net}
    \item \textbf{External IP Address:} \texttt{216.203.37.181}
\end{itemize}

% --- 3. Security Control Review ---
\section{Security Control Review}
A review of foundational security controls was conducted based on a supplied questionnaire. The responses indicate critical gaps in administrative and access control policies. A summary of the findings is presented in Table \ref{tab:controls}.

\begin{table}[h!]
\centering
\caption{Organizational Security Control Status}
\label{tab:controls}
\begin{tabular}{@{}lc@{}}
\toprule
\textbf{Control Question} & \textbf{Response} \\ \midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{51} \\
Do you require MFA to access sensitive data systems? & \ding{51} \\
Does your organization have an employee acceptable use policy? & \ding{55} \\
Does your organization do security awareness training for new employees? & \ding{55} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} \\ \bottomrule
\end{tabular}
\end{table}

\noindent \textit{Note: \ding{51} indicates 'Yes' (control implemented), \ding{55} indicates 'No' (control gap).}

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{192.168.10.5}
    \item \textbf{Scan Date:} 2025-11-22
\end{itemize}

The scan identified one open port, as detailed in Table \ref{tab:scan}.

\begin{table}[h!]
\centering
\caption{Open Port Analysis}
\label{tab:scan}
\begin{tabular}{@{}cllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\ \midrule
443/tcp & open & https & nginx & \textbf{1.18.0} \\ \bottomrule
\end{tabular}
\end{table}

\noindent The web server software, \textbf{Nginx version 1.18.0}, is outdated. This version was released in April 2020 and is known to be vulnerable to several security issues, including but not limited to CVE-2021-23017. Running outdated software presents a significant risk of exploitation.

% --- 5. Risk Assessment Summary ---
\section{Risk Assessment Summary}
The following table synthesizes findings from the security control review and technical scans into a prioritized list of risks. No pre-existing vulnerabilities were reported in the input data.

\begin{table}[h!]
\centering
\caption{Identified Risks and Severity}
\label{tab:risks}
\begin{tabular}{@{}p{0.1\linewidth}p{0.25\linewidth}p{0.45\linewidth}p{0.1\linewidth}@{}}
\toprule
\textbf{Risk ID} & \textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\ \midrule
RSK-001 & Lack of MFA on Email & The absence of MFA on email accounts exposes the organization to a high likelihood of account takeover, phishing, and Business Email Compromise (BEC). & \textbf{Critical} \\ \addlinespace
RSK-002 & Outdated Web Server Software & The public-facing web server runs Nginx 1.18.0, an outdated version with known vulnerabilities. This could allow an attacker to compromise the server, leading to data breach or service disruption. & \textbf{High} \\ \addlinespace
RSK-003 & Inadequate Security Policies and Training & The lack of an Acceptable Use Policy and any form of security awareness training leaves employees unprepared to identify and respond to threats, significantly increasing the risk of human error leading to a security incident. & \textbf{High} \\ \bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
To address the identified risks, the following actions are recommended with urgency.

\subsection{RSK-001: Lack of MFA on Email (Critical)}
\begin{itemize}
    \item \textbf{Immediate Action:} Procure and enforce a mandatory MFA solution for all user access to the email system (\texttt{BinaryStar.net}). This is the single most effective control to prevent unauthorized account access.
\end{itemize}

\subsection{RSK-002: Outdated Web Server Software (High)}
\begin{itemize}
    \item \textbf{Immediate Action:} Plan and execute an upgrade of the Nginx server on host \texttt{192.168.10.5} from version \texttt{1.18.0} to the latest stable version.
    \item \textbf{Strategic Action:} Implement a formal patch and vulnerability management program to ensure all systems are updated in a timely manner.
\end{itemize}

\subsection{RSK-003: Inadequate Security Policies and Training (High)}
\begin{itemize}
    \item \textbf{Immediate Action:} Develop and formally adopt an employee Acceptable Use Policy (AUP) that defines the rules for using company IT assets.
    \item \textbf{Mid-Term Action:} Implement a mandatory security awareness training program for all employees. This program should be required for new hires during onboarding and for all staff on an annual basis.
\end{itemize}

% --- 7. Conclusion ---
\section{Conclusion}
The assessment for \textbf{Binary Star} has identified critical and high-severity risks that require immediate remediation. The primary areas of concern are the lack of essential access controls (MFA on email), the presence of a vulnerable public-facing server, and foundational gaps in security governance and employee training.

By implementing the recommendations outlined in this report, \textbf{Binary Star} can significantly reduce its attack surface and build a more resilient security posture against prevalent cyber threats.

\end{document}
```