```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings
\usepackage{xcolor} % For colors
\usepackage{graphicx} % For logo
\usepackage{fancyhdr} % For header/footer

% --- Document Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Report},
    pdfauthor={Automated Security Analysis System},
    pdfsubject={Cybersecurity Assessment},
    pdfkeywords={Security, Report, Analysis},
}

% --- Custom Colors for Severity ---
\definecolor{sev_critical}{HTML}{940000}
\definecolor{sev_high}{HTML}{D14000}
\definecolor{sev_medium}{HTML}{E8A100}

% --- Header and Footer ---
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyhead[L]{Cybersecurity Posture Report}
\fancyhead[R]{White Label}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Document Start ---
\begin{document}

\begin{titlepage}
    \centering
    \vfill
    {\Huge\bfseries Cybersecurity Posture Report\par}
    \vspace{1.5cm}
    {\Large\bfseries Prepared For:\par}
    {\Large White Label\par}
    \vspace{2cm}
    {\large \today\par}
    \vfill
    \textit{This report contains sensitive information. Distribution should be limited to authorized personnel only.}
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report provides a cybersecurity assessment for White Label, based on an analysis of network scan data, organizational security controls, and known risks. The assessment was conducted on \today.

The overall security posture is determined to be at a \textbf{high risk level}. Several critical vulnerabilities and security gaps were identified that expose the organization to significant threats, including data breaches, account compromise, and service disruption.

Key findings include:
\begin{itemize}
    \item \textbf{Critical Lack of Multi-Factor Authentication (MFA):} MFA is not enforced for accessing email or for computer logins, creating a high risk of unauthorized access via stolen credentials.
    \item \textbf{Use of Unencrypted Protocols:} The external network scan identified an open port 80 (HTTP), indicating that web traffic is transmitted in cleartext. This exposes data to interception and manipulation.
    \item \textbf{Inadequate Security Policies and Training:} The absence of a formal Acceptable Use Policy and the lack of recurring, annual security awareness training for all staff weaken the organization's human firewall and create compliance risks.
\end{itemize}

Immediate remediation of these issues is strongly recommended to reduce the organization's attack surface and improve its defensive capabilities. Detailed findings and actionable recommendations are provided in the subsequent sections.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment. This information helps establish the context and scope of the review.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & White Label \\
    Email Domain & \texttt{WhiteLabel.org} \\
    Website Domain & \url{www.WhiteLabel.org} \\
    External IP Address & \texttt{124.60.239.58} \\
    \bottomrule
\end{tabular}

\textit{Note: The provided risk data (Input 3) was determined to be malformed or non-actionable and has been excluded from this analysis. The assessment proceeds based on the security control questionnaire and technical scan data.}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
An internal review of security controls was conducted via a questionnaire. The responses highlight significant gaps in foundational security practices. A "No" response indicates a deviation from best practices and a potential security risk.

\begin{tabular}{@{}p{0.6\linewidth}cp{0.25\linewidth}@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
    \midrule
    Do you require MFA to access email? & \ding{55} & \textcolor{sev_critical}{\textbf{Critical Gap.}} Email is a primary target for phishing and account takeover. \\
    \addlinespace
    Do you require MFA to log into computers? & \ding{55} & \textcolor{sev_critical}{\textbf{Critical Gap.}} Lack of endpoint MFA allows lateral movement if credentials are compromised. \\
    \addlinespace
    Do you require MFA to access sensitive data systems? & \ding{51} & \textbf{Good Practice.} This control is correctly implemented and should be expanded. \\
    \addlinespace
    Does your organization have an employee acceptable use policy? & \ding{55} & \textcolor{sev_high}{\textbf{High Risk.}} Absence of a formal policy creates legal and operational ambiguity for employees. \\
    \addlinespace
    Does your organization do security awareness training for new employees? & \ding{51} & \textbf{Good Start.} Onboarding training is a positive first step. \\
    \addlinespace
    Does your organization do security awareness training for all employees at least once per year? & \ding{55} & \textcolor{sev_high}{\textbf{High Risk.}} Security is an ongoing effort; one-time training is insufficient to maintain awareness. \\
    \bottomrule
\end{tabular}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed against the target IP address \texttt{172.16.0.1}. The scan revealed the following open ports and services.

\begin{tabular}{@{}lllll@{}}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Finding} \\
    \midrule
    80/tcp & Open & HTTP & \textcolor{sev_high}{\textbf{High Risk}} \\
    \bottomrule
\end{tabular}

\subsection*{Finding: Unencrypted Web Traffic (HTTP)}
The presence of an open port 80 indicates that a web server is operating using the Hypertext Transfer Protocol (HTTP). HTTP is an unencrypted protocol, meaning that all data transmitted between a user's browser and the server, including login credentials or sensitive information, is sent in cleartext. This data can be easily intercepted and read by an attacker on the same network (e.g., public Wi-Fi) or through a Man-in-the-Middle (MitM) attack. Standard practice is to use HTTPS (Port 443), which encrypts traffic using TLS/SSL.

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes findings from the security control review and the technical scan into a prioritized list of risks.

\begin{tabular}{@{}p{0.1\linewidth}p{0.25\linewidth}p{0.45\linewidth}l@{}}
    \toprule
    \textbf{ID} & \textbf{Risk Title} & \textbf{Description} & \textbf{Severity} \\
    \midrule
    \addlinespace
    RISK-001 & Lack of Multi-Factor Authentication & The absence of MFA on email and computer logins exposes the organization to a high likelihood of account compromise through phishing or credential stuffing attacks. & \textcolor{sev_critical}{Critical} \\
    \addlinespace
    RISK-002 & Use of Unencrypted Web Traffic & The active HTTP service on port 80 transmits data in cleartext, making it vulnerable to eavesdropping and credential theft. & \textcolor{sev_high}{High} \\
    \addlinespace
    RISK-003 & Inadequate Security Policies and Training & The lack of an Acceptable Use Policy and recurring security training for all staff leads to a weak security culture and increases the risk of human error. & \textcolor{sev_high}{High} \\
    \addlinespace
    \bottomrule
\end{tabular}

% --- Section 6: Recommendations ---
\section{Recommendations}
To mitigate the identified risks and improve the overall security posture, the following actions are recommended with urgency.

\subsection*{Immediate Actions (0-30 Days)}
\begin{enumerate}
    \item \textbf{Enable MFA for All Email Accounts (RISK-001):} Immediately enforce MFA (using an authenticator app, SMS, or hardware token) for all user accounts accessing the \texttt{WhiteLabel.org} email system. This is the single most effective control to prevent email account takeovers.
    
    \item \textbf{Decommission HTTP Service (RISK-002):} Immediately disable the service on TCP port 80. If a web service is required, configure it to use HTTPS exclusively on TCP port 443 with a valid TLS certificate and strong cipher suites. Implement HTTP Strict Transport Security (HSTS).
\end{enumerate}

\subsection*{Short-Term Actions (30-90 Days)}
\begin{enumerate}
    \setcounter{enumi}{2}
    \item \textbf{Deploy Endpoint MFA (RISK-001):} Implement MFA for all employee computer logins (Windows, macOS, etc.). This adds a critical layer of security to prevent unauthorized access to endpoints and lateral movement within the network.
    
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP) (RISK-003):} Draft and ratify a formal AUP that clearly defines the rules for using company IT assets, data, and internet access. Require all employees to read and acknowledge the policy.
    
    \item \textbf{Institute Annual Security Awareness Training (RISK-003):} Establish a mandatory security awareness training program for all employees, to be completed annually. The training should cover current threats such as phishing, social engineering, and password hygiene.
\end{enumerate}

% --- Document End ---
\end{document}
```