```latex
\documentclass[12pt]{article}

% Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmark and X symbols
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{xcolor} % For colors in tables

% Document Metadata
\title{Cybersecurity Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfpagemode=FullScreen,
}

\begin{document}

\maketitle
\thispagestyle{empty}

\newpage
\tableofcontents
\thispagestyle{empty}

\newpage
\section{Executive Overview}

This report provides a comprehensive cybersecurity assessment for \textbf{Stone Arch Masonry}. The analysis is based on a correlation of technical network scan data, a review of organizational security controls via a questionnaire, and an evaluation of pre-existing risks.

The assessment reveals a mixed security posture. While the organization has implemented Multi-Factor Authentication (MFA) for critical systems like email and sensitive data access, there are significant and high-risk gaps in foundational administrative and procedural controls. 

Key findings include:
\begin{itemize}
    \item \textbf{Critical Policy Gaps:} The complete absence of an employee Acceptable Use Policy (AUP) and a security awareness training program presents a critical risk. These gaps leave the organization highly vulnerable to social engineering, phishing attacks, and insider threats.
    \item \textbf{Endpoint Security Weakness:} The lack of MFA for computer logins is a high-risk vulnerability that could allow an attacker with compromised credentials to gain direct access to internal network resources.
    \item \textbf{External Service Exposure:} A technical scan identified an open Secure Shell (SSH) port on an external IPv6 address. While necessary for remote administration, this service must be rigorously secured to prevent unauthorized access.
\end{itemize}

Immediate and decisive action is required to address the identified policy and training deficiencies. Strengthening these foundational controls will significantly improve the organization's resilience against common cyber threats.

\section{Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \textbf{Stone Arch Masonry} \\
    Email Domain & \texttt{StoneArchMasonry.org} \\
    Website Domain & \url{www.StoneArchMasonry.org} \\
    External IP Address & \texttt{209.64.17.216} \\
    \bottomrule
\end{tabular}

\section{Security Control Review}

The following table summarizes the organization's responses to a security controls questionnaire. Items marked with \ding{55} represent significant gaps in the security framework and are considered high-risk findings.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{8cm}cc@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
    \midrule
    Do you require MFA to access email? & \ding{51} (Yes) & Meets Best Practice \\
    Do you require MFA to log into computers? & \textcolor{red}{\ding{55}} (No) & \textcolor{red}{High Risk} \\
    Do you require MFA to access sensitive data systems? & \ding{51} (Yes) & Meets Best Practice \\
    Does your organization have an employee acceptable use policy? & \textcolor{red}{\ding{55}} (No) & \textcolor{red}{Critical Control Gap} \\
    Does your organization do security awareness training for new employees? & \textcolor{red}{\ding{55}} (No) & \textcolor{red}{Critical Control Gap} \\
    Does your organization do security awareness training for all employees at least once per year? & \textcolor{red}{\ding{55}} (No) & \textcolor{red}{Critical Control Gap} \\
    \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Analysis}
\end{table}

\section{Technical Scan Results}

A network scan was performed on the specified target to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \seqsplit{\texttt{2001:db8::1}}
    \item \textbf{Host Status:} Up
\end{itemize}

The following table details the open ports discovered during the scan.

\begin{table}[h!]
\centering
\begin{tabular}{@{}llll@{}}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Notes} \\
    \midrule
    22/tcp & Open & SSH & Service version not enumerated. Exposed SSH \\
    & & (Secure Shell) & requires strong credentials, key-based \\
    & & & authentication, and access control lists. \\
    \bottomrule
\end{tabular}
\caption{Open Port Analysis}
\end{table}

\section{Risk Assessment Summary}

The following table consolidates findings from the security control review and technical scan into a prioritized list of risks. No pre-existing vulnerabilities were reported.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lp{5.5cm}l@{}}
    \toprule
    \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
    \midrule
    Absence of Security Awareness Training & The lack of any employee training program leaves the organization highly susceptible to phishing, malware, and social engineering attacks. & \textbf{Critical} \\
    \addlinespace
    Lack of Acceptable Use Policy & Without a formal AUP, there are no established rules for employee use of company assets, creating legal and security risks. & \textbf{High} \\
    \addlinespace
    No Endpoint Multi-Factor Authentication & The absence of MFA on computer logins means a single compromised password could grant an attacker full access to an endpoint. & \textbf{High} \\
    \addlinespace
    Exposed SSH Service & Port 22 is open to the internet, creating a direct vector for brute-force attacks and unauthorized access if not properly secured. & \textbf{Medium} \\
    \bottomrule
\end{tabular}
\caption{Consolidated Risk Register}
\end{table}

\section{Recommendations}

Based on the analysis, the following actions are recommended to mitigate the identified risks and improve the overall security posture of \textbf{Stone Arch Masonry}.

\begin{itemize}
    \item \textbf{[Critical Priority] Implement a Security Awareness Program:}
    \begin{itemize}
        \item Immediately establish a mandatory security awareness training program for all employees.
        \item Training should be conducted for all new hires during onboarding and annually for all staff.
        \item Key topics must include phishing identification, password security, safe browsing, and data handling procedures.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{[High Priority] Develop and Enforce an Acceptable Use Policy (AUP):}
    \begin{itemize}
        \item Create a formal AUP that clearly defines the rules for using company networks, devices, and data.
        \item Require all current and new employees to read and sign the policy to acknowledge their understanding and agreement.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{[High Priority] Enforce MFA on All Endpoints:}
    \begin{itemize}
        \item Deploy a solution to require MFA for all computer and laptop logins. This significantly reduces the risk of unauthorized access from compromised credentials.
        \item Solutions can include Windows Hello for Business, Duo Security, or other third-party MFA providers.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{[Medium Priority] Secure the Exposed SSH Service:}
    \begin{itemize}
        \item Review the business justification for exposing SSH on \seqsplit{\texttt{2001:db8::1}}.
        \item If required, implement firewall rules to restrict access to only trusted source IP addresses.
        \item Enforce public key authentication and disable password-based logins to prevent brute-force attacks.
    \end{itemize}
\end{itemize}

\end{document}
```