```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For \ding
\usepackage{booktabs} % For professional tables (\toprule, \midrule, \bottomrule)
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in \texttt
\usepackage{xcolor} % For colors

% Document Information
\title{Cybersecurity Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cybersecurity Assessment Report},
    pdfauthor={Cybersecurity Analysis Division},
    pdfsubject={Security Assessment},
    pdfkeywords={Security, Analysis, Report}
}

\begin{document}

\maketitle
\hrule
\vspace{1cm}

\begin{center}
    \textbf{Prepared for: Iron Bridge Legal}
\end{center}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section*{1. Executive Summary}

This report provides a comprehensive cybersecurity assessment for Iron Bridge Legal, based on network scans, a security controls questionnaire, and a review of pre-existing risks. The analysis reveals several critical and high-risk findings that require immediate attention to mitigate potential security breaches.

The primary technical finding is a publicly accessible MySQL database (port 3306) running an \textbf{End-of-Life (EOL) version (5.7.33)}. This service is no longer receiving security updates, exposing it to a wide range of known vulnerabilities. This finding confirms and elevates a previously identified risk of database exposure.

Furthermore, the security controls review identified significant administrative gaps. The organization lacks a formal \textbf{Acceptable Use Policy (AUP)} and does not conduct \textbf{annual security awareness training} for all employees. These policy and training deficiencies increase the likelihood of human error leading to a security incident, compounding the technical risks.

Immediate remediation should focus on restricting network access to the database server and developing a plan to upgrade the EOL software. Concurrently, the development and implementation of foundational security policies and training programs are crucial for improving the organization's long-term security posture.

% --- Section 2: Organizational Information ---
\section*{2. Organizational Information}

The following information was provided for the assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & Iron Bridge Legal \\
Email Domain & \texttt{IronBridgeLegal.net} \\
Website Domain & \url{www.IronBridgeLegal.net} \\
External IP Address & \texttt{81.125.127.199} \\
\bottomrule
\end{tabular}
\caption{Client Organizational Details}
\end{table}

% --- Section 3: Security Control Review ---
\section*{3. Security Control Review}

A review of the organization's security controls was conducted via a questionnaire. The results are summarized below. A checkmark (\ding{51}) indicates a positive control is in place, while a cross (\ding{55}) indicates a control gap.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lc@{}}
\toprule
\textbf{Security Control Question} & \textbf{Status} \\
\midrule
Do you require MFA to access email? & \textcolor{green}{\ding{51}} \\
Do you require MFA to log into computers? & \textcolor{green}{\ding{51}} \\
Do you require MFA to access sensitive data systems? & \textcolor{green}{\ding{51}} \\
\textbf{Does your organization have an employee acceptable use policy?} & \textcolor{red}{\ding{55}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} \\
\textbf{Does your organization do security awareness training for all employees annually?} & \textcolor{red}{\ding{55}} \\
\bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results}
\end{table}

\subsection*{Analysis of Control Gaps}
The questionnaire reveals two significant gaps in administrative controls:
\begin{itemize}
    \item \textbf{Lack of Acceptable Use Policy (AUP):} Without a formal AUP, there are no defined rules for employees regarding the use of company assets, data handling, and internet usage. This ambiguity can lead to unintentional policy violations and security incidents.
    \item \textbf{Lack of Annual Security Training:} While new employees receive training, the absence of an annual refresher program for all staff is a high-risk gap. The threat landscape evolves continuously, and without regular training, employees are more susceptible to modern phishing, ransomware, and social engineering attacks.
\end{itemize}

% --- Section 4: Technical Scan Results ---
\section*{4. Technical Scan Results}

A network scan was performed on the target system to identify open ports and running services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.50.20}
    \item \textbf{Scan Date:} As per scan metadata.
\end{itemize}

\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & Open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}
\caption{Open Ports and Services Detected}
\end{table}

\subsection*{Technical Analysis}
The scan identified one open port, which presents a critical security risk:
\begin{itemize}
    \item \textbf{Exposed MySQL Database (Port 3306):} The MySQL database service is directly accessible from the network. Database servers should not be publicly exposed and should only be accessible from trusted application servers or via a secure VPN connection. This configuration makes the server a prime target for brute-force attacks, credential stuffing, and exploitation of vulnerabilities.
    \item \textbf{End-of-Life (EOL) Software:} The detected version, \textbf{MySQL 5.7.33}, reached its official End of Life in \textbf{October 2023}. This means it no longer receives security patches from the vendor. Any vulnerabilities discovered after this date will remain unpatched, leaving the system critically vulnerable to exploitation.
\end{itemize}

% --- Section 5: Consolidated Risk Assessment ---
\section*{5. Consolidated Risk Assessment}

The following table synthesizes findings from the technical scan, control review, and pre-existing risk data into a prioritized list of security risks.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.3\linewidth}p{0.55\linewidth}p{0.1\linewidth}@{}}
\toprule
\textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\
\midrule
\textbf{End-of-Life Database Software} & The MySQL server is running version 5.7.33, which is past its End of Life and no longer receives security updates. This exposes the system to numerous unpatchable vulnerabilities. & \textbf{Critical} \\
\addlinespace
\textbf{Database Exposure} & The MySQL database port (3306) is open to the network, allowing direct connection attempts. This increases the risk of unauthorized access, data breach, and denial-of-service attacks. & High \\
\addlinespace
\textbf{Inadequate Security Training} & The lack of mandatory annual security awareness training for all employees weakens the human firewall, making the organization more vulnerable to phishing and social engineering. & High \\
\addlinespace
\textbf{Lack of Acceptable Use Policy} & The absence of a formal AUP creates ambiguity around security responsibilities and proper handling of company assets, increasing the risk of insider threat and data mishandling. & High \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\end{table}

% --- Section 6: Recommendations ---
\section*{6. Recommendations}

Based on the risk assessment, the following prioritized actions are recommended to improve the security posture of Iron Bridge Legal.

\subsection*{Immediate Priority (0-7 Days)}
\begin{enumerate}
    \item \textbf{Restrict Access to Database:} Immediately implement firewall rules to restrict access to TCP port 3306. Access should be denied from all sources except for specific, authorized application servers or management IP addresses.
\end{enumerate}

\subsection*{High Priority (1-3 Months)}
\begin{enumerate}
    \item \textbf{Upgrade End-of-Life Software:} Plan and execute the migration of the MySQL 5.7 database to a currently supported version (e.g., MySQL 8.x). This is critical to ensure the system receives ongoing security patches.
    \item \textbf{Develop and Implement Acceptable Use Policy (AUP):} Draft a formal AUP that clearly outlines the rules and responsibilities for all employees when using company technology and data. The policy should be reviewed by management and legal counsel, and all employees must read and acknowledge it.
    \item \textbf{Establish Annual Security Training Program:} Procure and roll out a mandatory security awareness training program for all employees to be completed annually. This training should cover topics such as phishing, password security, and data handling.
\end{enumerate}

\subsection*{Long-Term Strategy}
\begin{enumerate}
    \item \textbf{Network Segmentation:} Review and implement network segmentation to isolate critical systems like databases from general user networks, reducing the attack surface.
    \item \textbf{Vulnerability Management Program:} Establish a formal process for regularly scanning systems for vulnerabilities and managing the patching lifecycle to prevent EOL software issues in the future.
\end{enumerate}

\end{document}
```