```latex
\documentclass[12pt]{article}

% --- PACKAGE IMPORTS ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage[T1]{fontenc}

% --- DOCUMENT METADATA ---
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% --- HYPERREF SETUP ---
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analysis Division},
}

% --- DOCUMENT START ---
\begin{document}

\maketitle
\hrule
\vspace{1em}

% ==============================================================================
% 1. EXECUTIVE SUMMARY
% ==============================================================================
\section*{1. Executive Summary}

This report provides a comprehensive cybersecurity assessment for \textbf{Infinity Loop}, based on an analysis of network scan data, organizational security controls, and pre-existing risk information.

The assessment reveals several critical and high-risk security gaps that require immediate attention. The most significant findings include the complete absence of Multi-Factor Authentication (MFA) across all critical systems, including email, computer logins, and access to sensitive data. This represents a fundamental failure in identity and access management.

Furthermore, a technical scan confirmed a publicly accessible MySQL database running on an End-of-Life (EOL) version (5.7.33). This exposes the organization to numerous known and future vulnerabilities for which no security patches will be released. This technical vulnerability, combined with the lack of MFA and insufficient annual security training, creates a high-likelihood path for a significant data breach.

Immediate remediation should focus on restricting access to the exposed database, implementing MFA universally, and planning the urgent migration of the EOL database software.

% ==============================================================================
% 2. ORGANIZATIONAL INFORMATION
% ==============================================================================
\section*{2. Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Infinity Loop} \\
Email Domain & \texttt{InfinityLoop.com} \\
Website Domain & \url{www.InfinityLoop.com} \\
External IP Address & \texttt{79.159.192.166} \\
\bottomrule
\end{tabular}

% ==============================================================================
% 3. SECURITY CONTROL REVIEW (QUESTIONNAIRE)
% ==============================================================================
\section*{3. Security Control Review}

A review of the organization's security controls via a questionnaire identified significant gaps in access control and employee security awareness. "No" answers indicate a failure to meet baseline security best practices and are highlighted as major risks.

\begin{tabular}{@{}p{0.8\linewidth}c}
\toprule
\textbf{Control Question} & \textbf{Status} \\
\midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{55} \\
Do you require MFA to access sensitive data systems? & \ding{55} \\
Does your organization have an employee acceptable use policy? & \ding{51} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} \\
\bottomrule
\end{tabular}
\\ \vspace{0.5em}
\textit{Key: \ding{51} = Yes (Control in place) \quad \ding{55} = No (Control gap identified)}

% ==============================================================================
% 4. TECHNICAL SCAN RESULTS
% ==============================================================================
\section*{4. Technical Scan Results}

An external network scan was performed on the target system to identify open ports and exposed services.

\subsection*{4.1 Scan Details}
\begin{itemize}
    \item \textbf{Target IP:} \texttt{172.16.50.20}
    \item \textbf{Scan Tool:} Nmap
\end{itemize}

\subsection*{4.2 Open Ports and Services}
The scan identified the following open port, which directly corresponds to a database service.

\begin{tabular}{@{}lllll}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}

\subsection*{4.3 Analysis of Technical Findings}
The scan confirms that a MySQL database on port \texttt{3306} is directly exposed to the network. This is a high-risk configuration that allows attackers to directly target the database for brute-force attacks, credential stuffing, or exploitation of vulnerabilities.

\textbf{Crucially, the identified version, MySQL 5.7, reached its official End-of-Life (EOL) in October 2023.} This means Oracle will no longer provide security patches, updates, or bug fixes for this version. Running EOL software presents a critical risk, as any newly discovered vulnerabilities will remain unpatched, leaving the system perpetually vulnerable to exploitation.

% ==============================================================================
% 5. CONSOLIDATED RISK ASSESSMENT
% ==============================================================================
\section*{5. Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list of security risks.

\begin{tabular}{@{}p{0.25\linewidth}p{0.15\linewidth}p{0.55\linewidth}}
\toprule
\textbf{Risk Name} & \textbf{Severity} & \textbf{Overview} \\
\midrule
\textbf{Lack of Multi-Factor Authentication (MFA)} & \textbf{Critical} & The absence of MFA across email, computer logins, and sensitive systems makes the organization highly susceptible to account takeovers via phishing or password compromise. This is the most critical process gap. \\
\addlinespace
\textbf{End-of-Life Software in Use} & \textbf{Critical} & The exposed MySQL database is running version 5.7, which is no longer supported with security patches. This system is a prime target for attackers exploiting known or future vulnerabilities. \\
\addlinespace
\textbf{Database Exposure} & \textbf{High} & The MySQL service on port 3306 is open to the network, violating the principle of least privilege. This allows attackers to directly interact with a critical data store. This finding confirms a pre-existing identified risk. \\
\addlinespace
\textbf{Insufficient Security Awareness Training} & \textbf{High} & The lack of mandatory annual security training for all employees increases the organization's susceptibility to social engineering and phishing attacks, which are primary vectors for initial compromise. \\
\bottomrule
\end{tabular}

% ==============================================================================
% 6. RECOMMENDATIONS
% ==============================================================================
\section*{6. Recommendations}

The following actions are recommended to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection*{6.1 Immediate Priority (Within 72 Hours)}
\begin{enumerate}
    \item \textbf{Restrict Database Access:} Immediately implement strict firewall rules to ensure that the MySQL server (\texttt{172.16.50.20:3306}) is only accessible from trusted internal IP addresses. Public access must be disabled.
\end{enumerate}

\subsection*{6.2 High Priority (Within 30 Days)}
\begin{enumerate}
    \item \textbf{Enforce Universal MFA:} Procure and enforce an MFA solution for all employees and contractors. Prioritize its rollout in the following order:
    \begin{itemize}
        \item Access to sensitive data systems (including databases).
        \item Email access (e.g., Office 365, Google Workspace).
        \item All computer and remote access (VPN) logins.
    \end{itemize}
    \item \textbf{Plan Database Migration:} Develop a formal project plan to migrate the MySQL 5.7 database to a fully supported version (e.g., MySQL 8.x or a suitable alternative). This plan should include data backup, testing, and a scheduled cutover date.
\end{enumerate}

\subsection*{6.3 Medium Priority (Within 90 Days)}
\begin{enumerate}
    \item \textbf{Implement Annual Security Training:} Establish a mandatory security awareness training program for all employees to be completed annually. This program should cover topics such as phishing identification, password hygiene, and acceptable use policies.
\end{enumerate}

\end{document}
```