```latex
\documentclass[12pt]{article}

% --- PACKAGES ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage{xcolor} % For colors
\usepackage{graphicx} % For logos, etc.
\usepackage{fancyhdr} % For headers and footers

% --- DOCUMENT SETUP ---
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.33}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}

\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
    citecolor=darkblue,
}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Cybersecurity Assessment Report}
\fancyhead[R]{For: Skyward Bound}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- COMMANDS ---
\newcommand{\yes}{\ding{51}}
\newcommand{\no}{\ding{55}}

% --- DOCUMENT START ---
\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{2cm}
    
    {\Huge \textbf{Cybersecurity Posture and Risk Assessment Report}\par}
    \vspace{1.5cm}
    
    {\Large \textbf{Prepared for:}\par}
    {\Large Skyward Bound\par}
    
    \vspace{2cm}
    
    {\Large \textbf{Date of Report:}\par}
    {\Large \today\par}
    
    \vfill
    
    {\large \textit{This report contains sensitive information and should be handled with care. Distribution is restricted to authorized personnel only.}\par}
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report provides a comprehensive analysis of the cybersecurity posture for Skyward Bound, based on a combination of network scanning, a security controls questionnaire, and a review of pre-existing risks.

The external network scan of the target host \texttt{192.168.1.100} revealed a strong security configuration, with \textbf{no open ports detected}. This indicates a well-hardened perimeter for the assessed system, significantly reducing its external attack surface.

However, the security controls review identified several \textbf{critical and high-risk administrative and policy gaps}. The most severe findings include the lack of multi-factor authentication (MFA) on sensitive data systems and employee computers. Furthermore, the absence of an acceptable use policy and mandatory security training for new hires introduces significant human-factor risks.

While no pre-existing vulnerabilities were noted, the identified policy gaps represent a substantial threat to the organization's data and operational integrity. This report outlines prioritized, actionable recommendations to mitigate these risks and strengthen the overall security framework.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following details were provided for the assessment.
\begin{itemize}
    \item \textbf{Organization Name:} Skyward Bound
    \item \textbf{Email Domain:} \texttt{SkywardBound.org}
    \item \textbf{Website Domain:} \url{www.SkywardBound.org}
    \item \textbf{External IP Address:} \texttt{162.55.105.87}
\end{itemize}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}
The following table summarizes the responses from the security questionnaire. "No" answers indicate significant gaps in security controls and are correlated with the risks identified in Section 5.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\label{tab:controls}
\begin{tabular}{@{}p{0.6\linewidth} c p{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \yes & Best Practice Met \\
\addlinespace
Do you require MFA to log into computers? & \textcolor{darkred}{\no} & \textbf{High Risk Gap} \\
\addlinespace
Do you require MFA to access sensitive data systems? & \textcolor{darkred}{\no} & \textbf{Critical Risk Gap} \\
\addlinespace
Does your organization have an employee acceptable use policy? & \textcolor{darkred}{\no} & \textbf{High Risk Gap} \\
\addlinespace
Does your organization do security awareness training for new employees? & \textcolor{darkred}{\no} & \textbf{High Risk Gap} \\
\addlinespace
Does your organization do security awareness training for all employees at least once per year? & \yes & Best Practice Met \\
\bottomrule
\end{tabular}
\end{table}

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
An Nmap scan was conducted to identify open ports and services on the target system. The results indicate a very secure network posture for the scanned host.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{192.168.1.100}
    \item \textbf{Host Status:} Up
\end{itemize}

\begin{table}[h!]
\centering
\caption{Network Scan Findings for \texttt{192.168.1.100}}
\label{tab:nmap}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{Service} & \textbf{Product / Version} & \textbf{Finding} \\
\midrule
\multicolumn{4}{c}{\textit{No open ports were detected.}} \\
\multicolumn{4}{c}{All 1000 scanned ports on this host are in a 'closed' state.} \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textbf{Analysis:} The absence of open ports is an excellent security practice. It means the host does not expose any network services, minimizing the potential for remote exploitation. No further technical vulnerabilities were identified on this host.

% --- RISK ASSESSMENT ---
\section{Risk Assessment}
This section synthesizes findings from the security control review and technical scan. While the technical posture of the scanned host is strong, significant policy and administrative risks were identified.

\begin{table}[h!]
\centering
\caption{Identified Risks and Severity}
\label{tab:risks}
\begin{tabular}{@{}p{0.25\linewidth} p{0.55\linewidth} l@{}}
\toprule
\textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\
\midrule
\addlinespace
No MFA on Sensitive Systems & The absence of a second authentication factor for systems containing critical data exposes the organization to severe data breach risk if credentials are compromised. & \textcolor{darkred}{\textbf{Critical}} \\
\addlinespace
No MFA on Workstations & Lack of MFA on computer logins allows an attacker with stolen credentials to easily gain network access and potentially move laterally to other systems. & High \\
\addlinespace
No New Hire Security Training & New employees are a primary target for phishing and social engineering. Without initial training, they are more likely to fall victim to attacks. & High \\
\addlinespace
No Acceptable Use Policy (AUP) & Without a formal AUP, employees may be unaware of security responsibilities and acceptable behavior, leading to unintentional insider threats and policy violations. & High \\
\bottomrule
\end{tabular}
\end{table}

% --- RECOMMENDATIONS ---
\section{Recommendations}
The following actionable recommendations are prioritized based on the severity of the identified risks. Implementing these controls will significantly improve the security posture of Skyward Bound.

\begin{enumerate}
    \item \textbf{[Critical] Implement MFA for All Sensitive Data Systems:}
    \begin{itemize}
        \item \textbf{Action:} Immediately enforce MFA for all users, especially administrators, accessing databases, financial systems, and other critical applications.
        \item \textbf{Impact:} Drastically reduces the risk of unauthorized access to the organization's most valuable data assets.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[High] Enforce MFA for All Computer Logins:}
    \begin{itemize}
        \item \textbf{Action:} Deploy an MFA solution for all employee workstations and laptops (e.g., Windows Hello, Duo, etc.).
        \item \textbf{Impact:} Prevents unauthorized access to endpoints, which are the primary entry point for most network compromises.
    \end{itemize}
    \vspace{0.5cm}

    \item \textbf{[High] Establish a New Hire Security Training Program:}
    \begin{itemize}
        \item \textbf{Action:} Develop a mandatory security awareness training module to be completed by all new employees as part of their onboarding process. This should cover phishing, password security, and data handling.
        \item \textbf{Impact:} Equips new staff with the knowledge to recognize and report security threats from day one, reducing human-related risks.
    \end{itemize}
    \vspace{0.5cm}
    
    \item \textbf{[High] Develop and Implement an Acceptable Use Policy (AUP):}
    \begin{itemize}
        \item \textbf{Action:} Draft a formal AUP that clearly defines the rules for using company technology and data. Require all employees to read and acknowledge the policy annually.
        \item \textbf{Impact:} Establishes a clear security baseline for employee behavior and provides a framework for enforcing security standards.
    \end{itemize}
\end{enumerate}

\end{document}
```