```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long monospaced text
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Document Metadata & Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Report},
    pdfauthor={Cybersecurity Analysis Service},
    pdfsubject={Security Assessment},
    pdfkeywords={Cybersecurity, Risk, Assessment},
    bookmarks=true
}

% Define colors for table headers
\definecolor{tableheader}{rgb}{0.1, 0.3, 0.5}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Cybersecurity Posture Report}
\fancyhead[R]{\textbf{Great Lakes}}
\fancyfoot[C]{\thepage}

% --- DOCUMENT START ---
\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge
    \textbf{Cybersecurity Posture Report}
    
    \vspace{1.5cm}
    \Large
    Prepared For: \\
    \vspace{0.5cm}
    \textbf{Great Lakes}
    
    \vspace{2cm}
    \large
    Report Date: November 22, 2025 \\
    Scan Date: November 22, 2025
    
    \vfill
    
    \large
    \textbf{CONFIDENTIAL} \\
    \small
    This document contains sensitive information. Distribution is restricted to authorized personnel within the client organization.
    
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report details the findings of a cybersecurity assessment conducted for \textbf{Great Lakes}. The assessment combined a review of organizational security controls, an external network scan, and an analysis of known risks.

The overall security posture requires immediate attention. Several critical and high-risk vulnerabilities were identified that expose the organization to significant threats, including account compromise, data breaches, and service disruption.

Key findings include:
\begin{itemize}
    \item \textbf{Critical Gaps in Multi-Factor Authentication (MFA):} MFA is not enforced for accessing email or other sensitive data systems. This represents a critical vulnerability, as compromised credentials could grant attackers direct access to core business communications and confidential information.
    \item \textbf{Outdated Web Server Software:} The external-facing web server at \texttt{192.168.10.5} is running an outdated version of Nginx (1.18.0). This version is several years old and is known to have multiple security vulnerabilities, making it a prime target for exploitation.
    \item \textbf{Deficient Security Policies and Training:} The organization lacks a formal Acceptable Use Policy and does not conduct mandatory annual security awareness training for all staff. These gaps weaken the human element of security, increasing susceptibility to phishing and social engineering attacks.
\end{itemize}

Immediate remediation of these issues is strongly recommended to reduce the organization's risk profile. Detailed recommendations are provided in Section \ref{sec:recommendations}.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \textbf{Great Lakes} \\
    Email Domain & \texttt{GreatLakes.org} \\
    External IP Address & \texttt{136.1.86.51} \\
    \bottomrule
\end{tabular}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}
A questionnaire was completed to evaluate the implementation of fundamental security controls. The responses indicate significant gaps in the organization's security framework.

\begin{table}[h!]
\centering
\caption{Security Control Questionnaire Responses}
\begin{tabular}{p{0.6\linewidth} c c}
    \toprule
    \rowcolor{tableheader}
    \textcolor{white}{\textbf{Control Question}} & \textcolor{white}{\textbf{Response}} & \textcolor{white}{\textbf{Status}} \\
    \midrule
    Do you require MFA to access email? & No & \textcolor{red}{\ding{55}} \\
    Do you require MFA to log into computers? & Yes & \textcolor{green}{\ding{51}} \\
    Do you require MFA to access sensitive data systems? & No & \textcolor{red}{\ding{55}} \\
    Does your organization have an employee acceptable use policy? & No & \textcolor{red}{\ding{55}} \\
    Does your organization do security awareness training for new employees? & Yes & \textcolor{green}{\ding{51}} \\
    Does your organization do security awareness training for all employees at least once per year? & No & \textcolor{red}{\ding{55}} \\
    \bottomrule
\end{tabular}
\end{table}

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
An Nmap scan was performed on the target system to identify open ports and running services.

\subsection{Host: \texttt{192.168.10.5}}
The scan revealed one open port on the target host.

\begin{table}[h!]
\centering
\caption{Open Ports and Services for \texttt{192.168.10.5}}
\begin{tabular}{l l l l l}
    \toprule
    \rowcolor{tableheader}
    \textcolor{white}{\textbf{Port}} & \textcolor{white}{\textbf{State}} & \textcolor{white}{\textbf{Service}} & \textcolor{white}{\textbf{Product}} & \textcolor{white}{\textbf{Version}} \\
    \midrule
    443/tcp & open & https & nginx & \textbf{1.18.0} \\
    \bottomrule
\end{tabular}
\end{table}

\paragraph{Analysis:} The host is running an Nginx web server, version \textbf{1.18.0}, which was released in April 2020. This version is outdated and no longer receives security updates. Publicly known vulnerabilities, such as CVE-2021-23017, affect this version, exposing the server to potential compromise.

% --- RISK ASSESSMENT ---
\section{Risk Assessment}
The following table synthesizes findings from the security control review and technical scan into a prioritized list of risks. No pre-existing vulnerabilities were reported.

\begin{table}[h!]
\centering
\caption{Synthesized Risk Summary}
\begin{tabular}{p{0.1\linewidth} p{0.3\linewidth} p{0.15\linewidth} p{0.35\linewidth}}
    \toprule
    \rowcolor{tableheader}
    \textcolor{white}{\textbf{Risk ID}} & \textcolor{white}{\textbf{Risk Name}} & \textcolor{white}{\textbf{Severity}} & \textcolor{white}{\textbf{Description}} \\
    \midrule
    RISK-001 & Critical MFA Gaps & \textbf{\textcolor{red}{Critical}} & Lack of MFA on email and sensitive data systems allows for account takeover via credential theft, a common attack vector. \\
    \addlinespace
    RISK-002 & Outdated Web Server Software & \textbf{\textcolor{orange}{High}} & The Nginx server (v1.18.0) is exposed to publicly known vulnerabilities, which could lead to a server compromise or data breach. \\
    \addlinespace
    RISK-003 & Deficient Security Policies \& Training & \textbf{\textcolor{orange}{High}} & The absence of an Acceptable Use Policy and annual training increases the risk of insider threats and successful social engineering attacks. \\
    \bottomrule
\end{tabular}
\end{table}

% --- RECOMMENDATIONS ---
\section{Recommendations}
\label{sec:recommendations}
The following actions are recommended to mitigate the identified risks.

\subsection{RISK-001: Remediate Critical MFA Gaps}
\begin{itemize}
    \item \textbf{Immediate Action:} Procure and implement an MFA solution for all user accounts.
    \item \textbf{Priority 1:} Enforce MFA for access to all email accounts (e.g., Office 365, Google Workspace).
    \item \textbf{Priority 2:} Enforce MFA for access to all systems containing sensitive or confidential data.
\end{itemize}

\subsection{RISK-002: Upgrade Outdated Web Server Software}
\begin{itemize}
    \item \textbf{Immediate Action:} Plan and execute an upgrade of the Nginx server on host \texttt{192.168.10.5} to the latest stable version.
    \item \textbf{Long-Term Action:} Implement a formal patch management policy. This policy should mandate regular scanning for outdated software and a defined process for testing and deploying security patches in a timely manner.
\end{itemize}

\subsection{RISK-003: Establish Security Policies \& Training Program}
\begin{itemize}
    \item \textbf{Immediate Action:} Develop and ratify a formal Acceptable Use Policy (AUP) that all employees must read and acknowledge. This policy should define the rules for using company IT assets.
    \item \textbf{Long-Term Action:} Establish a mandatory, annual security awareness training program for all employees. This program should cover key topics such as phishing, password security, and data handling.
\end{itemize}

\end{document}
```