```latex
\documentclass[12pt]{article}

% --- PACKAGES ---
\usepackage[margin=1in]{geometry} % Set page margins
\usepackage{pifont}               % For checkmarks and crosses (dingbats)
\usepackage{booktabs}             % For professional-looking tables
\usepackage{xcolor}               % For colors
\usepackage{hyperref}             % For hyperlinks
\usepackage{url}                  % For URL formatting
\usepackage{seqsplit}             % For splitting long strings in texttt
\usepackage{graphicx}             % For logos, if needed
\usepackage{fancyhdr}             % For headers and footers

% --- DOCUMENT METADATA & HYPERREF SETUP ---
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analyst},
    pdfsubject={Security Analysis},
    pdfkeywords={Security, Risk, Assessment, Nmap, Vulnerability}
}

% --- DEFINE COLORS ---
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
\definecolor{darkorange}{rgb}{0.8, 0.33, 0.0}
\definecolor{darkgreen}{rgb}{0.0, 0.39, 0.0}

% --- CUSTOM COMMANDS ---
\newcommand{\yes}{\ding{51}}
\newcommand{\no}{\ding{55}}
\newcommand{\reportdate}{\today}

% --- PAGE STYLE ---
\pagestyle{fancy}
\fancyhf{}
\lhead{Cybersecurity Posture Assessment}
\rhead{Confidential}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- BEGIN DOCUMENT ---
\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{2cm}
    \Huge \textbf{Cybersecurity Posture Assessment Report}
    \vspace{1.5cm}
    \Large \textbf{Prepared for:} \\
    \vspace{0.5cm}
    \huge Urban Jungle Planning
    \vfill
    \large \textbf{Date of Report:} \reportdate \\
    \vspace{0.5cm}
    \large \textbf{Generated By:} \\
    \vspace{0.2cm}
    Expert Cybersecurity Analyst
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section*{1.0 Executive Summary}

This report provides a comprehensive cybersecurity posture assessment for Urban Jungle Planning, based on an analysis of network scan data, organizational security controls, and pre-existing risk information. The assessment reveals several critical and high-risk vulnerabilities that require immediate attention to mitigate the potential for significant security incidents.

The most critical findings include a publicly exposed and outdated MySQL database service, which is no longer receiving security updates, creating a severe risk of data breach. This technical vulnerability is compounded by critical gaps in organizational security controls, specifically the lack of Multi-Factor Authentication (MFA) for email access and the absence of a mandatory annual security awareness training program for all employees.

These deficiencies create multiple attack vectors that could be exploited by malicious actors, leading to unauthorized access, data exfiltration, or ransomware events. This report outlines the identified risks in detail and provides a series of actionable recommendations to strengthen the organization's security posture and reduce its attack surface.

% --- ORGANIZATIONAL INFORMATION ---
\section*{2.0 Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & Urban Jungle Planning \\
    Email Domain & \texttt{UrbanJunglePlanning.com} \\
    Website Domain & \url{www.UrbanJunglePlanning.com} \\
    External IP Address & \texttt{96.191.205.92} \\
    \bottomrule
\end{tabular}

% --- SECURITY CONTROL REVIEW ---
\section*{3.0 Security Control Review}

A review of the organization's security controls was conducted via a questionnaire. The results highlight significant gaps in identity management and security awareness, which are foundational pillars of a robust security program. "No" answers indicate areas of high risk that must be addressed.

\begin{tabular}{@{}p{0.7\textwidth}c}
    \toprule
    \textbf{Control Question} & \textbf{Status} \\
    \midrule
    Do you require MFA to access email? & \textcolor{darkred}{\no} \\
    Do you require MFA to log into computers? & \textcolor{darkgreen}{\yes} \\
    Do you require MFA to access sensitive data systems? & \textcolor{darkgreen}{\yes} \\
    Does your organization have an employee acceptable use policy? & \textcolor{darkgreen}{\yes} \\
    Does your organization do security awareness training for new employees? & \textcolor{darkgreen}{\yes} \\
    Does your organization do security awareness training for all employees at least once per year? & \textcolor{darkred}{\no} \\
    \bottomrule
\end{tabular}

% --- TECHNICAL SCAN RESULTS ---
\section*{4.0 Technical Scan Results}

An external network scan was performed to identify open ports and exposed services. The scan identified a critical exposure related to a database service.

\subsection*{4.1 Scan Details}
\begin{tabular}{@{}ll}
    \toprule
    \textbf{Parameter} & \textbf{Value} \\
    \midrule
    Target IP & \texttt{172.16.50.20} \\
    Scanner & Nmap \\
    \bottomrule
\end{tabular}

\subsection*{4.2 Open Ports and Services}
The scan revealed the following open port:

\begin{tabular}{@{}lllll}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
    \midrule
    3306/TCP & Open & mysql & MySQL & \textbf{5.7.33} \\
    \bottomrule
\end{tabular}

\subsection*{4.3 Technical Analysis}
The scan confirms that a MySQL database on port 3306 is directly exposed to the network. The identified version, \textbf{MySQL 5.7.33}, is a significant concern. MySQL version 5.7 reached its official \textbf{End of Life (EOL) in October 2023}. This means it no longer receives security patches or updates from the vendor, leaving it perpetually vulnerable to any newly discovered exploits. An exposed, EOL database service is a critical risk and a prime target for attackers.

% --- CONSOLIDATED RISK ASSESSMENT ---
\section*{5.0 Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list of security risks.

\begin{tabular}{@{}p{0.25\textwidth}p{0.5\textwidth}p{0.15\textwidth}}
    \toprule
    \textbf{Risk Title} & \textbf{Description} & \textbf{Severity} \\
    \midrule
    \textbf{Exposed \& Outdated Database Service} & A MySQL database (v5.7.33) is exposed on port 3306. This version is End of Life (EOL) and no longer receives security updates, making it highly susceptible to exploitation. This confirms and elevates the pre-existing "Database Exposure" risk. & \textbf{Critical} \\
    \addlinespace
    \textbf{Lack of MFA on Email} & Email accounts, a primary target for phishing and account takeover, are not protected by Multi-Factor Authentication. A compromised email account can lead to widespread system access and data breaches. & \textbf{Critical} \\
    \addlinespace
    \textbf{Insufficient Security Awareness Training} & The absence of mandatory annual security training for all employees increases the organization's susceptibility to phishing, social engineering, and other human-targeted attacks. & \textbf{High} \\
    \bottomrule
\end{tabular}

% --- ACTIONABLE RECOMMENDATIONS ---
\section*{6.0 Actionable Recommendations}

The following actions are recommended to mitigate the identified risks. Recommendations are prioritized based on severity.

\subsection*{6.1 Critical Priority Recommendations}
\begin{enumerate}
    \item \textbf{Remediate Exposed Database Service (Risk: Exposed \& Outdated Database):}
    \begin{itemize}
        \item \textbf{Immediate Action:} Implement strict firewall rules to block all public access to TCP port 3306. Access should only be permitted from trusted internal IP addresses.
        \item \textbf{Short-Term Action:} Plan and execute an upgrade of the MySQL 5.7 database to a currently supported version (e.g., MySQL 8.0 or later) to ensure it receives security patches.
        \item \textbf{Long-Term Strategy:} For any required remote access, implement a Virtual Private Network (VPN) solution. This ensures that all connections to the database are encrypted and authenticated.
    \end{itemize}

    \item \textbf{Enforce MFA on All Email Accounts (Risk: Lack of MFA on Email):}
    \begin{itemize}
        \item \textbf{Immediate Action:} Enable and enforce Multi-Factor Authentication for all user accounts across the email system (e.g., Microsoft 365, Google Workspace). This is the single most effective control to prevent unauthorized account access.
    \end{itemize}
\end{enumerate}

\subsection*{6.2 High Priority Recommendations}
\begin{enumerate}
    \setcounter{enumi}{2} % Continue numbering from previous list
    \item \textbf{Implement Annual Security Training (Risk: Insufficient Security Awareness):}
    \begin{itemize}
        \item \textbf{Short-Term Action:} Procure and deploy a security awareness training platform. Enroll all employees in a mandatory annual training program covering key topics such as phishing, password security, and acceptable use.
    \end{itemize}
\end{enumerate}

\end{document}
```