```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and metadata
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Document Metadata and Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Report},
    pdfauthor={Cybersecurity Analyst},
    pdfsubject={Security Assessment},
    pdfkeywords={Cybersecurity, Risk, Analysis},
    bookmarks=true
}

% Define checkmark and cross symbols
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Cybersecurity Posture Report}}
\rhead{\textbf{Binary Star}}
\cfoot{\thepage}

% --- START OF DOCUMENT ---
\begin{document}

\begin{center}
    \vspace*{1cm}
    {\Huge \textbf{Cybersecurity Posture Report}}
    \vspace{0.5cm}
    
    {\Large \textbf{Prepared for: Binary Star}}
    \vspace{1.5cm}
    
    \textbf{Date of Report:} \today \\
    \textbf{Author:} Cybersecurity Analyst
    \vspace{2cm}
    
    \rule{\linewidth}{0.5mm}
    \vspace{0.5cm}
    {\large \textit{Confidential Assessment}}
    \vspace{0.5cm}
    \rule{\linewidth}{0.5mm}
\end{center}

\newpage

\tableofcontents

\newpage

\section*{1. Executive Summary}

This report provides a comprehensive analysis of the cybersecurity posture for \textbf{Binary Star}, based on a recent network scan, a review of organizational security controls, and an assessment of known risks.

The analysis reveals several \textbf{critical and high-risk vulnerabilities} that require immediate attention. The most significant findings include:
\begin{itemize}
    \item \textbf{Complete Lack of Multi-Factor Authentication (MFA):} The absence of MFA for email, computer logins, and sensitive data systems exposes the organization to a high risk of account compromise through phishing and credential theft.
    \item \textbf{Unencrypted Web Communications:} The external network scan identified a web server operating over unencrypted HTTP (Port 80). This allows for the potential interception of sensitive data transmitted to and from the server.
    \item \textbf{Significant Policy and Training Gaps:} The organization lacks a formal Acceptable Use Policy and does not provide security awareness training to new employees, creating a culture where security best practices may be unknown or ignored.
\end{itemize}

While the provided list of current risks was determined to be invalid during analysis, the combination of technical and procedural weaknesses identified presents a clear and present danger to the organization's data, operations, and reputation. Immediate remediation of the issues outlined in this report is strongly recommended.

\section*{2. Organizational Information}

The following details were provided for the assessment. This information is used to establish the context and scope of the review.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & Binary Star \\
    Email Domain & \texttt{BinaryStar.net} \\
    Website Domain & \url{www.BinaryStar.net} \\
    External IP Address & \texttt{47.92.79.52} \\
    \bottomrule
\end{tabular}

\section*{3. Security Control Review}

A questionnaire was conducted to evaluate the implementation of fundamental security controls. The results indicate major gaps in identity and access management and employee security awareness. Answers marked with a red \xmark\ represent a deviation from security best practices and introduce significant risk.

\begin{center}
\begin{tabular}{p{0.75\linewidth} c}
    \toprule
    \textbf{Control Question} & \textbf{Response} \\
    \midrule
    Do you require MFA to access email? & \textcolor{red}{\xmark} \\
    Do you require MFA to log into computers? & \textcolor{red}{\xmark} \\
    Do you require MFA to access sensitive data systems? & \textcolor{red}{\xmark} \\
    Does your organization have an employee acceptable use policy? & \textcolor{red}{\xmark} \\
    Does your organization do security awareness training for new employees? & \textcolor{red}{\xmark} \\
    Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\cmark} \\
    \bottomrule
\end{tabular}
\end{center}

\subsection*{Analysis of Controls}
The lack of MFA across all critical access points (email, endpoints, data systems) is a \textbf{critical deficiency}. A single compromised password could grant an attacker widespread access. Furthermore, the absence of an Acceptable Use Policy and security training for new hires creates an environment where employees are more likely to engage in risky behavior, unaware of their security responsibilities.

\section*{4. Technical Scan Results}

An external network scan was performed to identify open ports and services exposed to the internet.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.0.1}
    \item \textbf{Scan Tool:} Nmap
\end{itemize}

\subsection*{Open Ports Discovered}
The following table details the ports found to be open and accessible from the internet.

\begin{center}
\begin{tabular}{c c p{0.6\linewidth}}
    \toprule
    \textbf{Port} & \textbf{Protocol} & \textbf{Inferred Service \& Analysis} \\
    \midrule
    80 & TCP & \textbf{HTTP (Hypertext Transfer Protocol).} This port is used for unencrypted web traffic. Exposing a web service over HTTP is a high-risk configuration, as any data exchanged, including potential login credentials or sensitive information, is transmitted in cleartext and can be easily intercepted. The industry standard is to use HTTPS (Port 443) with TLS encryption. \\
    \bottomrule
\end{tabular}
\end{center}

\section*{5. Consolidated Risk Assessment}
Based on the correlation of the security control review and technical scan results, the following key risks have been identified. The risk data provided in \texttt{Input\_3\_Current\_Risks\_JSON} was found to be anomalous and has been excluded in favor of this direct analysis.

\begin{center}
\begin{tabular}{p{0.2\linewidth} p{0.15\linewidth} p{0.55\linewidth}}
    \toprule
    \textbf{Risk Title} & \textbf{Severity} & \textbf{Overview} \\
    \midrule
    \textbf{Lack of MFA} & \textbf{Critical} & The absence of a secondary authentication factor for email, endpoints, and data systems makes user accounts highly susceptible to takeover via phishing, credential stuffing, or password spraying attacks. \\
    \addlinespace
    \textbf{Unencrypted Web Traffic} & \textbf{High} & The active HTTP service on port 80 transmits data in cleartext. This exposes user credentials and sensitive session information to man-in-the-middle (MitM) attacks and passive eavesdropping. \\
    \addlinespace
    \textbf{Inadequate Security Policies \& Training} & \textbf{High} & The lack of an Acceptable Use Policy and onboarding security training increases the likelihood of human error, policy violations, and successful social engineering attacks against new employees. \\
    \bottomrule
\end{tabular}
\end{center}

\section*{6. Recommendations}

To mitigate the identified risks and improve the overall security posture of \textbf{Binary Star}, the following actions are recommended, prioritized by urgency.

\subsection*{Immediate Actions (To Be Completed Within 7 Days)}
\begin{enumerate}
    \item \textbf{Enforce MFA Everywhere:} Immediately enable and enforce MFA for all users on all critical systems, starting with email (e.g., Office 365, Google Workspace), VPN access, and any application handling sensitive data.
    \item \textbf{Disable HTTP Access:} Reconfigure the web server at \texttt{172.16.0.1} to use HTTPS exclusively. Obtain a valid TLS/SSL certificate and implement a permanent (301) redirect for all traffic from HTTP to HTTPS.
\end{enumerate}

\subsection*{Short-Term Actions (To Be Completed Within 30 Days)}
\begin{enumerate}
    \item \textbf{Develop an Acceptable Use Policy (AUP):} Draft and ratify a formal AUP that clearly defines the rules and responsibilities for all employees when using company technology and data. Ensure all employees read and acknowledge the policy.
    \item \textbf{Implement Onboarding Security Training:} Create a mandatory security awareness training module for all new hires. This training should be part of the onboarding process and cover topics such as phishing, password hygiene, and the new AUP.
\end{enumerate}

\subsection*{Strategic Recommendations}
\begin{enumerate}
    \item \textbf{Establish a Vulnerability Management Program:} Implement a schedule for regular, comprehensive, and authenticated vulnerability scans of all internal and external assets to proactively identify and remediate software vulnerabilities and misconfigurations.
    \item \textbf{Conduct a Full Risk Assessment:} Engage in a broader risk assessment to identify, analyze, and evaluate risks across the entire organization, not just those covered by this targeted review.
\end{enumerate}

\end{document}
```