```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry} % Set page margins
\usepackage{pifont}               % For checkmarks and crosses (\ding)
\usepackage{booktabs}             % For professional-looking tables
\usepackage{hyperref}             % For hyperlinks and document metadata
\usepackage{url}                  % For formatting URLs
\usepackage{seqsplit}             % To split long monospaced strings
\usepackage{xcolor}               % For coloring text
\usepackage{graphicx}             % For including logos (optional)

% --- Document Metadata and Hyperlink Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analysis Division},
    pdfsubject={Security Assessment},
    pdfkeywords={Cybersecurity, Nmap, Risk, Assessment},
    bookmarks=true,
    pdfpagemode=FullScreen,
}

% --- Custom Commands and Colors ---
\newcommand{\yes}{\ding{51}} % Green checkmark
\newcommand{\no}{\ding{55}}  % Red cross
\definecolor{severityhigh}{HTML}{d9534f}
\definecolor{severitymedium}{HTML}{f0ad4e}
\definecolor{severitylow}{HTML}{5cb85c}

% --- Document Start ---
\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge\textbf{Cybersecurity Posture Assessment Report}
    \vspace{1.5cm}
    \Large
    \textbf{Prepared for:}\\
    \vspace{0.5cm}
    \textbf{Astraeus Aerospace}
    \vspace{2.5cm}
    \large
    \textbf{Analysis Date:} \today \\
    \vspace{0.5cm}
    \textbf{Report ID:} CYBER-2024-08A
    \vfill
    \large
    \textbf{Generated by:}\\
    Cybersecurity Analysis Division
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report provides a comprehensive cybersecurity posture assessment for Astraeus Aerospace, based on network scans, organizational data, and a review of existing risks. The analysis reveals several critical and high-risk security gaps that require immediate attention.

The primary findings indicate a direct, high-risk exposure of a sensitive database to the network. A technical scan confirmed that a MySQL database server is running an outdated and unsupported version (\textbf{5.7.33}), which no longer receives security patches. This technical vulnerability is critically compounded by an organizational policy gap: Multi-Factor Authentication (MFA) is not required for accessing sensitive data systems.

The combination of an exposed, unpatched database and the lack of mandatory MFA creates a significant risk of data breach. An attacker could exploit known vulnerabilities in the database software or use compromised credentials to gain direct access to potentially sensitive information without being challenged by a second authentication factor.

Immediate remediation should focus on restricting network access to the database and enforcing MFA on all sensitive systems. A plan to upgrade the outdated database software is also a high-priority recommendation.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided by the client and used as a baseline for this assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \textbf{Astraeus Aerospace} \\
    Email Domain & \texttt{AstraeusAerospace.com} \\
    Website Domain & \url{www.AstraeusAerospace.com} \\
    External IP & \texttt{164.148.71.222} \\
    \bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a standardized questionnaire. The responses highlight a critical gap in the access control policy for sensitive systems.

\begin{table}[h!]
\centering
\caption{Security Questionnaire Responses}
\begin{tabular}{@{}p{0.8\linewidth}c@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} \\
    \midrule
    Do you require MFA to access email? & \yes \\
    Do you require MFA to log into computers? & \yes \\
    \textbf{Do you require MFA to access sensitive data systems?} & \textcolor{red}{\no} \\
    Does your organization have an employee acceptable use policy? & \yes \\
    Does your organization do security awareness training for new employees? & \yes \\
    Does your organization do security awareness training for all employees at least once per year? & \yes \\
    \bottomrule
\end{tabular}
\end{table}

\paragraph{Analysis:} The failure to enforce Multi-Factor Authentication (MFA) on sensitive data systems represents a critical security weakness. While MFA is correctly applied to email and computer logins, its absence on high-value assets like databases or file servers means that a single compromised password could lead directly to a significant data breach. This gap is particularly concerning given the technical findings in the following section.

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify exposed services and potential vulnerabilities.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.50.20}
    \item \textbf{Scan Status:} Host is up.
\end{itemize}

The following open ports and services were discovered:

\begin{table}[h!]
\centering
\caption{Open Port Scan Findings}
\begin{tabular}{@{}lllll@{}}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
    \midrule
    3306/tcp & open & mysql & MySQL & 5.7.33 \\
    \bottomrule
\end{tabular}
\end{table}

\paragraph{Analysis:} The scan confirms that port \textbf{3306}, the default port for MySQL, is open to the network. This directly exposes the database service to potential attackers. Furthermore, the identified version, \textbf{MySQL 5.7.33}, reached its official End-of-Life (EOL) in October 2023. This means it no longer receives security updates from the vendor, and any newly discovered vulnerabilities will remain unpatched, posing a severe and escalating risk to the data it contains.

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
By correlating the organizational, technical, and pre-existing risk data, we have identified the following key risks to Astraeus Aerospace.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{@{}p{0.25\linewidth}p{0.1\linewidth}p{0.55\linewidth}@{}}
    \toprule
    \textbf{Risk Name} & \textbf{Severity} & \textbf{Description \& Impact} \\
    \midrule
    \textbf{Lack of MFA for Sensitive Systems} & \textcolor{severityhigh}{\textbf{Critical}} & The absence of MFA on critical systems means a compromised password is all an attacker needs to access sensitive data. This significantly increases the likelihood and impact of a data breach. \\
    \addlinespace
    \textbf{Exposed \& Outdated Database} & \textcolor{severityhigh}{\textbf{High}} & An unsupported MySQL database (v5.7.33, CVSS 7.5) is directly exposed. It is highly susceptible to known exploits and brute-force attacks. This could lead to data theft, manipulation, or service disruption. \\
    \bottomrule
\end{tabular}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}
The following prioritized actions are recommended to mitigate the identified risks and improve the overall security posture of Astraeus Aerospace.

\subsection{Immediate Priority (Remediate within 72 hours)}
\begin{enumerate}
    \item \textbf{Restrict Database Access:} Immediately apply firewall rules to block all public access to port 3306 on the server at \texttt{172.16.50.20}. Access should be restricted to a whitelist of trusted internal IP addresses only.
    \item \textbf{Enforce MFA on Sensitive Systems:} Begin immediate implementation of MFA on all systems classified as sensitive, with the highest priority on database management interfaces and administrative portals.
\end{enumerate}

\subsection{High Priority (Remediate within 30 days)}
\begin{enumerate}
    \item \textbf{Upgrade Database Software:} Develop and execute a plan to migrate the MySQL 5.7.33 database to a currently supported version (e.g., MySQL 8.x). This will ensure the system receives critical security patches.
    \item \textbf{Conduct a Vulnerability Scan:} Perform a comprehensive, authenticated vulnerability scan on the server at \texttt{172.16.50.20} to identify any other outdated software or misconfigurations.
\end{enumerate}

\subsection{Strategic Recommendations (Implement within 6 months)}
\begin{enumerate}
    \item \textbf{Implement a Secure Administration Zone:} Establish a long-term solution for database administration, such as a VPN or a secured bastion host (jump box), to eliminate any need for direct public exposure of critical services.
    \item \textbf{Review Data Classification Policy:} Review and enhance the organization's data classification policy to ensure all sensitive systems are correctly identified and that appropriate security controls (like MFA) are mandated accordingly.
\end{enumerate}

\end{document}
```