```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and ToC
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in \texttt

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analyst},
    pdfsubject={Security Analysis},
    pdfkeywords={Cybersecurity, Risk Assessment, Network Scan}
}

% Document Information
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analyst}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- Section 1: Executive Overview ---
\section{Executive Overview}
This report provides a comprehensive cybersecurity assessment for \textbf{Structure \& Form}, based on network scan data, organizational security controls, and pre-existing risk information. The analysis was conducted to identify security gaps, evaluate the current risk posture, and provide actionable recommendations for improvement.

The assessment reveals a mixed security posture. The organization has implemented positive security controls, such as requiring Multi-Factor Authentication (MFA) for sensitive data systems and conducting regular security awareness training for all employees. These measures are commendable and form a solid foundation for a security program.

However, several critical and high-risk vulnerabilities were identified that require immediate attention. Key findings include:
\begin{itemize}
    \item \textbf{Lack of MFA:} MFA is not enforced for accessing email or for logging into employee computers. This represents a significant vulnerability to credential theft and account takeover attacks.
    \item \textbf{Governance Gap:} The absence of an employee Acceptable Use Policy (AUP) creates ambiguity regarding the secure and appropriate use of company assets, increasing insider and operational risks.
    \item \textbf{Insecure Network Service:} A technical scan of the internal host \texttt{172.16.0.1} discovered an open port 80 (HTTP), indicating that data is likely being transmitted in cleartext. This exposes the organization to eavesdropping and man-in-the-middle attacks.
\end{itemize}

This report details these findings and concludes with prioritized recommendations to mitigate the identified risks and strengthen the overall security posture of \textbf{Structure \& Form}.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & \textbf{Structure \& Form} \\
    Email Domain & \texttt{StructureForm.org} \\
    Website Domain & \url{www.StructureForm.org} \\
    External IP Address & \texttt{81.124.125.166} \\
    \bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a questionnaire. The responses indicate foundational gaps in access control and policy governance. A green checkmark (\ding{51}) indicates a positive control, while a red cross (\ding{55}) highlights a security gap.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Results}
\begin{tabular}{@{}lc}
    \toprule
    \textbf{Control Question} & \textbf{Status} \\
    \midrule
    Do you require MFA to access email? & \ding{55} \\
    Do you require MFA to log into computers? & \ding{55} \\
    Do you require MFA to access sensitive data systems? & \ding{51} \\
    Does your organization have an employee acceptable use policy? & \ding{55} \\
    Does your organization do security awareness training for new employees? & \ding{51} \\
    Does your organization do security awareness training for all employees at least once per year? & \ding{51} \\
    \bottomrule
\end{tabular}
\end{table}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An Nmap scan was performed on the specified target to identify open ports and running services. The scan data provided was minimal but revealed a significant finding.

\subsection{Target: \texttt{172.16.0.1}}
The host was found to be online and responsive. The following open port was identified:

\begin{table}[h!]
\centering
\caption{Open Ports on \texttt{172.16.0.1}}
\begin{tabular}{@{}llll}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Analysis} \\
    \midrule
    80/tcp & Open & HTTP & Unencrypted web traffic. High risk. \\
    \bottomrule
\end{tabular}
\end{table}

\textbf{Note:} Detailed service, product, and version information was not available in the provided scan data. The presence of an open port 80 strongly implies a web server is running and is not configured to redirect to or use HTTPS, exposing all communications to and from the server to interception.

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes the findings from the security control review and the technical scan into a prioritized list of risks. The malicious risk entry from the input data has been disregarded as invalid.

\begin{table}[h!]
\centering
\caption{Identified Security Risks}
\begin{tabular}{@{}p{0.3\linewidth}p{0.5\linewidth}l}
    \toprule
    \textbf{Risk Title} & \textbf{Overview} & \textbf{Severity} \\
    \midrule
    \textbf{Lack of MFA on Core Systems} & Email and computer endpoints are protected only by passwords. A single compromised credential could lead to a full account takeover and unauthorized network access. & \textbf{High} \\
    \addlinespace
    \textbf{Missing Acceptable Use Policy (AUP)} & Without a formal AUP, there is no enforceable policy governing employee use of IT assets. This increases the risk of misuse, data leakage, and legal liability. & \textbf{High} \\
    \addlinespace
    \textbf{Unencrypted Web Traffic (HTTP)} & The web server at \texttt{172.16.0.1} uses HTTP, transmitting data (including potential credentials or sensitive information) in cleartext over the network. & \textbf{High} \\
    \bottomrule
\end{tabular}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks and improve the overall security posture of the organization. Recommendations are prioritized based on severity and impact.

\subsection{Priority 1: Immediate Actions (0-30 Days)}
\begin{enumerate}
    \item \textbf{Enforce MFA on Email and Endpoints:}
    \begin{itemize}
        \item \textbf{Action:} Immediately enable and enforce MFA for all user accounts on the email system (e.g., Microsoft 365, Google Workspace) and for all computer logins (e.g., via Windows Hello for Business, Duo, or a similar solution).
        \item \textbf{Impact:} Drastically reduces the risk of account takeovers from compromised credentials.
    \end{itemize}
    \item \textbf{Secure Internal Web Server:}
    \begin{itemize}
        \item \textbf{Action:} For the server at \texttt{172.16.0.1}, obtain and install a TLS/SSL certificate. Reconfigure the web service to use HTTPS (port 443) exclusively and disable or redirect all traffic from HTTP (port 80).
        \item \textbf{Impact:} Encrypts all data in transit, protecting it from eavesdropping and modification.
    \end{itemize}
\end{enumerate}

\subsection{Priority 2: Short-Term Actions (30-90 Days)}
\begin{enumerate}
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP):}
    \begin{itemize}
        \item \textbf{Action:} Draft a formal AUP that clearly defines the rules for using company computers, networks, and data. The policy should be reviewed by legal counsel, communicated to all employees, and formally acknowledged via signature.
        \item \textbf{Impact:} Establishes clear security expectations for all employees, reduces insider risk, and provides a basis for disciplinary action in case of violation.
    \end{itemize}
\end{enumerate}

\end{document}
```