```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and TOC
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings like IPs
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{datetime}

% --- Document Setup ---

% Define colors for the report
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
\definecolor{darkgreen}{rgb}{0.0, 0.39, 0.0}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue,
    pdftitle={Cybersecurity Posture Report},
    pdfauthor={Automated Security Analysis System},
    pdfsubject={Security Assessment},
    pdfkeywords={Cybersecurity, Risk, Assessment, Scan}
}

% Header and Footer setup
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Cybersecurity Posture Report}
\fancyhead[R]{Blue Horizon Initiative}
\fancyfoot[C]{\thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Helper Commands ---
\newcommand{\yes}{\ding{51}} % Checkmark
\newcommand{\no}{\ding{55}}  % Cross

% --- Document Start ---
\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{2cm}
    
    {\Huge \textbf{Cybersecurity Posture Report}\par}
    \vspace{1.5cm}
    
    {\Large \textbf{Prepared for:}\par}
    \vspace{0.5cm}
    {\Large Blue Horizon Initiative\par}
    
    \vfill
    
    {\large \textbf{Date of Report:}} \\
    {\large \today}
    
    \vspace{1cm}
    \rule{\textwidth}{0.4pt}
    \vspace{0.5cm}
    \textit{This report contains sensitive information and should be handled with care. Distribution is restricted to authorized personnel only.}
    
\end{titlepage}

\newpage

% --- Table of Contents ---
\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}

This report provides a cybersecurity assessment for Blue Horizon Initiative, synthesizing information from organizational questionnaires, network scans, and pre-existing risk data. The analysis reveals several critical and high-risk security gaps that require immediate attention.

The primary findings indicate significant weaknesses in fundamental security controls. The lack of Multi-Factor Authentication (MFA) for email and computer access, combined with the absence of a formal security awareness training program, exposes the organization to a high likelihood of account compromise through social engineering attacks like phishing.

Furthermore, a technical scan identified an externally accessible Secure Shell (SSH) service. While necessary for remote administration, an improperly secured SSH service is a common target for attackers. When correlated with weak identity and access controls, this creates a viable pathway for an external threat actor to gain internal network access.

The overall security posture is considered weak. This report outlines specific, actionable recommendations to mitigate the identified risks and strengthen the organization's defenses against common cyber threats. Priority should be given to implementing MFA and establishing a security training program.

\vspace{1cm}

% --- Section 2: Organizational Information ---
\section{Organizational Information}

The following details were provided for the assessment. This information is used to establish the context and scope of the review.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & Blue Horizon Initiative \\
Email Domain & \texttt{BlueHorizonInitiative.com} \\
Website Domain & \url{www.BlueHorizonInitiative.com} \\
External IP Address & \seqsplit{\texttt{126.163.227.13}} \\
Target IP Scanned & \seqsplit{\texttt{2001:db8::1}} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details}
\label{tab:org_info}
\end{table}

% --- Section 3: Security Control Review ---
\section{Security Control Review}

A review of the organization's security policies and controls was conducted via a questionnaire. The responses highlight significant gaps in foundational security practices.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.6\textwidth} c p{0.2\textwidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Analyst Note} \\ \midrule
Do you require MFA to access email? & \textcolor{darkred}{\no} & \textbf{Critical Gap.} Email is a primary target for phishing and account takeover. \\
\addlinespace
Do you require MFA to log into computers? & \textcolor{darkred}{\no} & \textbf{High Risk.} Lack of endpoint MFA allows lateral movement if credentials are stolen. \\
\addlinespace
Do you require MFA to access sensitive data systems? & \textcolor{darkgreen}{\yes} & Good Practice. Protects the most critical assets. \\
\addlinespace
Does your organization have an employee acceptable use policy? & \textcolor{darkgreen}{\yes} & Foundational. Sets clear expectations for employees. \\
\addlinespace
Does your organization do security awareness training for new employees? & \textcolor{darkred}{\no} & \textbf{High Risk.} New hires are often targeted and unaware of policies. \\
\addlinespace
Does your organization do security awareness training for all employees at least once per year? & \textcolor{darkred}{\no} & \textbf{Critical Gap.} Without regular training, staff are unprepared for evolving threats. \\ \bottomrule
\end{tabular}
\caption{Security Control Questionnaire Analysis}
\label{tab:controls}
\end{table}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed on the target IP address \seqsplit{\texttt{2001:db8::1}}. The scan identified the following open ports accessible from the public internet.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{Protocol} & \textbf{State} & \textbf{Service} & \textbf{Notes} \\ \midrule
22 & TCP & Open & ssh & Service inferred from port number. No version data was available. \\ \bottomrule
\end{tabular}
\caption{Open Ports on \seqsplit{\texttt{2001:db8::1}}}
\label{tab:scan_results}
\end{table}

\subsection*{Analysis of Technical Findings}
The presence of an open SSH port (22/TCP) is a significant finding. This service is used for remote administration and is a high-value target for attackers. Without further information, it is assumed to be exposed to the entire internet, making it susceptible to:
\begin{itemize}
    \item \textbf{Brute-force attacks:} Automated attempts to guess usernames and passwords.
    \item \textbf{Credential stuffing:} Using credentials stolen from other breaches.
    \item \textbf{Exploitation:} If the SSH server software is outdated, it may contain known vulnerabilities.
\end{itemize}
This finding, when combined with the lack of MFA and security training, elevates the risk of a successful compromise.

% --- Section 5: Risk Assessment ---
\section{Risk Assessment}

Based on the synthesis of organizational and technical data, the following key risks have been identified. The pre-existing risk register was empty, therefore all findings below are new.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.1\textwidth} p{0.25\textwidth} p{0.45\textwidth} p{0.1\textwidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\ \midrule
\textbf{R-01} & Lack of Multi-Factor Authentication (MFA) & The absence of MFA on email and computer logins makes user accounts highly vulnerable to takeover from stolen credentials. & \textbf{Critical} \\
\addlinespace
\textbf{R-02} & Inadequate Security Awareness Training & No security training for new or existing employees leaves the organization susceptible to social engineering, phishing, and malware infections. & \textbf{High} \\
\addlinespace
\textbf{R-03} & Exposed SSH Management Service & Port 22 (SSH) is open to the internet, creating a direct target for brute-force attacks and potential exploitation, which could lead to unauthorized network access. & \textbf{High} \\ \bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\label{tab:risks}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}

The following actions are recommended to mitigate the identified risks and improve the overall security posture of Blue Horizon Initiative.

\subsection*{Immediate Priority (Critical Risks)}
\begin{itemize}
    \item \textbf{R-01 | Implement MFA for Email:} Immediately enforce MFA for all users accessing the email system (\texttt{BlueHorizonInitiative.com}). This is the single most effective control to prevent email account takeovers.
\end{itemize}

\subsection*{High Priority}
\begin{itemize}
    \item \textbf{R-02 | Establish Security Awareness Training:}
    \begin{itemize}
        \item Develop and implement a mandatory security awareness training module for all new employees as part of their onboarding process.
        \item Schedule and conduct annual security awareness training for all staff to keep them informed about current threats.
    \end{itemize}
    \item \textbf{R-03 | Secure the SSH Service:}
    \begin{itemize}
        \item Review the business justification for exposing SSH to the internet. If not essential, disable access externally.
        \item If required, restrict access to a whitelist of trusted IP addresses.
        \item Enforce public key authentication and disable password-based logins for SSH.
    \end{itemize}
    \item \textbf{R-01 | Implement MFA for Endpoints:} Deploy MFA for logging into all company-managed computers (desktops and laptops) to protect against unauthorized local access.
\end{itemize}

\subsection*{Medium Priority}
\begin{itemize}
    \item \textbf{R-03 | Conduct Vulnerability Scanning:} Perform an authenticated vulnerability scan on the system at \seqsplit{\texttt{2001:db8::1}} to identify the exact SSH version and check for any known vulnerabilities or misconfigurations.
\end{itemize}

\end{document}
```