```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For check and cross marks
\usepackage{booktabs} % For professional tables
\usepackage[hidelinks]{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long text strings
\usepackage{xcolor} % For colors in the risk table
\usepackage{graphicx} % For potential logos or graphics
\usepackage{fancyhdr} % For headers and footers

% --- Document Setup ---

% Define colors for risk levels
\definecolor{criticalrisk}{HTML}{D32F2F}
\definecolor{highrisk}{HTML}{F57C00}
\definecolor{mediumrisk}{HTML}{FBC02D}
\definecolor{lowrisk}{HTML}{388E3C}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Cybersecurity Postfumre Assessment}
\fancyhead[R]{Summit Peak Partners}
\fancyfoot[C]{\thepage}

% --- Document Start ---

\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge\textbf{Cybersecurity Posture Assessment Report}
    \vspace{1.5cm}
    \Large
    \textbf{Prepared for:}\\
    Summit Peak Partners
    \vspace{2cm}
    \large
    \textbf{Date of Report:}\\
    \today
    \vfill
    \large
    \textit{This report contains sensitive information and should be handled with care.}
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report provides a comprehensive assessment of the cybersecurity posture for \textbf{Summit Peak Partners}. The analysis is based on a correlation of network scan data, a security controls questionnaire, and a review of pre-existing risks.

The assessment identified several critical and high-risk findings that require immediate attention. Key among these is the external exposure of a database service (\texttt{MySQL 5.7.33}) which is confirmed to be an End-of-Life (EOL) product, meaning it no longer receives security updates. This technical vulnerability is severely compounded by systemic gaps in foundational security controls, most notably a complete lack of Multi-Factor Authentication (MFA) across email, workstations, and sensitive systems.

Furthermore, the absence of an acceptable use policy and mandatory annual security training for all employees creates a permissive environment for human error, which is a leading cause of security breaches.

Immediate remediation should focus on isolating the exposed database, implementing MFA on all critical accounts, and initiating a plan to upgrade the EOL software. Addressing these issues will significantly reduce the organization's risk profile and strengthen its defense against common cyber threats.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & Summit Peak Partners \\
    Email Domain & \texttt{SummitPeakPartners.org} \\
    Website Domain & \seqsplit{\url{www.SummitPeakPartners.org}} \\
    External IP Address & \texttt{214.11.113.99} \\
    \bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a questionnaire. The responses indicate significant gaps in fundamental security practices. A "No" response (\ding{55}) highlights a missing control that increases organizational risk.

\begin{tabular}{@{}p{8cm} c p{4cm}@{}}
    \toprule
    \textbf{Control Question} & \textbf{Response} & \textbf{Analyst Notes} \\
    \midrule
    Do you require MFA to access email? & \ding{55} & \textbf{Critical Gap.} Email is a primary target for account takeover. \\
    Do you require MFA to log into computers? & \ding{55} & \textbf{High Risk.} Lack of MFA allows for easier lateral movement if credentials are stolen. \\
    Do you require MFA to access sensitive data systems? & \ding{55} & \textbf{Critical Gap.} Direct, single-factor access to critical data is extremely risky. \\
    Does your organization have an employee acceptable use policy? & \ding{55} & \textbf{High Risk.} Lack of a formal policy leads to inconsistent security behavior. \\
    Does your organization do security awareness training for new employees? & \ding{51} & A positive control for onboarding. \\
    Does your organization do security awareness training for all employees at least once per year? & \ding{55} & \textbf{High Risk.} Security knowledge degrades; annual refreshers are essential. \\
    \bottomrule
\end{tabular}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify exposed services and potential vulnerabilities.

\subsection{Host: \texttt{172.16.50.20}}
The scan identified the following open port on the target system.

\begin{tabular}{@{}lllll@{}}
    \toprule
    \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
    \midrule
    3306/tcp & Open & mysql & MySQL & 5.7.33 \\
    \bottomrule
\end{tabular}

\subsubsection*{Analyst Finding: End-of-Life Software}
The detected version, \textbf{MySQL 5.7.33}, is a significant concern. MySQL version 5.7 reached its official End-of-Life (EOL) in October 2023. Systems running EOL software no longer receive security patches from the vendor, even for newly discovered critical vulnerabilities. This exposes the organization to a high risk of compromise from publicly known exploits.

% --- Section 5: Risk Assessment ---
\section{Risk Assessment}
The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data. Risks are prioritized by severity to guide remediation efforts.

\begin{tabular}{@{}p{4.5cm} p{1.8cm} p{7.5cm}@{}}
    \toprule
    \textbf{Risk Title} & \textbf{Severity} & \textbf{Description} \\
    \midrule
    \textbf{End-of-Life Database Software} & \colorbox{criticalrisk}{\color{white}\textbf{ Critical }} & The publicly accessible MySQL server is running version 5.7.33, which is End-of-Life and no longer receives security updates. This makes it a prime target for automated exploits. \\
    \addlinespace
    \textbf{Lack of Multi-Factor Authentication} & \colorbox{criticalrisk}{\color{white}\textbf{ Critical }} & MFA is not enforced on email, computers, or sensitive systems. This allows an attacker with stolen credentials to gain full access, bypassing a critical layer of defense. \\
    \addlinespace
    \textbf{Public Database Exposure} & \colorbox{highrisk}{\color{white}\textbf{ High }} & The MySQL database port (3306) is open to the network. This allows attackers to directly attempt to brute-force credentials or exploit vulnerabilities in the database software itself. \\
    \addlinespace
    \textbf{Insufficient Security Policies \& Training} & \colorbox{highrisk}{\color{white}\textbf{ High }} & The absence of an acceptable use policy and annual security training increases the likelihood of human error, such as falling for phishing attacks, leading to credential compromise. \\
    \bottomrule
\end{tabular}

% --- Section 6: Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks. They are prioritized into immediate, short-term, and long-term phases.

\subsection{Immediate Actions (Next 72 Hours)}
\begin{enumerate}
    \item \textbf{Isolate the Database Server:} Immediately apply firewall rules to restrict all access to port \texttt{3306} on host \texttt{172.16.50.20}. Access should only be permitted from specific, trusted internal IP addresses. Public access must be disabled.
    \item \textbf{Enforce MFA on Critical Systems:} Prioritize the deployment of MFA for all users on:
    \begin{itemize}
        \item Email accounts (e.g., Office 365, Google Workspace).
        \item All administrative accounts.
        \item Any systems identified as containing sensitive data.
    \end{itemize}
    \item \textbf{Initiate EOL Upgrade Plan:} Begin the formal planning process to migrate the MySQL 5.7 database to a currently supported version (e.g., MySQL 8.0 or later). This includes data backup, compatibility testing, and scheduling a migration window.
\end{enumerate}

\subsection{Short-Term Actions (Next 30-60 Days)}
\begin{enumerate}
    \item \textbf{Develop and Implement Policies:} Draft and ratify a formal Acceptable Use Policy (AUP) for all employees. Ensure every employee reads and acknowledges the policy.
    \item \textbf{Deploy Annual Security Training:} Procure and schedule mandatory annual security awareness training for all employees. Track completion to ensure 100\% compliance.
    \item \textbf{Expand MFA Deployment:} Continue the MFA rollout to include all user workstations and any remaining applications that support it.
\end{enumerate}

\subsection{Long-Term Strategic Actions (Next 6-12 Months)}
\begin{enumerate}
    \item \textbf{Implement Network Segmentation:} Review the network architecture to logically or physically segment critical systems (like databases) from the general user network. This contains the impact of a potential breach.
    \item \textbf{Establish a Vulnerability Management Program:} Implement a formal program that includes regular network scanning, patch management, and a defined process for remediating vulnerabilities based on risk.
    \item \textbf{Consider a VPN for Remote Access:} For any required external access to internal resources like the database, implement a Virtual Private Network (VPN) with MFA to provide a secure, encrypted tunnel.
\end{enumerate}

\end{document}
```