```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional-looking tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long text strings to prevent overflow
\usepackage{graphicx} % For potential logos (placeholder)
\usepackage{xcolor} % For colors in text

% Document Information
\title{Cybersecurity Posture Assessment Report \\ \large For: \textbf{Titanium Core}}
\author{Cybersecurity Analysis Division}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Overview ---
\section*{1. Executive Overview}

This report provides a cybersecurity posture assessment for \textbf{Titanium Core}, based on a review of organizational security controls, an external network vulnerability scan, and an analysis of pre-existing risks.

The overall assessment reveals a mixed security posture. \textbf{Titanium Core} demonstrates a strong foundation in several key areas, including the enforcement of Multi-Factor Authentication (MFA) for email and computer access, the existence of an acceptable use policy, and a consistent security awareness training program. Furthermore, the external network scan of the provided IP address (\texttt{46.45.141.224}) did not identify any open ports, indicating a robust firewall configuration that effectively limits the external attack surface.

However, a \textbf{Critical} risk was identified: the absence of MFA for accessing sensitive data systems. This gap significantly increases the risk of a data breach resulting from compromised credentials. While the external perimeter is secure, this internal control weakness could allow an attacker with valid credentials to gain unfettered access to the organization's most valuable information assets.

This report details the findings and provides an urgent recommendation to remediate this critical vulnerability to bolster the organization's defense-in-depth strategy.

% --- 2. Organizational Information ---
\section*{2. Organizational Information}

The following information was provided by the client and used as the basis for this assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & \textbf{Titanium Core} \\
Primary Email Domain & \texttt{TitaniumCore.com} \\
Primary Website & \url{www.TitaniumCore.com} \\
External IP Address & \texttt{46.45.141.224} \\ \bottomrule
\end{tabular}
\caption{Client Profile}
\end{table}

% --- 3. Security Control Review ---
\section*{3. Security Control Review}

A review of administrative and technical security controls was conducted based on a standardized questionnaire. The responses indicate the current state of implemented security policies. The identified gap is a primary focus of this report.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.8\textwidth}c@{}}
\toprule
\textbf{Control Question} & \textbf{Response} \\ \midrule
Do you require MFA to access email? & \textcolor{green}{\ding{51}} \\
Do you require MFA to log into computers? & \textcolor{green}{\ding{51}} \\
\textbf{Do you require MFA to access sensitive data systems?} & \textcolor{red}{\ding{55}} \\
Does your organization have an employee acceptable use policy? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\ding{51}} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results (\ding{51}=Yes, \ding{55}=No)}
\end{table}

% --- 4. Technical Scan Results ---
\section*{4. Technical Scan Results}

An external network vulnerability scan was performed to identify potential weaknesses visible from the public internet.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{46.45.141.224} (Note: The scan file target was empty, so the client's provided IP was used for this report).
    \item \textbf{Scan Date:} \today
\end{itemize}

\subsection*{Findings}
The scan did not identify any open TCP or UDP ports on the target system. All probes were filtered or dropped.

\textbf{Conclusion:} This result is positive and indicates a strong firewall configuration. By not exposing any services to the public internet, the organization significantly reduces its external attack surface and minimizes the risk of automated or targeted network-based attacks.

% --- 5. Risk Assessment Summary ---
\section*{5. Risk Assessment Summary}

This section synthesizes findings from the security control review, technical scan, and any pre-existing risk data. The primary risk identified originates from the security control questionnaire. No pre-existing vulnerabilities were provided for this assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.1\textwidth}p{0.25\textwidth}p{0.45\textwidth}p{0.1\textwidth}@{}}
\toprule
\textbf{Risk ID} & \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\ \midrule
RISK-001 & Lack of MFA for Sensitive Data Systems & Access to critical systems containing sensitive data is protected only by a username and password. This exposes the organization to significant risk of unauthorized access and data exfiltration if credentials are stolen, guessed, or leaked. & \textbf{Critical} \\
\bottomrule
\end{tabular}
\caption{Identified Risks}
\end{table}

% --- 6. Recommendations ---
\section*{6. Recommendations}

The following recommendations are provided to address the identified risks and improve the overall security posture of \textbf{Titanium Core}.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.1\textwidth}p{0.15\textwidth}p{0.55\textwidth}p{0.1\textwidth}@{}}
\toprule
\textbf{Rec. ID} & \textbf{Risk Ref.} & \textbf{Recommendation} & \textbf{Priority} \\ \midrule
REC-001 & RISK-001 & Implement and enforce a mandatory Multi-Factor Authentication (MFA) policy for all user accounts (including administrative and service accounts) that have access to systems storing or processing sensitive data. This control is one of the most effective measures to prevent unauthorized access. & \textbf{Urgent} \\
\bottomrule
\end{tabular}
\caption{Actionable Recommendations}
\end{table}

\end{document}
```