```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and references
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % To split long strings in tt font
\usepackage{xcolor} % For colors
\usepackage{graphicx} % For images, if needed

% Document Metadata
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analyst}
\date{\today}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% Define custom colors for severity
\definecolor{criticalred}{HTML}{990000}
\definecolor{highorange}{HTML}{E69138}
\definecolor{mediumyellow}{HTML}{F1C232}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Executive Summary}

This report provides a comprehensive analysis of the cybersecurity posture for \textbf{Oasis Wellness}, based on network scans, organizational data, and a review of existing risks. The assessment was conducted on \today.

The analysis reveals several critical-risk findings that require immediate attention. The most significant concerns are the complete absence of Multi-Factor Authentication (MFA) across all critical systems (email, computers, and sensitive data access) and the public exposure of a database server running an End-of-Life (EOL) version of MySQL (5.7.33).

The lack of MFA creates a substantial risk of account compromise, which could lead to unauthorized access and data breaches. This risk is severely amplified by the exposed MySQL database. An attacker who compromises a single set of credentials could potentially gain direct access to sensitive data without any secondary security checks. The database software itself is no longer receiving security updates, leaving it vulnerable to known exploits.

Immediate remediation should focus on implementing strict firewall rules to isolate the database and beginning a phased rollout of MFA, starting with email and sensitive systems. A plan to upgrade the unsupported database software is also a high-priority recommendation.

\section{Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Oasis Wellness} \\
Email Domain & \texttt{OasisWellness.org} \\
Website Domain & \texttt{www.OasisWellness.org} \\
External IP Address & \texttt{88.244.195.51} \\
\bottomrule
\end{tabular}

\section{Security Control Review}

A review of organizational security controls was conducted based on a standard questionnaire. The results indicate strong practices in policy and training but reveal critical gaps in technical access controls.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\begin{tabular}{@{}p{0.6\linewidth}cp{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Analyst Note} \\
\midrule
Do you require MFA to access email? & \textcolor{criticalred}{\ding{55}} & Critical Gap \\
Do you require MFA to log into computers? & \textcolor{criticalred}{\ding{55}} & Critical Gap \\
Do you require MFA to access sensitive data systems? & \textcolor{criticalred}{\ding{55}} & Critical Gap \\
Does your organization have an employee acceptable use policy? & \textcolor{green}{\ding{51}} & Good Practice \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} & Good Practice \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\ding{51}} & Good Practice \\
\bottomrule
\end{tabular}
\end{table}

The three "No" responses related to Multi-Factor Authentication represent a systemic failure in identity and access management. MFA is a foundational security control that protects against the majority of credential-based attacks. Its absence is a high-priority risk that undermines other security efforts.

\section{Technical Scan Results}

An external network scan was performed on the target system to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP:} \texttt{172.16.50.20}
    \item \textbf{Scan Date:} Not provided in scan data; report generated on \today.
\end{itemize}

\subsection{Open Ports and Services}
The scan identified one open port, which exposes a critical database service directly to the network.

\begin{table}[h!]
\centering
\caption{Identified Open Ports}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & Open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Analysis of Findings}
The primary finding is the exposure of a MySQL database on port 3306. Further investigation reveals a critical vulnerability:
\begin{itemize}
    \item \textbf{End-of-Life Software:} MySQL version 5.7 reached its official End of Life (EOL) in October 2023. This means it no longer receives security patches from the vendor, leaving it perpetually vulnerable to any newly discovered exploits.
    \item \textbf{Direct Exposure:} Exposing a database port directly to the network is a highly discouraged practice. It significantly increases the attack surface and makes the database a prime target for brute-force attacks, credential stuffing, and exploitation of known vulnerabilities.
\end{itemize}

\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{@{}p{0.25\linewidth}p{0.45\linewidth}p{0.2\linewidth}@{}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Lack of Multi-Factor Authentication (MFA)} & No MFA is enforced for email, computer, or sensitive system access, leaving accounts vulnerable to takeover via compromised credentials. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
\textbf{Exposed End-of-Life Database} & A MySQL 5.7.33 database (EOL) is exposed on port 3306. This combines the risk of an unpatchable service with direct network accessibility. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
\textbf{Database Exposure} & This pre-existing risk is confirmed by the technical scan. The MySQL port 3306 is open, allowing direct connection attempts from the network. & \textcolor{highorange}{\textbf{High}} \\
\bottomrule
\end{tabular}
\end{table}

\section{Recommendations}

The following actionable recommendations are provided to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection{Risk: Exposed End-of-Life Database (Critical)}

\begin{itemize}
    \item \textbf{Immediate Action (Containment):} Implement strict firewall rules to deny all access to TCP port 3306 from the public internet and internal network segments. Only allow connections from specific, authorized application server IP addresses. This immediately reduces the exposure.
    \item \textbf{Short-Term (Remediation):} Develop and execute a plan to upgrade the MySQL 5.7 instance to a currently supported version (e.g., MySQL 8.x). This is essential to ensure the system receives security patches.
    \item \textbf{Long-Term (Strategic):} Adopt a Zero Trust network model where databases are never directly exposed. Access should be brokered through a secure application layer or require a VPN with strict access controls for administrative purposes.
\end{itemize}

\subsection{Risk: Lack of Multi-Factor Authentication (Critical)}

\begin{itemize}
    \item \textbf{Immediate Action (High-Impact):} Procure and deploy an MFA solution for the email system (\texttt{OasisWellness.org}). As email is a primary target for phishing and account takeover, this is the most critical first step.
    \item \textbf{Short-Term (Expansion):} Extend the MFA requirement to all remote access solutions (e.g., VPN), privileged user accounts, and logins to sensitive data systems.
    \item \textbf{Long-Term (Comprehensive):} Establish a formal Identity and Access Management (IAM) policy that mandates MFA for all user accounts and services wherever technically feasible, including standard computer logins.
\end{itemize}

\end{document}
```