```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{pifont} % For checkmarks and crosses (\ding)
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and references
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{array}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analyst},
}

% Custom command for table cell formatting
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% Document Start
\begin{document}

% Title Page
\title{
    \vspace{2cm}
    \textbf{Cybersecurity Posture Assessment Report} \\
    \large \textit{Prepared for Golden Gate Gaming}
    \vspace{1cm}
}
\author{Cybersecurity Analyst}
\date{November 22, 2025}
\maketitle
\thispagestyle{empty}
\newpage

% Table of Contents
\tableofcontents
\newpage

% 1. Executive Summary
\section{Executive Summary}
This report provides a comprehensive cybersecurity assessment for Golden Gate Gaming, conducted on November 22, 2025. The analysis is based on a network vulnerability scan, a review of organizational security controls, and an evaluation of pre-existing risks.

The assessment reveals a mixed security posture. The organization demonstrates strong foundational controls, particularly in the mandatory use of Multi-Factor Authentication (MFA) across email, computer logins, and sensitive data systems. These measures significantly reduce the risk of unauthorized access through compromised credentials.

However, two critical areas of concern were identified that require immediate attention:
\begin{itemize}
    \item \textbf{Outdated Web Server Software:} The external-facing web server at \texttt{192.168.10.5} is running Nginx version 1.18.0, which is outdated and no longer receives security updates. This exposes the server to numerous publicly known vulnerabilities, posing a high risk of compromise.
    \item \textbf{Inadequate Security Training Cadence:} While new employees receive security awareness training, there is no program for mandatory, annual refresher training for all staff. This gap creates a significant human-element risk, as employees may not be aware of evolving threats like sophisticated phishing and social engineering tactics.
\end{itemize}

This report details these findings and provides actionable recommendations to mitigate the identified risks and enhance the overall security posture of Golden Gate Gaming.

% 2. Organizational Information
\section{Organizational Information}
The following information was provided for the assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name    & Golden Gate Gaming \\
Email Domain         & \seqsplit{\texttt{GoldenGateGaming.net}} \\
Website Domain       & \seqsplit{\url{www.GoldenGateGaming.net}} \\
External IP Address  & \seqsplit{\texttt{68.195.93.129}} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Data}
\label{tab:org_data}
\end{table}

% 3. Security Control Review
\section{Security Control Review}
A review of the organization's security controls was conducted via a standardized questionnaire. The results indicate a strong baseline but highlight a critical gap in ongoing employee training. A \textcolor{green}{\ding{51}} indicates a positive control is in place, while a \textcolor{red}{\ding{55}} indicates a potential gap.

\begin{table}[h!]
\centering
\begin{tabular}{@{}L{12cm}C{2cm}@{}}
\toprule
\textbf{Security Control Question} & \textbf{Status} \\ \midrule
Do you require MFA to access email? & \textcolor{green}{\ding{51}} \\
Do you require MFA to log into computers? & \textcolor{green}{\ding{51}} \\
Do you require MFA to access sensitive data systems? & \textcolor{green}{\ding{51}} \\
Does your organization have an employee acceptable use policy? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} \\
\textbf{Does your organization do security awareness training for all employees at least once per year?} & \textcolor{red}{\ding{55}} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results}
\label{tab:controls}
\end{table}

% 4. Technical Scan Results
\section{Technical Scan Results}
An external network scan was performed to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \seqsplit{\texttt{192.168.10.5}}
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

The scan identified one open port, which is running an outdated version of the Nginx web server software.

\begin{table}[h!]
\centering
\begin{tabular}{@{}llllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} & \textbf{Notes} \\ \midrule
443/tcp & open & https & nginx & 1.18.0 & \textbf{Outdated Version} \\ \bottomrule
\end{tabular}
\caption{Open Ports and Services on \texttt{192.168.10.5}}
\label{tab:scan_results}
\end{table}

% 5. Risk Assessment
\section{Risk Assessment}
Based on the analysis of security controls and technical scan data, the following risks have been identified. The pre-existing risk register (Input 3) was empty, so all listed risks are new findings from this assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.05\textwidth} p{0.3\textwidth} p{0.45\textwidth} p{0.1\textwidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\ \midrule
\textbf{R-01} & Outdated Web Server Software & The public-facing web server is running Nginx 1.18.0, a version with multiple known vulnerabilities (e.g., CVE-2021-23017). This could allow an attacker to cause a denial of service or execute arbitrary code. & \textbf{High} \\
\addlinespace
\textbf{R-02} & Lack of Annual Security Training & The absence of mandatory, recurring security training for all staff increases susceptibility to phishing, social engineering, and other human-targeted attacks. This weakens the overall security culture. & \textbf{High} \\ \bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\label{tab:risks}
\end{table}

% 6. Recommendations
\section{Recommendations}
To address the identified risks and improve the organization's security posture, the following actions are recommended.

\begin{enumerate}
    \item \textbf{Upgrade Outdated Nginx Server (Risk R-01):}
    \begin{itemize}
        \item \textbf{Action:} Plan and execute an upgrade of the Nginx server on host \seqsplit{\texttt{192.168.10.5}} from version 1.18.0 to the latest stable version.
        \item \textbf{Justification:} Upgrading patches known vulnerabilities, protecting the server and its data from compromise.
        \item \textbf{Timeline:} Immediate (within 30 days).
        \item \textbf{Additional Step:} Implement a formal patch management policy and schedule for all internet-facing systems to prevent future occurrences of this risk.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{Implement Annual Security Awareness Training (Risk R-02):}
    \begin{itemize}
        \item \textbf{Action:} Establish a mandatory security awareness training program that all employees must complete annually.
        \item \textbf{Justification:} Regular training ensures that employees' knowledge of cyber threats remains current, reinforcing their ability to act as a human firewall against attacks. Topics should include phishing identification, password hygiene, and incident reporting.
        \item \textbf{Timeline:} Within 90 days.
        \item \textbf{Additional Step:} Conduct periodic, unannounced phishing simulations to test and measure the effectiveness of the training program.
    \end{itemize}
\end{enumerate}

% 7. Conclusion
\section{Conclusion}
Golden Gate Gaming has established a solid security foundation with its comprehensive implementation of Multi-Factor Authentication. However, the organization's security is undermined by critical vulnerabilities in its technical and human layers. The use of outdated server software and the lack of recurring security training present clear and immediate risks.

By prioritizing the recommendations outlined in this report—specifically, upgrading the vulnerable Nginx server and instituting an annual security training program—Golden Gate Gaming can significantly reduce its attack surface and build a more resilient and secure operational environment.

\end{document}
```