```latex
\documentclass[12pt]{article}

% --- PACKAGES ---
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=black]{hyperref}
\usepackage{url}
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{xcolor}

% --- DOCUMENT SETUP ---
\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
    citecolor=darkblue,
}

\pagestyle{fancy}
\fancyhf{}
\lhead{Cybersecurity Assessment Report}
\rhead{Confidential}
\cfoot{\thepage}

% --- TITLE ---
\title{
    \vspace{2cm}
    \textbf{Cybersecurity Posture Assessment Report} \\
    \large \textit{Prepared for: Echo Chamber Arts}
}
\author{Cybersecurity Analyst}
\date{November 22, 2025}

% --- DOCUMENT START ---
\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}

This report provides a comprehensive analysis of the cybersecurity posture of \textbf{Echo Chamber Arts}, based on a technical network scan, a review of organizational security controls, and an assessment of existing risks. The assessment was conducted on \textbf{November 22, 2025}.

The analysis revealed several critical and high-risk security gaps that require immediate attention. Most notably, there is a complete absence of Multi-Factor Authentication (MFA) across all critical systems, including email, computer logins, and access to sensitive data. This represents a significant vulnerability to account takeover and unauthorized access.

Furthermore, the external-facing web server at \texttt{192.168.10.5} is running an outdated version of Nginx (\texttt{1.18.0}), which is known to have unpatched vulnerabilities. This is compounded by an SSL certificate mismatch, which can erode user trust and may indicate a more severe misconfiguration.

The lack of foundational security policies and a consistent employee training schedule exacerbates these technical risks. Immediate and decisive action is required to remediate these findings and establish a robust security baseline.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}

The following details were provided for the assessment.

\begin{tabular}{@{}ll}
    \toprule
    \textbf{Attribute} & \textbf{Value} \\
    \midrule
    Organization Name & Echo Chamber Arts \\
    Email Domain & \texttt{EchoChamberArts.net} \\
    Website Domain & \url{www.EchoChamberArts.net} \\
    External IP Address & \texttt{15.22.211.79} \\
    \bottomrule
\end{tabular}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}

A review of internal security controls was conducted via a questionnaire. The results highlight critical gaps in identity and access management, as well as in governance and training. The symbol \ding{51} denotes "Yes," and \ding{55} denotes "No."

\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lc}
        \toprule
        \textbf{Security Control Question} & \textbf{Response} \\
        \midrule
        Do you require MFA to access email? & \ding{55} \\
        Do you require MFA to log into computers? & \ding{55} \\
        Do you require MFA to access sensitive data systems? & \ding{55} \\
        Does your organization have an employee acceptable use policy? & \ding{55} \\
        Does your organization do security awareness training for new employees? & \ding{51} \\
        Does your organization do security awareness training for all employees at least once per year? & \ding{55} \\
        \bottomrule
    \end{tabular}
    \caption{Security Control Questionnaire Results}
\end{table}

\subsection{Analysis of Controls}
The lack of MFA for email, computer, and sensitive data access is a \textbf{critical risk}. It significantly increases the likelihood of a successful breach via credential theft or phishing. The absence of an acceptable use policy and annual security training for all staff creates an environment where employees may be unaware of their security responsibilities, increasing the risk of human error.

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}

A network scan was performed to identify open ports, running services, and potential vulnerabilities on the specified target system.

\subsection{Scan Metadata}
\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{192.168.10.5}
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

\subsection{Open Ports and Services}
The following services were identified as accessible on the target system.

\begin{table}[h!]
    \centering
    \begin{tabular}{@{}lllll}
        \toprule
        \textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
        \midrule
        443/tcp & open & https & nginx & 1.18.0 \\
        \bottomrule
    \end{tabular}
    \caption{Identified Open Ports}
\end{table}

\subsection{Key Technical Findings}

\subsubsection{Outdated Web Server Software}
The web server is running \textbf{Nginx version 1.18.0}, which was released in April 2020. This version is significantly outdated and no longer receives security updates. Outdated software is a primary target for attackers, as it often contains publicly known and exploitable vulnerabilities.

\subsubsection{SSL Certificate Mismatch}
The SSL certificate presented by the server has a Common Name of \texttt{www.acme-corp.com}, which does not match the organization's domain (\texttt{www.EchoChamberArts.net}). This misconfiguration will cause browser trust warnings for visitors and could be exploited in man-in-the-middle attacks. It suggests a potential deployment error or a repurposed server that was not correctly reconfigured.

% --- RISK ASSESSMENT ---
\section{Risk Assessment}

The following table summarizes the key risks identified during this assessment, correlating findings from the security control review and the technical scan.

\begin{table}[h!]
    \centering
    \begin{tabular}{@{}p{0.1\linewidth} p{0.5\linewidth} p{0.15\linewidth} p{0.15\linewidth}@{}}
        \toprule
        \textbf{Risk ID} & \textbf{Description} & \textbf{Severity} & \textbf{Source} \\
        \midrule
        RISK-001 & \textbf{Lack of Multi-Factor Authentication (MFA):} Absence of MFA on email, computers, and sensitive systems exposes the organization to high risk of account compromise and unauthorized access. & \textbf{Critical} & Questionnaire \\
        \addlinespace
        RISK-002 & \textbf{Outdated Web Server Software:} The public-facing Nginx server is running a vulnerable, end-of-life version, making it a prime target for automated exploitation. & \textbf{High} & Network Scan \\
        \addlinespace
        RISK-003 & \textbf{Inadequate Security Policies and Training:} Lack of an Acceptable Use Policy and annual security training increases the likelihood of security incidents caused by human error. & \textbf{High} & Questionnaire \\
        \addlinespace
        RISK-004 & \textbf{SSL Certificate Mismatch:} The web server presents an invalid certificate for the organization's domain, eroding user trust and indicating a server misconfiguration. & \textbf{Medium} & Network Scan \\
        \bottomrule
    \end{tabular}
    \caption{Summary of Identified Risks}
\end{table}

% --- RECOMMENDATIONS ---
\section{Recommendations}

To mitigate the identified risks and improve the overall security posture of \textbf{Echo Chamber Arts}, the following actions are recommended, prioritized by urgency.

\begin{enumerate}
    \item \textbf{[Immediate] Implement Multi-Factor Authentication (MFA):}
    \begin{itemize}
        \item Immediately enforce MFA for all user accounts across all critical platforms, including email (e.g., Office 365, Google Workspace), VPN access, and administrative interfaces.
        \item Prioritize systems containing sensitive or confidential data.
    \end{itemize}

    \item \textbf{[High] Remediate Web Server Vulnerabilities:}
    \begin{itemize}
        \item Plan and execute an upgrade of the Nginx server from version \texttt{1.18.0} to the latest stable version.
        \item Before upgrading, ensure application compatibility in a staging environment.
        \item Establish a patch management process to ensure all public-facing software is kept up-to-date.
    \end{itemize}

    \item \textbf{[High] Correct SSL Certificate Configuration:}
    \begin{itemize}
        \item Investigate the certificate mismatch on the web server at \texttt{192.168.10.5}.
        \item Procure and install a valid SSL certificate that matches the organization's domain (\texttt{www.EchoChamberArts.net}).
    \end{itemize}

    \item \textbf{[Medium] Develop and Implement Security Policies:}
    \begin{itemize}
        \item Create a formal Acceptable Use Policy (AUP) that clearly defines the rules for using company assets, data, and networks.
        \item Ensure all employees read and acknowledge the policy upon hiring and annually thereafter.
    \end{itemize}

    \item \textbf{[Medium] Establish a Continuous Security Training Program:}
    \begin{itemize}
        \item Supplement the new-hire training with a mandatory annual security awareness program for all employees.
        \item Training should cover current threats such as phishing, social engineering, and password hygiene.
    \end{itemize}
\end{enumerate}

% --- CONCLUSION ---
\section{Conclusion}

The assessment for \textbf{Echo Chamber Arts} has identified significant and actionable risks. While the organization has initiated security training for new hires, critical deficiencies in technical controls (MFA, patch management) and governance (policies, ongoing training) leave it exposed to common cyber threats.

By implementing the recommendations outlined in this report, particularly the immediate deployment of MFA and the remediation of the vulnerable web server, the organization can substantially reduce its risk exposure and build a stronger foundation for its cybersecurity program.

\end{document}
```