```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long monospaced strings
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% --- Document Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfpagemode=FullScreen,
}

% Define colors for severity
\definecolor{criticalred}{HTML}{D73027}
\definecolor{highorange}{HTML}{F46D43}
\definecolor{mediumyellow}{HTML}{FEE08B}
\definecolor{lowblue}{HTML}{4575B4}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Cybersecurity Assessment Report}}
\rhead{\textbf{Hidden Gem}}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Document Start ---
\begin{document}

\title{
    \vspace{2cm}
    \textbf{Cybersecurity Assessment Report} \\
    \large \textbf{For: Hidden Gem}
}
\author{Cybersecurity Analyst}
\date{\today}
\maketitle

\newpage

% --- Table of Contents ---
\tableofcontents

\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}
This report details the findings of a cybersecurity assessment conducted for \textbf{Hidden Gem}. The analysis combined a network vulnerability scan, a review of organizational security controls, and an evaluation of pre-existing risk data.

The assessment identified several critical and high-severity risks that require immediate attention. The most significant finding is an externally exposed MySQL database service (\texttt{172.16.50.20:3306}). This service is running an outdated and End-of-Life version of MySQL (5.7.33), which no longer receives security patches, exposing it to numerous known vulnerabilities.

This technical vulnerability is severely compounded by organizational policy gaps. Specifically, the lack of Multi-Factor Authentication (MFA) for sensitive data systems means that a single compromised password could lead to a complete database breach. Furthermore, the absence of a formal Acceptable Use Policy weakens the organization's overall security posture.

Immediate remediation should focus on restricting network access to the database, followed by a plan to upgrade the database software and implement mandatory MFA for all sensitive systems.

% --- Section 2: Organizational Information ---
\section{Organizational Information}
The following information was provided for the assessment.
\begin{itemize}
    \item \textbf{Organization Name:} Hidden Gem
    \item \textbf{Email Domain:} \texttt{HiddenGem.com}
    \item \textbf{Website Domain:} \texttt{www.HiddenGem.com}
    \item \textbf{External IP Address:} \texttt{193.171.216.195}
\end{itemize}

% --- Section 3: Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a questionnaire. The responses highlight critical gaps in access control and governance policies.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Results}
\begin{tabular}{p{8cm} c p{4cm}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \textcolor{green}{\ding{51}} Yes & Good Practice \\
Do you require MFA to log into computers? & \textcolor{green}{\ding{51}} Yes & Good Practice \\
Do you require MFA to access sensitive data systems? & \textcolor{red}{\ding{55}} No & \textbf{\textcolor{criticalred}{Critical Gap}} \\
Does your organization have an employee acceptable use policy? & \textcolor{red}{\ding{55}} No & \textbf{\textcolor{highorange}{High Risk Policy Gap}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} Yes & Good Practice \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\ding{51}} Yes & Good Practice \\
\bottomrule
\end{tabular}
\end{table}

The lack of MFA for sensitive systems is the most urgent finding from this review, as it directly impacts the security of critical data assets like the database identified in the technical scan.

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}
An external network scan was performed to identify open ports and exposed services.
\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.50.20}
\end{itemize}

\begin{table}[h!]
\centering
\caption{Open Ports and Services Detected}
\begin{tabular}{l l l l l}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis of Technical Findings}
The scan revealed that port \textbf{3306} is open, exposing a \textbf{MySQL} database service directly to the network. The detected version, \textbf{5.7.33}, reached its official End-of-Life (EOL) in October 2023. EOL software no longer receives security updates from the vendor, leaving it perpetually vulnerable to newly discovered exploits. Publicly exposing an EOL database service is a critical security risk that can be easily exploited by automated attack tools.

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list of security risks.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{p{3.5cm} p{7cm} l}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Exposed \& Outdated Database} & The MySQL database on port 3306 is publicly accessible and running version 5.7.33, which is End-of-Life and unpatched. This aligns with the pre-existing "Database Exposure" risk. & \textbf{\textcolor{criticalred}{Critical}} \\
\addlinespace
\textbf{No MFA on Sensitive Systems} & The absence of Multi-Factor Authentication for sensitive systems, including the exposed database, dramatically increases the risk of unauthorized access via compromised credentials. & \textbf{\textcolor{criticalred}{Critical}} \\
\addlinespace
\textbf{Missing Acceptable Use Policy} & The lack of a foundational Acceptable Use Policy (AUP) creates ambiguity for employees regarding security responsibilities and the proper use of company assets. & \textbf{\textcolor{highorange}{High}} \\
\bottomrule
\end{tabular}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}
Based on the identified risks, the following remediation actions are recommended. They are prioritized to address the most critical threats first.

\subsection{Immediate Actions (0-7 Days)}
\begin{enumerate}
    \item \textbf{Restrict Database Access:} Immediately implement strict firewall rules to block all public access to TCP port 3306 on host \texttt{172.16.50.20}. Access should only be permitted from specific, trusted IP addresses required for application functionality or administration.
\end{enumerate}

\subsection{High-Priority Actions (1-3 Months)}
\begin{enumerate}
    \item \textbf{Upgrade Database Software:} Develop and execute a plan to upgrade the MySQL 5.7.33 instance to a currently supported version (e.g., MySQL 8.0 or later). This will ensure the service receives critical security patches.
    \item \textbf{Implement MFA for Sensitive Systems:} Enforce mandatory Multi-Factor Authentication for all accounts (user, service, and administrative) that can access sensitive data systems, with the highest priority on database access.
    \item \textbf{Develop an Acceptable Use Policy (AUP):} Create and implement a formal AUP that clearly defines the rules and responsibilities for all employees when using company technology and data. Ensure all employees read and acknowledge the policy.
\end{enumerate}

\subsection{Long-Term Strategic Recommendations}
\begin{enumerate}
    \item \textbf{Network Segregation:} As a long-term goal, critical infrastructure like databases should not be directly exposed to the internet. Plan to move the database into a private network segment, with access provided securely via a Virtual Private Network (VPN) or a bastion host.
    \item \textbf{Continuous Vulnerability Management:} Implement a regular vulnerability scanning and patch management program to proactively identify and remediate outdated software and misconfigurations across the entire infrastructure.
\end{enumerate}

\end{document}
```