```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings like IPs
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Document Information
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% Color definitions for risk levels
\definecolor{criticalred}{HTML}{D10000}
\definecolor{highorange}{HTML}{E25F00}
\definecolor{mediumyellow}{HTML}{F5C500}
\definecolor{lowblue}{HTML}{0073E6}
\definecolor{infogray}{HTML}{808080}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% Header and Footer
\pagestyle{fancy}
\fancyhf{}
\lhead{Iron River Finance}
\rhead{Confidential}
\cfoot{\thepage}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Executive Summary}

This report details the findings of a cybersecurity posture assessment conducted for \textbf{Iron River Finance}. The assessment combined a review of organizational security controls, an external network scan, and an analysis of pre-existing risks.

The overall security posture is assessed as \textbf{High-Risk}. Several critical deficiencies were identified that expose the organization to significant threats, including unauthorized access, data breach, and service disruption.

Key findings include:
\begin{itemize}
    \item \textbf{Critical Lack of Multi-Factor Authentication (MFA):} The organization has not implemented MFA for email, computer logins, or access to sensitive data systems. This represents a critical vulnerability, as a single compromised password could lead to a full account takeover.
    \item \textbf{Exposed Management Service:} An external network scan identified an open Secure Shell (SSH) port (22/TCP) on the IPv6 address \seqsplit{\texttt{2001:db8::1}}. Exposing management services directly to the internet significantly increases the risk of brute-force attacks and exploitation.
    \item \textbf{Foundational Policy Gap:} The organization lacks a formal employee Acceptable Use Policy (AUP). This absence creates ambiguity regarding security responsibilities and acceptable user behavior, weakening the overall security culture.
\end{itemize}

Immediate remediation is required to address these findings. Recommendations are prioritized to mitigate the most severe risks first. This report provides actionable steps to strengthen the organization's defenses and improve its resilience against cyber threats.

\section{Organizational Information}

The following information was provided for the assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name    & Iron River Finance \\
Email Domain         & \texttt{IronRiverFinance.com} \\
Website Domain       & \url{www.IronRiverFinance.com} \\
External IP (IPv4)   & \texttt{215.156.59.190} \\
External IP (IPv6)   & \seqsplit{\texttt{2001:db8::1}} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details}
\label{tab:org_info}
\end{table}

\section{Security Control Review}

A review of administrative and organizational security controls was conducted based on a standardized questionnaire. The results highlight significant gaps in access control and governance policies.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.6\textwidth}cc@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Status} \\ \midrule
Do you require MFA to access email? & No & \textcolor{criticalred}{\ding{55}} \\
Do you require MFA to log into computers? & No & \textcolor{criticalred}{\ding{55}} \\
Do you require MFA to access sensitive data systems? & No & \textcolor{criticalred}{\ding{55}} \\
Does your organization have an employee acceptable use policy? & No & \textcolor{highorange}{\ding{55}} \\
Does your organization do security awareness training for new employees? & Yes & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for all employees at least once per year? & Yes & \textcolor{green}{\ding{51}} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results}
\label{tab:controls}
\end{table}

\subsection{Analysis of Control Gaps}
\begin{itemize}
    \item \textbf{Multi-Factor Authentication:} The complete absence of MFA is a critical weakness. In today's threat landscape, password-only authentication is insufficient. This gap places email, endpoints, and sensitive data at high risk of unauthorized access via credential theft or brute-force attacks.
    \item \textbf{Acceptable Use Policy (AUP):} The lack of an AUP means there is no formal guidance for employees on protecting company assets, handling data securely, or using network resources appropriately. While security training is in place, its effectiveness is diminished without a foundational policy to enforce.
\end{itemize}

\section{Technical Scan Results}

An external network scan was performed against the target IP address \seqsplit{\texttt{2001:db8::1}}. The scan revealed the following open ports.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Details} \\ \midrule
22/TCP & Open & SSH & Secure Shell management port. Exposed to the public internet. \\
\bottomrule
\end{tabular}
\caption{Open Ports on \seqsplit{\texttt{2001:db8::1}}}
\label{tab:scan_results}
\end{table}

\subsection{Analysis of Technical Findings}
The SSH service on port 22 is a common administrative protocol. Exposing it directly to the internet makes it a prime target for automated scanning and brute-force password attacks. When correlated with the lack of MFA identified in the control review, this finding becomes significantly more severe. A successful password guess or credential leak could grant an attacker direct shell access to the server. No service version information was obtained during the scan, which prevents analysis for specific known vulnerabilities but does not reduce the inherent risk of exposure.

\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data. As no pre-existing vulnerabilities were reported, all risks listed below are new findings from this assessment.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.05\textwidth}p{0.4\textwidth}p{0.3\textwidth}p{0.15\textwidth}@{}}
\toprule
\textbf{ID} & \textbf{Risk Description} & \textbf{Affected Asset(s)} & \textbf{Severity} \\ \midrule
R-01 & \textbf{Lack of Multi-Factor Authentication (MFA):} User accounts can be compromised with a single factor (password), leading to unauthorized access. & All user accounts, email system, endpoints, and sensitive data platforms. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
R-02 & \textbf{Exposed SSH Management Port:} The SSH service on a key server is accessible from the public internet, inviting brute-force and credential stuffing attacks. & Server at \seqsplit{\texttt{2001:db8::1}}. & \textcolor{highorange}{\textbf{High}} \\
\addlinespace
R-03 & \textbf{Missing Acceptable Use Policy (AUP):} Lack of a formal policy creates inconsistent security practices and a weakened security culture. & Organization-wide processes and employee conduct. & \textcolor{highorange}{\textbf{High}} \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\label{tab:risks}
\end{table}

\section{Recommendations}

The following recommendations are prioritized to address the identified risks. It is strongly advised that \textbf{Iron River Finance} implement the Critical and High priority items as soon as possible.

\subsection{Priority 1: Critical Risks}

\begin{enumerate}
    \item \textbf{Implement Multi-Factor Authentication (MFA) Immediately (Mitigates R-01):}
    \begin{itemize}
        \item \textbf{Action:} Procure and deploy an MFA solution across the organization.
        \item \textbf{Priority Targets:}
            \begin{enumerate}
                \item All email accounts (e.g., Office 365, Google Workspace).
                \item All remote access systems (e.g., VPN).
                \item All systems hosting sensitive financial or customer data.
                \item All administrator and privileged accounts.
            \end{enumerate}
        \item \textbf{Justification:} This is the single most effective control to prevent account takeovers resulting from stolen credentials.
    \end{itemize}
    
    \item \textbf{Secure Exposed SSH Service (Mitigates R-02):}
    \begin{itemize}
        \item \textbf{Action:} Restrict and harden access to the SSH service on \seqsplit{\texttt{2001:db8::1}}.
        \item \textbf{Steps:}
            \begin{enumerate}
                \item \textbf{Restrict Access:} If possible, configure firewall rules to allow SSH access only from trusted IP addresses (e.g., office or administrator networks). If access is required from anywhere, implement access via a bastion host or VPN.
                \item \textbf{Enforce Strong Authentication:} Disable password-based authentication and enforce the use of public key cryptography (SSH keys).
                \item \textbf{Harden Configuration:} In the SSH daemon configuration file (`sshd_config`), disable root login (`PermitRootLogin no`) and consider changing the default port if policy allows.
            \end{enumerate}
        \item \textbf{Justification:} Reduces the attack surface and protects a critical entry point into the organization's infrastructure.
    \end{itemize}
\end{enumerate}

\subsection{Priority 2: High Risks}

\begin{enumerate}
    \setcounter{enumi}{2} % Continue numbering from previous list
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP) (Mitigates R-03):}
    \begin{itemize}
        \item \textbf{Action:} Draft a formal AUP that clearly defines the rules and responsibilities for all employees when using company technology and data.
        \item \textbf{Content to Include:} Rules for password management, data handling, internet usage, use of personal devices (BYOD), and incident reporting.
        \item \textbf{Implementation:} Require all employees to read and formally acknowledge the policy. Integrate the AUP into the new hire onboarding process and the annual security awareness training program.
        \item \textbf{Justification:} A formal AUP establishes a baseline for secure behavior, reduces insider risk, and provides a basis for enforcement actions if violations occur.
    \end{itemize}
\end{enumerate}

\end{document}
```