```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses (\ding)
\usepackage{booktabs} % For professional tables (\toprule, \midrule, \bottomrule)
\usepackage[hidelinks]{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % To split long strings in texttt
\usepackage{xcolor} % For colored text
\usepackage{graphicx} % For potential logos/images
\usepackage{fancyhdr} % For headers and footers

% Define colors for status indicators
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\definecolor{darkred}{rgb}{0.8, 0.0, 0.0}

% Document Information
\title{Cybersecurity Assessment Report \\ \large For: Green Sprout Organic}
\author{Cybersecurity Analysis Division}
\date{\today}

% Header and Footer Configuration
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Confidential Cybersecurity Report}
\fancyhead[R]{Green Sprout Organic}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section{Executive Summary}

This report provides a comprehensive cybersecurity assessment for \textbf{Green Sprout Organic}, based on the analysis and correlation of network scan data, organizational security controls, and known risks. The assessment was conducted to identify vulnerabilities, evaluate the current security posture, and provide actionable recommendations for remediation.

The analysis revealed two primary areas of significant concern:

\begin{enumerate}
    \item \textbf{Critical Infrastructure Risk:} A network scan identified an externally exposed MySQL database server. This server is running version \texttt{5.7.33}, which reached its official End-of-Life (EOL) in October 2023. EOL software no longer receives security updates, making it an easy target for attackers leveraging known vulnerabilities. This finding confirms and elevates the pre-existing risk of "Database Exposure" to a critical level.
    
    \item \textbf{High Organizational Risk:} The security questionnaire revealed a complete lack of a security awareness training program for both new and existing employees. This represents a significant gap in the organization's human firewall, increasing susceptibility to phishing, social engineering, and other employee-targeted attacks.
\end{enumerate}

Immediate action is required to mitigate the exposed database risk, followed by the strategic implementation of a security awareness program to address the organizational gaps. Detailed recommendations are provided in Section \ref{sec:recommendations}.

\section{Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Green Sprout Organic} \\
Email Domain & \texttt{GreenSproutOrganic.net} \\
Website Domain & \texttt{www.GreenSproutOrganic.net} \\
External IP Address & \texttt{147.142.11.187} \\
\bottomrule
\end{tabular}

\section{Security Control Review}

A review of organizational security controls was conducted via a questionnaire. The results below highlight key strengths and critical gaps. "No" answers indicate a lack of a fundamental security control and represent a significant risk.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.8\linewidth}c@{}}
\toprule
\textbf{Security Control Question} & \textbf{Status} \\
\midrule
Do you require MFA to access email? & {\color{darkgreen}\ding{51}} \\
Do you require MFA to log into computers? & {\color{darkgreen}\ding{51}} \\
Do you require MFA to access sensitive data systems? & {\color{darkgreen}\ding{51}} \\
Does your organization have an employee acceptable use policy? & {\color{darkgreen}\ding{51}} \\
\addlinespace
Does your organization do security awareness training for new employees? & {\color{darkred}\ding{55}} \\
Does your organization do security awareness training for all employees at least once per year? & {\color{darkred}\ding{55}} \\
\bottomrule
\end{tabular}
\caption{Organizational Security Control Status.}
\label{tab:controls}
\end{table}

\paragraph{Analysis:} The organization has a strong Multi-Factor Authentication (MFA) policy, which is commendable. However, the complete absence of a security awareness training program is a critical deficiency. Without training, employees are significantly more likely to fall victim to common cyberattacks such as phishing, which could compromise credentials and undermine the effectiveness of other security controls.

\section{Technical Scan Results}

An external network scan was performed on the target system to identify open ports and exposed services.

\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{172.16.50.20}
\end{itemize}

\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & open & mysql & MySQL & \seqsplit{\texttt{5.7.33}} \\
\bottomrule
\end{tabular}
\caption{Open Ports and Services Detected.}
\label{tab:scanresults}
\end{table}

\paragraph{Analysis:} The scan confirms that port \texttt{3306}, the default port for MySQL databases, is open to the network. The identified version, \textbf{MySQL 5.7.33}, is a significant finding. \textbf{MySQL 5.7 is End-of-Life (EOL) as of October 2023}. This means it no longer receives security patches from the vendor, and numerous public exploits exist for this version. Exposing an EOL database service directly to the internet constitutes a critical and immediate threat to data confidentiality, integrity, and availability.

\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a consolidated list of key risks.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.25\linewidth}p{0.45\linewidth}p{0.2\linewidth}@{}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Exposed \& Outdated Database} & MySQL port 3306 is open to the network. The running version, 5.7.33, is End-of-Life, unpatched, and vulnerable to known exploits. This directly impacts the system at \texttt{172.16.50.20}. & \textbf{Critical} \\
\addlinespace
\textbf{Lack of Security Awareness Program} & The organization does not train new or existing employees on cybersecurity best practices. This increases organizational susceptibility to phishing, malware, and social engineering attacks. & \textbf{High} \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks.}
\label{tab:risks}
\end{table}

\section{Recommendations}
\label{sec:recommendations}

The following actions are recommended to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection{Remediate Exposed \& Outdated Database (Critical)}

\begin{itemize}
    \item \textbf{Immediate Action (Containment):} Implement strict firewall rules to deny all public access to TCP port \texttt{3306} on \texttt{172.16.50.20}. Access should only be permitted from specific, trusted internal IP addresses required for application functionality.
    
    \item \textbf{Short-Term Action (Remediation):} Develop and execute a plan to upgrade the MySQL database from the EOL version 5.7 to a currently supported major version (e.g., MySQL 8.0 or higher). This will ensure the system receives ongoing security updates.
    
    \item \textbf{Long-Term Action (Architectural Improvement):} For any required administrative access, implement a Virtual Private Network (VPN). This will provide a secure, encrypted tunnel for administrators and eliminate the need for any direct public exposure of the database port.
\end{itemize}

\subsection{Implement Security Awareness Program (High)}

\begin{itemize}
    \item \textbf{Immediate Action (Foundation):} Procure and enroll all current employees in a foundational security awareness training module. This should cover essential topics like phishing identification, password security, and safe browsing habits.
    
    \item \textbf{Short-Term Action (Policy):} Develop a formal policy that mandates security awareness training for all new hires as part of their onboarding process and requires annual refresher training for all staff.
    
    \item \textbf{Long-Term Action (Maturity):} Establish a continuous security culture program. This should include regular simulated phishing campaigns to test and measure employee resilience, with follow-up training for those who are susceptible.
\end{itemize}

\end{document}
```