```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long strings in tt font
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{fancyhdr}

% Document Metadata
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% Define colors for severity
\definecolor{criticalred}{HTML}{D10000}
\definecolor{highorange}{HTML}{E57200}
\definecolor{mediumyellow}{HTML}{FFC72C}

% Header and Footer Configuration
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyhead[L]{Aetheric Systems // Confidential}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}
This report provides a comprehensive cybersecurity assessment for \textbf{Aetheric Systems}, based on network scan data, organizational security questionnaires, and a review of pre-existing risks. The analysis correlates technical vulnerabilities with organizational policy gaps to provide a holistic view of the current security posture.

The overall security posture is assessed as \textbf{CRITICAL}. This assessment is driven by the discovery of a publicly exposed, end-of-life database service combined with a complete absence of fundamental security controls, such as Multi-Factor Authentication (MFA) and employee security training.

\textbf{Key Findings Include:}
\begin{itemize}
    \item \textbf{Critical Database Exposure:} An internet-facing MySQL database (version 5.7.33) was identified on port 3306. This version is End-of-Life (EOL) as of October 2023 and no longer receives security updates, making it an easy target for exploitation.
    \item \textbf{Complete Lack of MFA:} The organization does not enforce MFA for email, computer logins, or access to sensitive data systems. This significantly increases the risk of account compromise and unauthorized access.
    \item \textbf{Absence of Security Policies and Training:} There is no Acceptable Use Policy (AUP) for employees, nor is there any security awareness training. This indicates a low level of security maturity and leaves the organization highly susceptible to social engineering and phishing attacks.
\end{itemize}

Immediate remediation is required to address the exposed database. Strategic initiatives must be launched to implement foundational security controls across the organization to mitigate these severe risks.

% --- 2. Organizational Information ---
\section{Organizational Information}
The following information was provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Aetheric Systems} \\
Email Domain & \texttt{AethericSystems.com} \\
Website Domain & \url{www.AethericSystems.com} \\
External IP Address & \texttt{201.195.126.137} \\
\bottomrule
\end{tabular}

% --- 3. Security Control Review ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a questionnaire. The responses reveal critical gaps in fundamental security practices. A summary is provided in Table \ref{tab:controls}.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\label{tab:controls}
\begin{tabular}{@{}p{0.6\linewidth} c p{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \ding{55} & \textcolor{criticalred}{\textbf{Critical Gap}} \\
Do you require MFA to log into computers? & \ding{55} & \textcolor{criticalred}{\textbf{Critical Gap}} \\
Do you require MFA to access sensitive data systems? & \ding{55} & \textcolor{criticalred}{\textbf{Critical Gap}} \\
Does your organization have an employee acceptable use policy? & \ding{55} & \textcolor{highorange}{\textbf{High Risk}} \\
Does your organization do security awareness training for new employees? & \ding{55} & \textcolor{criticalred}{\textbf{Critical Gap}} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} & \textcolor{criticalred}{\textbf{Critical Gap}} \\
\bottomrule
\end{tabular}
\end{table}

The symbol \ding{51} indicates a "Yes" response (control in place), while \ding{55} indicates a "No" response (control is missing). The complete absence of these basic controls points to a reactive and immature security program.

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}
A network scan was performed on the target IP address \texttt{172.16.50.20} to identify open ports and exposed services. The results are detailed in Table \ref{tab:scan}.

\begin{table}[h!]
\centering
\caption{Open Port Analysis}
\label{tab:scan}
\begin{tabular}{@{}llllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} & \textbf{Analysis} \\
\midrule
3306/tcp & Open & mysql & MySQL & 5.7.33 & \parbox{4cm}{\textcolor{criticalred}{\textbf{CRITICAL FINDING:}} Publicly exposed database. Version is End-of-Life (EOL) and highly vulnerable.} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Analysis of Findings}
The scan identified one open port: 3306/tcp, running MySQL version 5.7.33. This finding presents two distinct and severe risks:
\begin{enumerate}
    \item \textbf{Network Exposure:} Database ports should never be exposed directly to the public internet. This configuration allows attackers worldwide to attempt brute-force password attacks, exploit vulnerabilities, or perform denial-of-service attacks against the database.
    \item \textbf{End-of-Life Software:} The MySQL 5.7 branch reached its official End of Life in October 2023. Version 5.7.33 was released in early 2021. This software no longer receives security patches from the vendor, and numerous high-severity vulnerabilities have been discovered since its release.
\end{enumerate}

% --- 5. Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}
The following table synthesizes findings from the security questionnaire, technical scan, and pre-existing risk data into a consolidated list of key risks facing the organization.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\label{tab:risks}
\begin{tabular}{@{}p{0.25\linewidth} p{0.55\linewidth} l@{}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Outdated \& Exposed Database Service} & A public-facing MySQL 5.7.33 database is active. This version is EOL, unpatched, and exposed to network attacks. This is a new finding that elevates the pre-existing "Database Exposure" risk. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
\textbf{Lack of Multi-Factor Authentication} & No MFA is enforced for email, computer, or sensitive system access. A single compromised password could lead to a full breach. & \textcolor{criticalred}{\textbf{Critical}} \\
\addlinespace
\textbf{Lack of Security Policies \& Training} & The absence of an AUP and security training programs leaves employees unaware of threats, making them prime targets for phishing and social engineering. & \textcolor{highorange}{\textbf{High}} \\
\addlinespace
\textbf{Database Exposure} & \textit{(Pre-existing risk, confirmed by scan)} The MySQL port 3306 is open to the network, allowing unauthorized connection attempts. The CVSS score for this is 7.5. & \textcolor{highorange}{\textbf{High}} \\
\bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
The following actions are recommended to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection{Immediate Actions (To Be Completed Within 72 Hours)}
\begin{enumerate}
    \item \textbf{Firewall Port 3306:} Immediately implement firewall rules to block all public ingress traffic to TCP port 3306 on host \texttt{172.16.50.20}. Access should be restricted to a whitelist of trusted IP addresses or, preferably, only be allowed via a secure VPN tunnel.
    \item \textbf{Develop an Upgrade Plan:} Begin planning the urgent migration of the MySQL 5.7.33 database to a currently supported version (e.g., MySQL 8.x). This plan should include data backup, testing, and a scheduled maintenance window.
\end{enumerate}

\subsection{Short-Term Actions (To Be Completed Within 30-60 Days)}
\begin{enumerate}
    \item \textbf{Implement Multi-Factor Authentication (MFA):}
        \begin{itemize}
            \item Prioritize enabling MFA for all email accounts.
            \item Roll out MFA for all remote access systems (e.g., VPN).
            \item Enforce MFA for logins to all systems containing sensitive data.
        \end{itemize}
    \item \textbf{Establish Foundational Policies:} Draft and implement a formal Acceptable Use Policy (AUP) that all employees must read and acknowledge.
    \item \textbf{Conduct Security Awareness Training:} Enroll all employees in a mandatory, foundational security awareness training program covering phishing, password hygiene, and social engineering.
\end{enumerate}

\subsection{Long-Term Strategic Actions (To Be Completed Within 6-12 Months)}
\begin{enumerate}
    \item \textbf{Establish a Vulnerability Management Program:} Implement a formal process for regularly scanning internal and external assets, identifying vulnerabilities, and tracking them to remediation.
    \item \textbf{Implement Annual Training:} Make security awareness training an annual requirement for all employees to ensure continuous education on evolving threats.
\end{enumerate}

\end{document}
```