```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings in tt font
\usepackage{graphicx} % For potential logos (not used here, but good practice)
\usepackage{xcolor} % For colors in text

% Document Metadata
\title{Cybersecurity Assessment Report \\ \large For: Vanguard Heritage}
\author{Cybersecurity Analysis Division}
\date{November 22, 2025}

\begin{document}

\maketitle
\thispagestyle{empty}
\clearpage

\tableofcontents
\clearpage

% --- Section 1: Executive Overview ---
\section{Executive Overview}

This report details the findings of a cybersecurity assessment conducted for \textbf{Vanguard Heritage} on November 22, 2025. The assessment combined an external network scan, a review of organizational security controls via a questionnaire, and an analysis of pre-existing risks.

The analysis revealed several critical and high-risk security gaps that expose the organization to significant threats, including account compromise, data breaches, and service disruption. Key findings include:
\begin{itemize}
    \item \textbf{Critical Lack of Multi-Factor Authentication (MFA):} The complete absence of MFA for email, computer logins, and sensitive data systems represents a critical vulnerability. This is the most significant weakness identified and dramatically increases the risk of unauthorized access.
    \item \textbf{Outdated External Services:} The public-facing web server is running an outdated version of nginx (1.18.0), which is known to have security vulnerabilities. This exposes the organization to potential exploitation from external attackers.
    \item \textbf{Insufficient Security Policies and Training:} The organization lacks a formal Acceptable Use Policy and does not conduct annual security awareness training for all staff. These foundational gaps weaken the human element of the security posture.
    \item \textbf{Web Server Misconfiguration:} An SSL certificate mismatch was identified on the primary web server, which can erode user trust and may indicate underlying configuration issues.
\end{itemize}

Immediate and decisive action is required to remediate these findings. Recommendations provided in this report are prioritized to address the most critical risks first.

% --- Section 2: Organizational Information ---
\section{Organizational Information}

The following information was provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Vanguard Heritage} \\
Email Domain & \texttt{VanguardHeritage.org} \\
Website Domain & \texttt{www.VanguardHeritage.org} \\
External IP Address & \texttt{205.245.36.98} \\
\bottomrule
\end{tabular}

% --- Section 3: Security Control Review ---
\section{Security Control Review}

The following table summarizes the organization's responses to a security controls questionnaire. "No" answers indicate significant gaps in the current security posture.

\begin{tabular}{@{}p{0.6\linewidth} c p{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \ding{55} & \textcolor{red}{\textbf{Critical Gap}} \\
Do you require MFA to log into computers? & \ding{55} & \textcolor{red}{\textbf{Critical Gap}} \\
Do you require MFA to access sensitive data systems? & \ding{55} & \textcolor{red}{\textbf{Critical Gap}} \\
Does your organization have an employee acceptable use policy? & \ding{55} & High Risk \\
Does your organization do security awareness training for new employees? & \ding{51} & Good Practice \\
Does your organization do security awareness training for all employees at least once per year? & \ding{55} & High Risk \\
\bottomrule
\end{tabular}

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed against the target IP address to identify open ports and exposed services.

\subsection{Scan Details}
\begin{itemize}
    \item \textbf{Target IP:} \texttt{192.168.10.5}
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

\subsection{Open Ports and Services}
The following table details the services discovered.

\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product \& Version} \\
\midrule
443/tcp & open & https & nginx 1.18.0 \\
\bottomrule
\end{tabular}

\subsection{Analysis of Findings}
\begin{itemize}
    \item \textbf{Outdated Nginx Version:} The web server is running \textbf{nginx version 1.18.0}, which was released in April 2020. This version is significantly outdated and is missing numerous security patches for vulnerabilities discovered since its release. Running unsupported software on an internet-facing system presents a high risk of exploitation.
    \item \textbf{SSL Certificate Mismatch:} The scan revealed that the SSL certificate presented by the server is for the common name \seqsplit{\texttt{www.acme-corp.com}}. This does not match the organization's domain, \texttt{www.VanguardHeritage.org}. This misconfiguration will cause browser trust errors and could be exploited in man-in-the-middle scenarios.
\end{itemize}

% --- Section 5: Risk Assessment Summary ---
\section{Risk Assessment Summary}

The following table synthesizes findings from the security control review and the technical scan into a prioritized list of risks. No pre-existing vulnerabilities were reported.

\begin{tabular}{@{}p{0.1\linewidth} p{0.25\linewidth} p{0.45\linewidth} p{0.1\linewidth}@{}}
\toprule
\textbf{Risk ID} & \textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
RISK-001 & No Multi-Factor Authentication (MFA) & The absence of MFA for email, endpoints, and sensitive systems makes user accounts highly susceptible to takeover via stolen credentials. & \textcolor{red}{\textbf{Critical}} \\
\addlinespace
RISK-002 & Outdated Web Server Software & The public-facing nginx server is running an old version with known vulnerabilities, creating a direct vector for external attack. & High \\
\addlinespace
RISK-003 & Inadequate Security Policies & The lack of a formal Acceptable Use Policy creates ambiguity regarding security responsibilities and acceptable employee behavior. & High \\
\addlinespace
RISK-004 & Insufficient Security Awareness Training & Without mandatory annual training, employees' ability to recognize and respond to evolving threats like phishing diminishes over time. & High \\
\addlinespace
RISK-005 & SSL Certificate Mismatch & The web server presents an invalid certificate, which harms user trust and indicates a server misconfiguration. & Medium \\
\bottomrule
\end{tabular}

% --- Section 6: Recommendations ---
\section{Recommendations}

The following actions are recommended to mitigate the identified risks. They are prioritized based on severity.

\begin{enumerate}
    \item \textbf{(RISK-001) Implement Multi-Factor Authentication:}
    \begin{itemize}
        \item \textbf{Action:} Immediately deploy a robust MFA solution across the organization.
        \item \textbf{Priority:} Start with email (e.g., Office 365, Google Workspace), followed by remote access (VPN), and all systems containing sensitive data.
        \item \textbf{Impact:} Drastically reduces the risk of account compromise.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{(RISK-002) Remediate Outdated Nginx Server:}
    \begin{itemize}
        \item \textbf{Action:} Plan and execute an upgrade of the nginx server at \texttt{192.168.10.5} to the latest stable version.
        \item \textbf{Priority:} This should be done in a staging environment first to ensure compatibility, then deployed to production as soon as possible.
        \item \textbf{Impact:} Mitigates known vulnerabilities and protects the server from exploitation.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{(RISK-003 \& 004) Establish Security Policies and Training:}
    \begin{itemize}
        \item \textbf{Action:} Draft and ratify a formal Acceptable Use Policy (AUP). Concurrently, procure and schedule mandatory annual security awareness training for all employees.
        \item \textbf{Priority:} These foundational controls should be implemented within the next quarter.
        \item \textbf{Impact:} Strengthens the human firewall and establishes clear security expectations.
    \end{itemize}
    \vspace{0.5cm}
    \item \textbf{(RISK-005) Correct SSL Certificate Configuration:}
    \begin{itemize}
        \item \textbf{Action:} Investigate the certificate mismatch. Procure and correctly install a valid SSL/TLS certificate for the domain \texttt{www.VanguardHeritage.org}.
        \item \textbf{Priority:} Remediate to ensure secure connections and maintain user trust.
        \item \textbf{Impact:} Resolves browser security warnings and secures web traffic.
    \end{itemize}
\end{enumerate}

\end{document}
```