```latex
\documentclass[12pt]{article}

% --- PACKAGE IMPORTS ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links and ToC
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings to prevent overflow
\usepackage{graphicx} % For potential logos
\usepackage{xcolor} % For colors in text

% --- DOCUMENT METADATA & STYLING ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Report},
    pdfpagemode=FullScreen,
}

\newcommand{\yes}{\ding{51}} % Green checkmark
\newcommand{\no}{\ding{55}}  % Red X

\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge\textbf{Cybersecurity Posture Report}
    \vspace{1.5cm}
    \vfill
    \large
    \textbf{Prepared for:}\\
    Binary Star
    \vspace{0.5cm}
    
    \textbf{Date of Report:}\\
    \today
    
    \vspace{1cm}
    \textbf{Scan Date:}\\
    2025-11-22
    
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report provides a comprehensive analysis of the cybersecurity posture for \textbf{Binary Star}, based on a technical network scan, a review of organizational security controls, and an assessment of existing risks. The assessment was conducted on \textbf{2025-11-22}.

The analysis revealed several critical and high-risk security gaps that require immediate attention. The most significant findings include:
\begin{itemize}
    \item \textbf{Critical Risk - No Multi-Factor Authentication (MFA):} The complete absence of MFA for email, computer logins, and access to sensitive data systems represents a critical vulnerability. This significantly increases the risk of unauthorized access and account compromise.
    \item \textbf{High Risk - Outdated Web Server Software:} The external-facing web server is running an outdated version of Nginx (1.18.0), which has numerous publicly known vulnerabilities. This exposes the organization to potential exploitation.
    \item \textbf{High Risk - Lack of Foundational Security Policies:} The organization lacks a formal Acceptable Use Policy and a structured security awareness training program. This indicates a gap in security governance and employee education, increasing the likelihood of human error leading to security incidents.
\end{itemize}

Immediate remediation of these issues is strongly recommended to reduce the organization's attack surface and improve its overall resilience against cyber threats. Detailed findings and actionable recommendations are provided in the subsequent sections of this report.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following details were provided for the assessment.
\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & Binary Star \\
Email Domain & \texttt{BinaryStar.org} \\
Website Domain & \url{www.BinaryStar.org} \\
External IP Address & \texttt{221.82.52.124} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details}
\end{table}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}
A review of administrative security controls was conducted via a questionnaire. The results highlight significant gaps in fundamental security practices. A "No" answer indicates a missing control and a potential area of high risk.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.7\textwidth}c@{}}
\toprule
\textbf{Control Question} & \textbf{Status} \\ \midrule
Do you require MFA to access email? & \no \\
Do you require MFA to log into computers? & \no \\
Do you require MFA to access sensitive data systems? & \no \\
Does your organization have an employee acceptable use policy? & \no \\
Does your organization do security awareness training for new employees? & \no \\
Does your organization do security awareness training for all employees at least once per year? & \no \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Results}
\end{table}

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
An external network scan was performed to identify open ports and exposed services on the target system.

\subsection{Scan Metadata}
\begin{itemize}
    \item \textbf{Target IP Address:} \texttt{192.168.10.5}
    \item \textbf{Scan Date:} 2025-11-22T10:00:00Z
\end{itemize}

\subsection{Open Ports and Services}
The scan identified one open port on the target host.
\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\ \midrule
443/tcp & open & https & nginx & 1.18.0 \\ \bottomrule
\end{tabular}
\caption{Discovered Open Ports and Services}
\end{table}

\subsubsection{Analysis of Findings}
\begin{itemize}
    \item \textbf{Outdated Nginx Version:} The web server is running Nginx version 1.18.0, which was released in April 2020. This version is significantly outdated and is affected by multiple known vulnerabilities, including but not limited to request smuggling and denial-of-service flaws. Running unsupported software on an internet-facing system poses a high risk of compromise.
    \item \textbf{SSL Certificate Mismatch:} The SSL certificate presented by the server has a Common Name of \texttt{www.acme-corp.com}. This does not match the organization's domain (\texttt{www.BinaryStar.org}), which will cause browser trust errors for visitors and may indicate a server misconfiguration.
\end{itemize}

% --- RISK ASSESSMENT ---
\section{Risk Assessment}
Based on the correlation of the security control review and technical scan results, the following risks have been identified and prioritized.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.25\textwidth}p{0.55\textwidth}l@{}}
\toprule
\textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\ \midrule
\textbf{No MFA Implementation} & The lack of MFA across all critical systems (email, endpoints, data) makes the organization highly susceptible to credential theft and account takeover attacks. & \textbf{Critical} \\
\textbf{Outdated Web Server} & The public-facing web server runs an old version of Nginx with known vulnerabilities, creating a direct vector for external attackers to compromise the system. & \textbf{High} \\
\textbf{No Security Policies or Training} & The absence of an Acceptable Use Policy and security awareness training leaves employees without clear guidelines, increasing the risk of insider threats and human error. & \textbf{High} \\
\textbf{SSL Certificate Mismatch} & The server's SSL certificate does not match the organization's domain, which erodes user trust and could be indicative of broader configuration issues. & \textbf{Medium} \\ \bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\end{table}

% --- RECOMMENDATIONS ---
\section{Recommendations}
The following actionable recommendations are provided to mitigate the identified risks and improve the overall security posture of \textbf{Binary Star}.

\begin{enumerate}
    \item \textbf{Implement Multi-Factor Authentication (Priority: Critical):}
    \begin{itemize}
        \item Immediately enable MFA on the email platform (\texttt{BinaryStar.org}).
        \item Deploy an MFA solution for all computer and remote access logins.
        \item Enforce MFA for access to all systems containing sensitive or critical data.
    \end{itemize}

    \item \textbf{Upgrade Web Server Software (Priority: High):}
    \begin{itemize}
        \item Plan and execute an upgrade of the Nginx server from version 1.18.0 to the latest stable version.
        \item Implement a patch management process to ensure all internet-facing systems are kept up-to-date with security patches.
    \end{itemize}
    
    \item \textbf{Establish Foundational Security Programs (Priority: High):}
    \begin{itemize}
        \item Develop and implement a formal Acceptable Use Policy (AUP) that all employees must read and acknowledge.
        \item Institute a mandatory security awareness training program for all new and existing employees, to be conducted at least annually.
    \end{itemize}

    \item \textbf{Correct SSL Certificate Configuration (Priority: Medium):}
    \begin{itemize}
        \item Investigate the SSL certificate mismatch on the web server.
        \item Procure and install a valid SSL certificate for the \texttt{www.BinaryStar.org} domain to ensure encrypted connections are trusted by users and browsers.
    \end{itemize}
\end{enumerate}

\end{document}
```