```latex
\documentclass[12pt]{article}

% Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage[T1]{fontenc}

% Document Metadata
\title{Cybersecurity Assessment Report}
\author{Cybersecurity Analysis Division}
\date{November 22, 2025}

\begin{document}

\maketitle

\begin{abstract}
This report provides a comprehensive cybersecurity assessment for Gilded Cage Design. The analysis is based on a synthesis of network scan data, an organizational security questionnaire, and a review of pre-existing risks. The assessment identifies several critical and high-risk vulnerabilities related to identity and access management, patch management, and administrative controls. Immediate remediation is recommended to mitigate these risks and improve the organization's overall security posture.
\end{abstract}

\newpage

\tableofcontents

\newpage

\section{Executive Summary}
The security posture of Gilded Cage Design was evaluated through a combination of technical scanning and a review of administrative security controls. The assessment revealed significant gaps that expose the organization to substantial risk.

Key findings include:
\begin{itemize}
    \item \textbf{Critical Gaps in Access Control:} Multi-Factor Authentication (MFA) is not enforced for employee email or computer logins. This represents a critical vulnerability, as a single compromised password could lead to a widespread breach of communications and internal systems.
    \item \textbf{Vulnerable External Service:} The public-facing web server is running an outdated version of nginx (1.18.0), which has known security vulnerabilities. This service could serve as an initial entry point for an attacker.
    \item \textbf{Administrative Control Deficiencies:} The organization lacks a formal Acceptable Use Policy (AUP), a foundational document for guiding employee behavior and enforcing security standards.
    \item \textbf{Configuration Weakness:} The SSL certificate presented by the web server does not match the organization's domain, which can erode user trust and may indicate a server misconfiguration.
\end{itemize}

While the organization has implemented security awareness training and protects sensitive data systems with MFA, the identified weaknesses require immediate attention. This report outlines actionable recommendations to address each finding.

\section{Organizational Information}
The following details were provided for the assessment.

\begin{tabular}{@{}ll}
\toprule
\textbf{Attribute} & \textbf{Value} \\
\midrule
Organization Name & \textbf{Gilded Cage Design} \\
Email Domain & \texttt{GildedCageDesign.org} \\
Website Domain & \url{www.GildedCageDesign.org} \\
External IP Address & \seqsplit{\texttt{143.32.200.72}} \\
\bottomrule
\end{tabular}

\section{Security Control Review}
The following table summarizes the organization's responses to the security controls questionnaire. A checkmark (\ding{51}) indicates a positive control is in place, while a cross (\ding{55}) indicates a gap.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lc}
\toprule
\textbf{Security Control Question} & \textbf{Status} \\
\midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{55} \\
Do you require MFA to access sensitive data systems? & \ding{51} \\
Does your organization have an employee acceptable use policy? & \ding{55} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
Does your organization do security awareness training for all employees annually? & \ding{51} \\
\bottomrule
\end{tabular}
\caption{Organizational Security Controls Questionnaire Results}
\end{table}

\subsection*{Analysis of Control Gaps}
The questionnaire reveals critical deficiencies in fundamental security practices:
\begin{itemize}
    \item \textbf{Lack of MFA on Email/Computers:} The absence of MFA for email and computer access is the most severe finding. Email is a primary target for phishing and account takeover attacks. Without MFA, a compromised password gives an attacker full access. Similarly, unprotected computer logins allow for trivial lateral movement within the network.
    \item \textbf{No Acceptable Use Policy (AUP):} An AUP is a crucial administrative control that defines the rules for using company IT assets. Its absence creates ambiguity regarding security responsibilities and acceptable behavior, complicating policy enforcement and incident response.
\end{itemize}

\section{Technical Scan Results}
An external network scan was performed on \textbf{2025-11-22}. The scan targeted the organization's infrastructure to identify open ports and exposed services.

\subsection*{Host: \seqsplit{\texttt{192.168.10.5}}}
The scan identified one host as active and responsive.
\begin{itemize}
    \item \textbf{Status:} Up
\end{itemize}

\subsection*{Open Ports and Services}
The following service was found to be exposed:
\begin{description}
    \item[Port 443/tcp (https):] The port is \textbf{OPEN}.
    \begin{itemize}
        \item \textbf{Service:} nginx 1.18.0
        \item \textbf{Finding 1 (Vulnerable Software):} The identified nginx version (1.18.0) was released in April 2020 and is outdated. It is known to be affected by multiple security vulnerabilities, including CVE-2021-23017. Running unpatched, internet-facing software poses a high risk of exploitation.
        \item \textbf{Finding 2 (Certificate Mismatch):} The SSL certificate presented by the server has a Common Name of \texttt{www.acme-corp.com}, which does not match the organization's domain (\texttt{www.GildedCageDesign.org}). This misconfiguration can cause browser trust errors and may indicate an improper server setup.
    \end{itemize}
\end{description}

\section{Consolidated Risk Assessment}
The following table consolidates findings from the security control review and the technical scan into a prioritized list of risks.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.3\linewidth}p{0.5\linewidth}l@{}}
\toprule
\textbf{Risk Name} & \textbf{Overview} & \textbf{Severity} \\
\midrule
\textbf{Lack of MFA on Core Systems} & The absence of MFA on email and computer logins allows for account takeover and lateral movement with only a compromised password. & \textbf{Critical} \\
\addlinespace
\textbf{Outdated and Vulnerable Web Server} & The public-facing nginx server is running an old version with known vulnerabilities, making it a prime target for automated attacks and compromise. & \textbf{High} \\
\addlinespace
\textbf{Absence of Acceptable Use Policy} & Lacking a formal AUP creates an undisciplined security environment and weakens the organization's ability to enforce security standards. & \textbf{Medium} \\
\addlinespace
\textbf{SSL Certificate Mismatch} & The web server presents an invalid certificate for its domain, which damages user trust and indicates a server misconfiguration. & \textbf{Medium} \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks}
\end{table}

\section{Recommendations}
To address the identified risks, the following actions are recommended in order of priority.

\begin{enumerate}
    \item \textbf{Implement Comprehensive MFA (Priority: Immediate):}
    \begin{itemize}
        \item Deploy a robust Multi-Factor Authentication solution across the entire organization.
        \item Prioritize the immediate enforcement of MFA for all email access (e.g., O365, Google Workspace) and all workstation/laptop logins (e.g., Windows Hello, Duo).
    \end{itemize}

    \item \textbf{Remediate Web Server Vulnerabilities (Priority: Urgent):}
    \begin{itemize}
        \item Upgrade the nginx service on server \seqsplit{\texttt{192.168.10.5}} to the latest stable version to patch known vulnerabilities.
        \item Establish a formal patch management policy and schedule for all internet-facing systems to ensure they are updated in a timely manner.
    \end{itemize}

    \item \textbf{Correct SSL Certificate Configuration (Priority: High):}
    \begin{itemize}
        \item Investigate the certificate mismatch on the web server.
        \item Procure and correctly install a valid SSL/TLS certificate that corresponds to the organization's domain, \texttt{www.GildedCageDesign.org}.
    \end{itemize}

    \item \textbf{Develop and Implement an AUP (Priority: Medium):}
    \begin{itemize}
        \item Draft a comprehensive Acceptable Use Policy that clearly defines rules for employee use of company technology, data handling, and security responsibilities.
        \item Require all current and new employees to read and formally acknowledge the policy.
    \end{itemize}
\end{enumerate}

\end{document}
```