```latex
\documentclass[12pt, a4paper]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings
\usepackage{graphicx}
\usepackage{xcolor}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Risk Assessment Report},
    pdfpagemode=FullScreen,
}

% Define custom colors
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
\definecolor{darkorange}{rgb}{0.8, 0.33, 0.0}

% Document Title Block
\title{Cybersecurity Risk Assessment Report \\ \large For \textbf{[Organization Name]}}
\author{Cybersecurity Analyst}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}

This report provides a comprehensive cybersecurity risk assessment for \textbf{[Organization Name]}, synthesizing data from a network vulnerability scan, a security controls questionnaire, and a list of pre-existing risks. The assessment was conducted on \today.

The analysis reveals a high-risk security posture, characterized by several critical vulnerabilities and control gaps that require immediate attention. The most significant findings include:

\begin{itemize}
    \item \textbf{Critical Database Exposure:} A MySQL database server on port 3306 is directly exposed to the public internet. This system is running an outdated and End-of-Life (EOL) version of MySQL (5.7.33), which is no longer receiving security updates and likely contains unpatched vulnerabilities.
    \item \textbf{Insufficient Access Controls:} Multi-Factor Authentication (MFA) is not enforced for accessing email or other sensitive data systems. This gap dramatically increases the risk of unauthorized access, especially when combined with the publicly exposed database.
    - \textbf{Inadequate Employee Onboarding:} New employees do not receive security awareness training, leaving the organization vulnerable to social engineering and phishing attacks from day one of an employee's tenure.
\end{itemize}

These findings indicate a significant likelihood of a security breach if not remediated promptly. This report outlines detailed findings and provides actionable recommendations prioritized by severity to help \textbf{[Organization Name]} strengthen its security posture.

% --- 2. Organizational Information ---
\section{Organizational Information}

This section details the organizational and technical context for this assessment. The data provided was anonymized for the purpose of this report.

\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Domain:} \texttt{[Domain]}
    \item \textbf{Client External IP:} \texttt{[Client IP]}
    \item \textbf{Target IP Scanned:} \texttt{[Target IP]}
\end{itemize}

% --- 3. Security Control Review ---
\section{Security Control Review}

The following table summarizes the organization's responses to a security controls questionnaire. "No" answers represent significant gaps in the security framework and are highlighted as areas of concern.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\label{tab:controls}
\begin{tabular}{@{}p{0.6\linewidth} c p{0.2\linewidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Status} & \textbf{Assessment} \\
\midrule
Do you require MFA to access email? & \ding{55} & \textcolor{darkred}{\textbf{Critical Gap}} \\
Do you require MFA to log into computers? & \ding{51} & Implemented \\
Do you require MFA to access sensitive data systems? & \ding{55} & \textcolor{darkred}{\textbf{Critical Gap}} \\
Does your organization have an employee acceptable use policy? & \ding{51} & Implemented \\
Does your organization do security awareness training for new employees? & \ding{55} & \textcolor{darkorange}{\textbf{High Risk}} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{51} & Implemented \\
\bottomrule
\end{tabular}
\end{table}

The lack of MFA on email and sensitive systems, combined with the absence of security training during employee onboarding, creates a high-risk environment for credential theft and subsequent system compromise.

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed against the target IP address \texttt{[Target IP]}. The scan identified the following open ports and services.

\begin{table}[h!]
\centering
\caption{Open Ports and Services on \texttt{[Target IP]}}
\label{tab:nmap}
\begin{tabular}{@{}l l l l l@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Version} & \textbf{Analyst Notes} \\
\midrule
3306/tcp & Open & MySQL & 5.7.33 & \parbox{4cm}{\textcolor{darkred}{\textbf{Critical Finding:}} Publicly exposed database. Version 5.7 is End-of-Life (EOL) as of Oct 2023 and has known vulnerabilities.} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Analysis of Technical Findings}
The primary finding is the publicly accessible MySQL database. Exposing a database directly to the internet is a severe security risk, as it allows attackers to perform brute-force attacks, exploit vulnerabilities, or attempt to access data directly.

Furthermore, the running version, MySQL 5.7.33, reached its official End-of-Life in October 2023. This means it no longer receives security patches from the vendor, and any vulnerabilities discovered after this date will remain unpatched, leaving the system highly susceptible to exploitation.

% --- 5. Correlated Risk Assessment ---
\section{Correlated Risk Assessment}

This section synthesizes findings from the security control review, technical scan, and pre-existing risk data into a consolidated list of key risks.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\label{tab:risks}
\begin{tabular}{@{}p{0.2\linewidth} p{0.5\linewidth} l@{}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Database Exposure} & The MySQL database (v5.7.33) on port 3306 is publicly accessible. This risk is compounded by the lack of MFA on sensitive systems, allowing a single credential compromise to lead to a data breach. & \textbf{Critical (9.8)} \\
\addlinespace
\textbf{Outdated and Vulnerable Software} & The exposed MySQL server is running an End-of-Life version that is no longer supported with security patches, making it an easy target for known exploits. & \textbf{High (8.8)} \\
\addlinespace
\textbf{Weak Access Control} & Lack of MFA on email and sensitive data systems provides a weak defense against credential-based attacks like phishing and password spraying. & \textbf{High (8.5)} \\
\addlinespace
\textbf{Inadequate Employee Onboarding} & New employees are not trained on security best practices, increasing the organization's susceptibility to social engineering and accidental data disclosure. & \textbf{Medium (6.5)} \\
\bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}

The following actionable recommendations are provided to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection{Critical Priority}
\begin{enumerate}
    \item \textbf{Immediately Restrict Database Access:} Configure firewall rules to deny all public access to port 3306 on \texttt{[Target IP]}. Access should only be permitted from specific, trusted IP addresses (e.g., application servers) or exclusively through a secure Virtual Private Network (VPN).
    \item \textbf{Enforce MFA on Sensitive Systems:} Implement and enforce mandatory MFA for all accounts with access to sensitive data, especially administrative interfaces for the MySQL database.
    \item \textbf{Enforce MFA on Email:} Immediately enable and enforce MFA for all employee email accounts to protect against phishing and account takeovers.
\end{enumerate}

\subsection{High Priority}
\begin{enumerate}
    \item \textbf{Upgrade Database Software:} Plan and execute the migration of the MySQL 5.7.33 database to a currently supported version (e.g., MySQL 8.x or later). This will ensure the system receives timely security updates.
    \item \textbf{Implement Onboarding Security Training:} Develop and integrate a mandatory security awareness training module into the new employee onboarding process. This should cover topics such as phishing, password hygiene, and the acceptable use policy.
\end{enumerate}

\subsection{Medium Priority}
\begin{enumerate}
    \item \textbf{Conduct Regular Vulnerability Scans:} Implement a recurring schedule for both internal and external vulnerability scans to proactively identify and remediate security weaknesses.
    \item \textbf{Review and Enhance Annual Training:} Evaluate the existing annual security training program to ensure it covers current threats and reinforces the policies introduced during onboarding.
\end{enumerate}

\end{document}
```