```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses (\ding{51} and \ding{55})
\usepackage{booktabs} % For professional tables (\toprule, \midrule, \bottomrule)
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long text sequences
\usepackage{xcolor} % For colors in tables

% Document Metadata
\title{Cybersecurity Assessment Report}
\author{Cybersecurity Analysis Division}
\date{November 22, 2025}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfpagemode=FullScreen,
}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Overview ---
\section{Executive Overview}

This report details the findings of a cybersecurity assessment conducted for \textbf{[Organization Name]} on November 22, 2025. The assessment combined a review of organizational security controls, an external network scan, and an analysis of pre-existing risks.

The overall security posture reveals several critical areas requiring immediate attention. Key findings include:
\begin{itemize}
    \item \textbf{Critical Control Gap:} Multi-Factor Authentication (MFA) is not enforced for accessing sensitive data systems. This represents a significant risk of unauthorized access and potential data breach.
    \item \textbf{High-Risk Technical Finding:} The external-facing web server (\texttt{[Target IP]}) is running an outdated version of Nginx (1.18.0). This version is several years old and is likely missing critical security patches for numerous known vulnerabilities.
    \item \textbf{High-Risk Procedural Gap:} While initial security training is in place, there is no mandatory annual security awareness training for all employees. This increases the organization's susceptibility to social engineering attacks like phishing.
\end{itemize}

Immediate remediation of these issues is strongly recommended to reduce the organization's attack surface and strengthen its defense against common cyber threats. Detailed recommendations are provided in Section \ref{sec:recommendations}.

% --- 2. Organizational Information ---
\section{Organizational Information}

This section contains the high-level information for the assessed entity. Due to the anonymized nature of the input data, placeholders are used where necessary.

\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Email Domain:} \texttt{[Domain]}
    \item \textbf{External IP Scanned:} \texttt{[Client IP]}
    \item \textbf{Assessment Date:} November 22, 2025
\end{itemize}

% --- 3. Security Control Review ---
\section{Security Control Review}

The following table summarizes the organization's responses to a security controls questionnaire. A green checkmark (\ding{51}) indicates a positive control is in place, while a red cross (\ding{55}) highlights a potential gap in security posture.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Results}
\label{tab:controls}
\begin{tabular}{p{0.75\linewidth} c}
\toprule
\textbf{Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \textcolor{green}{\ding{51}} \\
Do you require MFA to log into computers? & \textcolor{green}{\ding{51}} \\
Do you require MFA to access sensitive data systems? & \textcolor{red}{\ding{55}} \\
Does your organization have an employee acceptable use policy? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{red}{\ding{55}} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Analysis:} The questionnaire reveals two significant gaps. The lack of MFA for sensitive systems is a critical vulnerability. Additionally, the absence of annual refresher security training for all staff members weakens the human element of the organization's defenses, leaving it more vulnerable to phishing and other social engineering tactics.

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed against the target IP address \texttt{[Target IP]}. The scan identified the following open ports and services.

\begin{table}[h!]
\centering
\caption{Nmap Scan Findings for Target: \texttt{[Target IP]}}
\label{tab:nmap}
\begin{tabular}{l l l l}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product \& Version} \\
\midrule
443/tcp & open & https & nginx 1.18.0 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Analysis:} The scan identified a single open port, 443 (HTTPS), which is served by Nginx version 1.18.0. This version was released in April 2020. As of the date of this report, it is severely outdated and no longer receives security updates from the mainline branch. Running outdated software on internet-facing systems is a high-risk practice, as it exposes the organization to a wide range of publicly known and exploitable vulnerabilities.

% --- 5. Risk Assessment Summary ---
\section{Risk Assessment Summary}

This section synthesizes findings from the security control review and the technical scan. No pre-existing vulnerabilities were provided for this assessment.

\begin{table}[h!]
\centering
\caption{Identified Risks}
\label{tab:risks}
\begin{tabular}{p{0.2\linewidth} p{0.55\linewidth} p{0.15\linewidth}}
\toprule
\textbf{Risk Name} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{No MFA on Sensitive Systems} & The absence of Multi-Factor Authentication on systems containing sensitive data allows for potential unauthorized access using only compromised credentials. & \textbf{Critical} \\
\addlinespace
\textbf{Outdated Web Server Software} & The public-facing web server runs Nginx 1.18.0, a version with multiple known vulnerabilities. This could lead to server compromise, data exfiltration, or denial of service. & \textbf{High} \\
\addlinespace
\textbf{Inadequate Security Training} & The lack of mandatory, annual security awareness training for all employees increases the likelihood of successful phishing attacks, malware infections, and other human-error-related security incidents. & \textbf{High} \\
\bottomrule
\end{tabular}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
\label{sec:recommendations}

Based on the analysis, we provide the following prioritized recommendations to mitigate the identified risks and improve the overall security posture of \textbf{[Organization Name]}.

\begin{enumerate}
    \item \textbf{Implement MFA for All Sensitive Systems (Critical):}
    \begin{itemize}
        \item \textbf{Action:} Immediately prioritize and deploy a robust Multi-Factor Authentication solution for all systems classified as containing sensitive or critical data.
        \item \textbf{Impact:} Drastically reduces the risk of unauthorized access via stolen or weak credentials, protecting the organization's most valuable data assets.
    \end{itemize}
    \vspace{1em}

    \item \textbf{Upgrade Internet-Facing Nginx Server (High):}
    \begin{itemize}
        \item \textbf{Action:} Plan and execute an upgrade of the Nginx server at \texttt{[Target IP]} from version 1.18.0 to a current, stable, and supported version. Establish a regular patch management cycle for all internet-facing systems.
        \item \textbf{Impact:} Closes known security vulnerabilities, protecting the server and its data from being compromised by automated or targeted attacks.
    \end{itemize}
    \vspace{1em}

    \item \textbf{Establish a Mandatory Annual Security Training Program (High):}
    \begin{itemize}
        \item \textbf{Action:} Develop and implement a mandatory security awareness training program that all employees must complete annually. This program should cover topics such as phishing, password security, and acceptable use policies.
        \item \textbf{Impact:} Strengthens the "human firewall" by ensuring employees are regularly reminded of security best practices, reducing the risk of successful social engineering attacks.
    \end{itemize}
\end{enumerate}

\end{document}
```