```latex
\documentclass[12pt]{article}

% Preamble: Required Packages and Document Setup
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses (\ding)
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For hyperlinks and metadata
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % To split long strings in tt font
\usepackage{xcolor} % For colored text
\usepackage{graphicx}
\usepackage{array}

% Define colors for risk levels
\definecolor{riskcritical}{HTML}{A50000}
\definecolor{riskhigh}{HTML}{D05000}
\definecolor{riskmedium}{HTML}{E5A000}
\definecolor{riskinformational}{HTML}{0055A4}

% Hyperref Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfauthor={Cybersecurity Analysis Cell},
    pdfsubject={Security Assessment},
    pdfkeywords={Cybersecurity, Risk, Assessment},
    bookmarks=true
}

% Document Title
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Cell}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% --- 1. Executive Summary ---
\section{Executive Summary}

This report provides a comprehensive cybersecurity posture assessment for \textbf{[Organization Name]}. The analysis is based on a correlation of network scan data, a security controls questionnaire, and a review of pre-existing risk documentation.

The assessment has identified several critical and high-risk findings that require immediate attention. Key areas of concern include:
\begin{itemize}
    \item \textbf{Critical Gap in Access Control:} Multi-Factor Authentication (MFA) is not enforced for accessing sensitive data systems. This significantly increases the risk of unauthorized access and data breaches resulting from compromised credentials.
    \item \textbf{High Risk from Inadequate Training:} The organization lacks a formal security awareness training program for both new and existing employees. This deficiency makes the organization highly susceptible to social engineering attacks, such as phishing.
    \item \textbf{High Risk from Insecure Network Service:} The external network scan revealed an open port (80/TCP) serving unencrypted HTTP traffic. This exposes data in transit to interception and manipulation.
\end{itemize}

The combination of these findings indicates a high-risk security posture. We strongly recommend prioritizing the remediation actions outlined in Section \ref{sec:recommendations} to mitigate these vulnerabilities and improve the organization's overall resilience against cyber threats. An anomalous entry was also noted in the existing risk register, suggesting a potential data integrity issue in the risk tracking process.

% --- 2. Organizational Information ---
\section{Organizational Information}

The following details were used as the basis for this assessment. Due to the anonymized nature of the input data, placeholders have been used where necessary.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & \textbf{[Organization Name]} \\
Primary Email Domain & \texttt{[Domain]} \\
External IP Address Scanned & \texttt{[Client IP]} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details.}
\label{tab:org_info}
\end{table}

% --- 3. Security Control Review ---
\section{Security Control Review}

A review of the organization's security controls was conducted via a questionnaire. The responses highlight significant gaps in foundational security practices. A summary of the findings is presented in Table \ref{tab:controls}.

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{@{}p{0.6\textwidth} c >{\raggedright\arraybackslash}p{0.2\textwidth}@{}}
\toprule
\textbf{Control Question} & \textbf{Response} & \textbf{Assessment} \\ \midrule
Do you require MFA to access email? & \ding{51} & Good Practice \\
Do you require MFA to log into computers? & \ding{51} & Good Practice \\
Do you require MFA to access sensitive data systems? & \textcolor{riskcritical}{\ding{55}} & \textcolor{riskcritical}{\textbf{Critical Gap}} \\
Does your organization have an employee acceptable use policy? & \ding{51} & Good Practice \\
Does your organization do security awareness training for new employees? & \textcolor{riskhigh}{\ding{55}} & \textcolor{riskhigh}{\textbf{High Risk}} \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{riskhigh}{\ding{55}} & \textcolor{riskhigh}{\textbf{High Risk}} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Analysis.}
\label{tab:controls}
\end{table}

% --- 4. Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed against the target IP address \texttt{[Target IP]}. The scan identified one open port, which presents a significant security risk.

\begin{table}[h!]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Analysis} \\ \midrule
80/TCP & Open & http (presumed) & Unencrypted web traffic. Exposes data to eavesdropping. \\ \bottomrule
\end{tabular}
\caption{Open Ports Detected on \texttt{[Target IP]}.}
\label{tab:nmap_results}
\end{table}

\subsection*{Finding: Unencrypted Web Communications}
The presence of an open Port 80 indicates that a web server is likely running and is not enforcing encryption (HTTPS). Transmitting data over HTTP is insecure, as it sends information in cleartext. This allows an attacker on the same network to intercept, read, and modify traffic, including login credentials, session cookies, and sensitive user data. All web traffic should be redirected to HTTPS (Port 443) and Port 80 should be closed or restricted.

% --- 5. Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}

This section synthesizes findings from the security questionnaire, technical scan, and pre-existing risk data into a consolidated list of identified risks.

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.3}
\begin{tabular}{@{}p{0.3\textwidth} p{0.5\textwidth} l@{}}
\toprule
\textbf{Risk Title} & \textbf{Description} & \textbf{Severity} \\ \midrule
\textbf{Lack of MFA on Sensitive Systems} & Failure to enforce MFA on systems containing sensitive data allows for single-factor authentication, making data breaches trivial if credentials are compromised. & \textcolor{riskcritical}{\textbf{Critical}} \\
\addlinespace
\textbf{Inadequate Security Awareness Training} & The absence of a security training program leaves employees unaware of common threats like phishing and social engineering, making them the weakest link in the security chain. & \textcolor{riskhigh}{\textbf{High}} \\
\addlinespace
\textbf{Unencrypted Web Traffic (HTTP)} & The active HTTP service on Port 80 transmits data in cleartext, exposing credentials and sensitive information to interception and man-in-the-middle (MitM) attacks. & \textcolor{riskhigh}{\textbf{High}} \\
\addlinespace
\textbf{Risk Register Data Integrity} & An anomalous, non-actionable entry was found in the risk register data provided for this assessment. This may indicate a lack of process or validation in the risk management lifecycle. & \textcolor{riskinformational}{\textbf{Informational}} \\
\bottomrule
\end{tabular}
\caption{Summary of Identified Risks.}
\label{tab:risk_summary}
\end{table}

% --- 6. Recommendations ---
\section{Recommendations}
\label{sec:recommendations}

Based on the identified risks, we provide the following prioritized recommendations to strengthen the organization's security posture.

\subsection*{Immediate (0-30 Days)}
\begin{enumerate}
    \item \textbf{Enforce MFA on Sensitive Systems:} Immediately deploy and enforce MFA for all user accounts with access to sensitive data systems. This is the single most effective control to mitigate the risk of unauthorized access.
    \item \textbf{Remediate Unencrypted Web Service:} Configure the web server on \texttt{[Target IP]} to enforce HTTPS. This involves obtaining and installing a valid TLS/SSL certificate and redirecting all HTTP traffic to HTTPS. If Port 80 is not required for business operations, it should be blocked at the firewall.
\end{enumerate}

\subsection*{Short-Term (30-90 Days)}
\begin{enumerate}
    \item \textbf{Develop and Deploy Security Awareness Training:} Implement a mandatory security awareness training program for all employees. The program should be part of the new employee onboarding process and conducted annually for all staff. Training should cover phishing, password security, acceptable use, and incident reporting.
\end{enumerate}

\subsection*{Administrative}
\begin{enumerate}
    \item \textbf{Review Risk Management Process:} Investigate the source of the anomalous entry in the risk register. Implement a formal review and validation process for all new risks to ensure they are accurate, actionable, and legitimate.
\end{enumerate}

\end{document}
```