```latex
\documentclass[12pt]{article}

% Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage[hidelinks]{hyperref} % For clickable links without boxes
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings in texttt

% Document Metadata
\title{Cybersecurity Posture Assessment Report \\ \large For \textbf{[Organization Name]}}
\author{Cybersecurity Analysis Division}
\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

\section*{Executive Summary}

This report details the findings of a cybersecurity posture assessment conducted for \textbf{[Organization Name]}. The assessment incorporated a review of organizational security controls, an external network scan, and an analysis of pre-existing risks.

The overall security posture is assessed as \textbf{High-Risk}. Several critical vulnerabilities and security gaps were identified that require immediate attention. Key findings include:

\begin{itemize}
    \item \textbf{Critical Access Control Gaps:} Multi-Factor Authentication (MFA) is not enforced for accessing email or sensitive data systems. This significantly increases the risk of account compromise and subsequent data breaches.
    \item \textbf{Publicly Exposed Database Service:} The external network scan confirmed that a MySQL database service on port 3306 is directly exposed to the internet. This aligns with a known risk and presents a direct vector for attack.
    \item \textbf{End-of-Life Software:} The exposed MySQL service is running version 5.7.33. This version reached its official End-of-Life (EOL) in October 2023 and no longer receives security patches, leaving it vulnerable to known exploits.
\end{itemize}

Immediate remediation is required to address the exposed database and enforce MFA. A strategic plan to upgrade the end-of-life software must be developed to mitigate long-term risks. Detailed findings and prioritized recommendations are provided in the subsequent sections of this report.

\section{Organizational Information}

The following information was used as the basis for this assessment. As per the template mode, placeholders are used where data was not provided.

\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Domain:} \texttt{[Domain]}
    \item \textbf{Scanned External IP:} \texttt{[Client IP]}
\end{itemize}

\section{Security Control Review}

A review of foundational security controls was conducted via a questionnaire. The responses indicate a solid foundation in policy and training but reveal critical weaknesses in technical access controls. The absence of MFA for email and sensitive data systems are significant gaps that undermine other security efforts.

\begin{table}[h!]
\centering
\caption{Organizational Security Controls Questionnaire}
\begin{tabular}{p{0.8\linewidth} c}
\toprule
\textbf{Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \ding{55} \\
Do you require MFA to log into computers? & \ding{51} \\
Do you require MFA to access sensitive data systems? & \ding{55} \\
Does your organization have an employee acceptable use policy? & \ding{51} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{51} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The two ``No'' responses (\ding{55}) represent critical risks. Email is the primary vector for phishing attacks, and a compromised account without MFA can lead to widespread system access. Similarly, sensitive data systems lacking MFA are prime targets for attackers who have obtained credentials.

\section{Technical Scan Results}

An external network scan was performed against the target IP address \texttt{[Target IP]}. The scan identified one open port, which corresponds to a database service.

\begin{table}[h!]
\centering
\caption{Open Ports and Services Detected on \texttt{[Target IP]}}
\begin{tabular}{l l l l l}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The scan confirms that a MySQL database server is directly accessible from the public internet. This is a highly dangerous configuration, as it exposes the database to brute-force attacks, credential stuffing, and exploitation of vulnerabilities.

Furthermore, the detected version, \textbf{MySQL 5.7.33}, is a significant finding. \textbf{MySQL version 5.7 is End-of-Life (EOL) as of October 2023}. This means it no longer receives security updates from the vendor, and any vulnerabilities discovered after this date will remain unpatched, posing a severe and unmitigated risk.

\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security questionnaire, the technical scan, and pre-existing risk data. Risks are categorized by severity to guide prioritization of remediation efforts.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{p{0.25\linewidth} p{0.1\linewidth} p{0.4\linewidth} p{0.2\linewidth}}
\toprule
\textbf{Risk Name} & \textbf{Severity} & \textbf{Description} & \textbf{Affected Systems} \\
\midrule
\textbf{Lack of MFA on Email} & Critical & Failure to enforce MFA on email accounts allows for account takeover via compromised credentials, enabling phishing and lateral movement. & All users, \texttt{[Domain]} \\
\addlinespace
\textbf{Lack of MFA on Sensitive Data Systems} & Critical & Sensitive data is not protected by a secondary authentication factor, exposing it to unauthorized access if credentials are stolen. & Core business systems \\
\addlinespace
\textbf{Publicly Exposed Database} & High (7.5) & The MySQL database port is open to the internet, inviting brute-force attacks and direct exploitation. & \texttt{[Target IP]}:3306 \\
\addlinespace
\textbf{End-of-Life Software in Use} & High & The exposed MySQL database is running an unsupported, EOL version (5.7.33) that no longer receives security patches. & \texttt{[Target IP]}:3306 \\
\bottomrule
\end{tabular}
\end{table}

\section{Recommendations}

The following actions are recommended to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection*{Immediate Priority (Within 72 Hours)}
\begin{enumerate}
    \item \textbf{Restrict Access to Database Port:} Immediately implement a firewall rule to block all public ingress traffic to TCP port 3306 on \texttt{[Client IP]}. Access should only be permitted from trusted internal IP addresses or through a secure VPN connection.
    \item \textbf{Enforce MFA on Email:} Enable and enforce MFA for all user accounts on the email system (\texttt{[Domain]}). This is the single most effective control to prevent business email compromise.
\end{enumerate}

\subsection*{High Priority (Within 30 Days)}
\begin{enumerate}
    \item \textbf{Enforce MFA on Sensitive Systems:} Roll out and enforce MFA for all applications and systems identified as containing sensitive data.
    \item \textbf{Plan Database Upgrade:} Develop a comprehensive plan to upgrade the MySQL 5.7 database to a currently supported version (e.g., MySQL 8.x). This plan should include data backup, testing in a staging environment, and a scheduled migration.
\end{enumerate}

\subsection*{Medium Priority (Ongoing)}
\begin{enumerate}
    \item \textbf{Conduct Asset and Vulnerability Review:} Perform a full review of all externally-facing services to ensure they are necessary, hardened, and monitored.
    \item \textbf{Enhance Security Training:} While a training program exists, update the curriculum to include specific warnings about the risks of phishing and the importance of MFA, reinforcing the new technical controls.
\end{enumerate}

\end{document}
```