```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses (\ding)
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For formatting URLs
\usepackage{seqsplit} % For splitting long strings in texttt
\usepackage{graphicx}
\usepackage{xcolor}

% --- Document Metadata ---
\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}

% --- Hyperref Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

% --- Begin Document ---
\begin{document}

\maketitle
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

% ==============================================================================
% SECTION 1: EXECUTIVE SUMMARY
% ==============================================================================
\section*{1. Executive Summary}

This report provides a comprehensive cybersecurity assessment for \textbf{[Organization Name]}, based on an analysis of network scan data, organizational security controls, and pre-existing risk information. The assessment was conducted on \today.

The analysis revealed several critical and high-severity risks that require immediate attention. The most significant findings include:

\begin{itemize}
    \item \textbf{Critical Gaps in Access Control:} Multi-Factor Authentication (MFA) is not enforced for accessing email or for logging into company computers. This represents a substantial risk, as compromised credentials could lead directly to a full-scale data breach or ransomware event.
    \item \textbf{Publicly Exposed Database Service:} A MySQL database (port 3306) was found to be directly accessible from the public internet on the host \texttt{[Target IP]}. This configuration exposes the database to brute-force attacks and direct exploitation.
    \item \textbf{End-of-Life Software:} The exposed MySQL service is running version 5.7.33, which is no longer supported by the vendor. This means it does not receive security patches for new vulnerabilities, leaving it perpetually at risk.
\end{itemize}

While the organization demonstrates a solid foundation in security policy and employee training, the identified technical and access control weaknesses currently overshadow these strengths. We strongly recommend prioritizing the remediation actions outlined in Section 6 to mitigate these risks and significantly improve the organization's security posture.

% ==============================================================================
% SECTION 2: ORGANIZATIONAL INFORMATION
% ==============================================================================
\section*{2. Organizational Information}

This section contains the high-level information used as a baseline for this assessment. Due to the anonymized nature of the provided data, placeholders have been used where necessary.

\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Email Domain:} \texttt{[Domain]}
    \item \textbf{External IP Address Scanned:} \texttt{[Client IP]}
\end{itemize}

% ==============================================================================
% SECTION 3: SECURITY CONTROL REVIEW (QUESTIONNAIRE)
% ==============================================================================
\section*{3. Security Control Review}

The following table summarizes the organization's responses to a security controls questionnaire. A green checkmark (\ding{51}) indicates a positive control is in place, while a red cross (\ding{55}) indicates a gap.

\begin{table}[h!]
\centering
\caption{Organizational Security Controls Review}
\begin{tabular}{p{0.7\linewidth} c}
\toprule
\textbf{Control Question} & \textbf{Response} \\
\midrule
Do you require MFA to access email? & \textcolor{red}{\ding{55}} \\
Do you require MFA to log into computers? & \textcolor{red}{\ding{55}} \\
Do you require MFA to access sensitive data systems? & \textcolor{green}{\ding{51}} \\
Does your organization have an employee acceptable use policy? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for new employees? & \textcolor{green}{\ding{51}} \\
Does your organization do security awareness training for all employees at least once per year? & \textcolor{green}{\ding{51}} \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The organization has successfully implemented foundational policies and training programs, including an acceptable use policy and regular security awareness training. However, the absence of MFA for email and computer logins are critical security deficiencies. Email is a primary target for phishing and account takeover, while unprotected computer logins remove a crucial layer of defense against unauthorized access to the internal network.

% ==============================================================================
% SECTION 4: TECHNICAL SCAN RESULTS
% ==============================================================================
\section*{4. Technical Scan Results}

An external network scan was performed against the target IP address \texttt{[Target IP]}. The scan identified the following open ports and services.

\begin{table}[h!]
\centering
\caption{Open Ports Detected on \texttt{[Target IP]}}
\begin{tabular}{l l l l}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product / Version} \\
\midrule
3306/tcp & open & mysql & MySQL 5.7.33 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{Analysis}
The scan confirms that a MySQL database service is publicly exposed on port 3306. Exposing database services directly to the internet is a highly discouraged practice as it invites automated attacks. Furthermore, the identified version, \textbf{MySQL 5.7.33}, reached its official End of Life (EOL) in October 2023. EOL software no longer receives security updates from the vendor, making it an easy target for attackers who can exploit known, unpatched vulnerabilities.

% ==============================================================================
% SECTION 5: CONSOLIDATED RISK ASSESSMENT
% ==============================================================================
\section*{5. Consolidated Risk Assessment}

This section synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list of security risks.

\begin{table}[h!]
\centering
\caption{Summary of Identified Risks}
\begin{tabular}{p{0.25\linewidth} p{0.15\linewidth} p{0.5\linewidth}}
\toprule
\textbf{Risk Name} & \textbf{Severity} & \textbf{Description} \\
\midrule
\textbf{Lack of MFA for Email and Endpoints} & \textbf{Critical} & The absence of MFA on primary access vectors (email, computers) allows an attacker with stolen credentials to gain immediate and widespread access. \\
\addlinespace
\textbf{Publicly Exposed Database Service} & \textbf{High} & The MySQL database is directly accessible from the internet, exposing it to brute-force attacks and exploitation attempts. This finding confirms a pre-existing identified risk. \\
\addlinespace
\textbf{End-of-Life Database Software} & \textbf{High} & The MySQL version 5.7.33 is unsupported and does not receive security patches, leaving it vulnerable to known exploits. \\
\bottomrule
\end{tabular}
\end{table}

% ==============================================================================
% SECTION 6: RECOMMENDATIONS
% ==============================================================================
\section*{6. Recommendations}

The following actions are recommended to mitigate the identified risks. They are prioritized based on severity and potential impact.

\subsection*{Immediate Priority (Critical Risks)}
\begin{enumerate}
    \item \textbf{Implement MFA for Email:} Immediately enforce MFA for all user accounts on the \texttt{[Domain]} email system. This is the single most effective control to prevent email account takeovers.
    \item \textbf{Implement MFA for Endpoints:} Deploy an MFA solution for all Windows, macOS, and Linux computer logins. This adds a critical layer of security to prevent unauthorized local and remote access.
    \item \textbf{Restrict Database Access:} Configure the firewall to \textbf{block all public inbound traffic} to port 3306 on \texttt{[Target IP]}. Access to the database should only be allowed from trusted internal IP addresses or through a secure Virtual Private Network (VPN).
\end{enumerate}

\subsection*{High Priority}
\begin{enumerate}
    \setcounter{enumi}{3} % Continue numbering
    \item \textbf{Upgrade Database Software:} Plan and execute a migration from the EOL MySQL 5.7 instance to a fully supported version (e.g., MySQL 8.x). This will ensure the service receives ongoing security patches.
\end{enumerate}

\subsection*{Ongoing Improvements}
\begin{enumerate}
    \setcounter{enumi}{4}
    \item \textbf{Maintain Positive Controls:} Continue the excellent practice of enforcing an acceptable use policy and conducting regular security awareness training for all employees.
\end{enumerate}

\end{document}
```