```latex
\documentclass[12pt]{article}

% --- PACKAGES ---
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses
\usepackage{booktabs} % For professional tables
\usepackage{hyperref} % For hyperlinks
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % For splitting long strings
\usepackage{graphicx}
\usepackage{xcolor}

% --- DOCUMENT SETUP ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Cybersecurity Posture Assessment Report},
    pdfpagemode=FullScreen,
}

\newcommand{\yes}{\ding{51}} % Checkmark
\newcommand{\no}{\ding{55}}  % Cross

% --- DOCUMENT START ---
\begin{document}

% --- TITLE PAGE ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge \textbf{Cybersecurity Posture Assessment Report}
    \vspace{1.5cm}
    \Large \textbf{For: \textbf{[Organization Name]}}
    \vspace{2cm}
    \rule{\linewidth}{0.5mm}
    \vspace{0.5cm}
    \large \textbf{Date of Report:} \today \\
    \textbf{Author:} Cybersecurity Analyst
    \rule{\linewidth}{0.5mm}
    \vfill
    \textit{This report contains sensitive information regarding the security posture of \textbf{[Organization Name]}. Distribution should be limited to authorized personnel only.}
\end{titlepage}

\tableofcontents
\newpage

% --- EXECUTIVE SUMMARY ---
\section{Executive Summary}
This report details the findings of a cybersecurity assessment conducted for \textbf{[Organization Name]}. The analysis, which correlates network scan data, organizational security controls, and known risks, reveals a \textbf{critical security posture} requiring immediate attention.

Key findings indicate severe deficiencies in fundamental access controls, most notably a complete lack of Multi-Factor Authentication (MFA) across email, endpoints, and sensitive data systems. This gap significantly increases the risk of unauthorized access via compromised credentials.

Furthermore, a technical network scan identified a publicly exposed database service (MySQL) running on an End-of-Life (EOL) version. This finding directly confirms a pre-existing high-risk vulnerability and exposes the organization to numerous unpatched exploits. These technical vulnerabilities are compounded by procedural weaknesses, such as the absence of security awareness training for new employees.

Urgent and decisive remediation is required to address these critical-risk items and mitigate the high probability of a significant security breach.

% --- ORGANIZATIONAL INFORMATION ---
\section{Organizational Information}
The following details were used as the basis for this assessment. As per the provided data, placeholder values are used where specific information was not available.
\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Domain:} \texttt{[Domain]}
    \item \textbf{External IP Scanned:} \texttt{[Target IP]}
\end{itemize}

% --- SECURITY CONTROL REVIEW ---
\section{Security Control Review}
A review of the organization's security controls was conducted via a questionnaire. The responses highlight significant gaps in foundational security practices, particularly concerning identity and access management.

\begin{table}[h!]
\centering
\caption{Security Controls Questionnaire Analysis}
\begin{tabular}{p{0.6\linewidth} c p{0.25\linewidth}}
\toprule
\textbf{Control Question} & \textbf{Status} & \textbf{Analyst Assessment} \\
\midrule
Do you require MFA to access email? & \no & \textbf{Critical Gap.} Email is a primary target for account takeover. \\
\addlinespace
Do you require MFA to log into computers? & \no & \textbf{Critical Gap.} Lack of MFA on endpoints allows lateral movement after a compromise. \\
\addlinespace
Do you require MFA to access sensitive data systems? & \no & \textbf{Critical Gap.} This exposes core data assets to unauthorized access. \\
\addlinespace
Does your organization have an employee acceptable use policy? & \yes & Control in place. \\
\addlinespace
Does your organization do security awareness training for new employees? & \no & \textbf{High Risk.} New hires are often targeted and are unaware of internal policies. \\
\addlinespace
Does your organization do security awareness training for all employees at least once per year? & \yes & Control in place. \\
\bottomrule
\end{tabular}
\end{table}

% --- TECHNICAL SCAN RESULTS ---
\section{Technical Scan Results}
An external network scan was performed on the target IP address \texttt{[Target IP]} to identify open ports and exposed services.

\subsection{Open Ports and Services}
The scan revealed one open port, which exposes a critical database service directly to the internet.

\begin{table}[h!]
\centering
\caption{Network Scan Findings for \texttt{[Target IP]}}
\begin{tabular}{l l l l l}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Version} & \textbf{Notes} \\
\midrule
3306/tcp & open & mysql & MySQL 5.7.33 & \textbf{Critical Finding.} This version is \\
& & & & End-of-Life (EOL) as of Oct 2023 \\
& & & & and no longer receives security patches. \\
\bottomrule
\end{tabular}
\end{table}

% --- RISK ASSESSMENT ---
\section{Risk Assessment}
This section synthesizes the findings from the security control review, technical scan, and pre-existing risk data. The correlation of these data points provides a holistic view of the organization's risk landscape.

\begin{table}[h!]
\centering
\caption{Synthesized Risk Summary}
\begin{tabular}{p{0.25\linewidth} l p{0.4\linewidth} p{0.2\linewidth}}
\toprule
\textbf{Risk Name} & \textbf{Severity} & \textbf{Overview} & \textbf{Affected Systems} \\
\midrule
\textbf{Exposed End-of-Life Database} & \textbf{Critical} & A MySQL database (v5.7.33) is publicly accessible and is no longer supported with security updates. This aligns with the known risk "Database Exposure" and is exacerbated by the lack of MFA. & \texttt{[Target IP]}:3306 \\
\addlinespace
\textbf{Widespread Lack of MFA} & \textbf{Critical} & No MFA is enforced for email, computers, or sensitive data systems. This allows for simple account takeover via credential theft or phishing. & All users, endpoints, and data systems \\
\addlinespace
\textbf{Inadequate Employee Onboarding Security} & \textbf{High} & New employees do not receive security awareness training, making them highly susceptible to social engineering attacks and unaware of security policies. & New employees, organizational data security \\
\bottomrule
\end{tabular}
\end{table}

% --- RECOMMENDATIONS ---
\section{Recommendations}
Based on the identified risks, the following prioritized recommendations are provided to improve the security posture of \textbf{[Organization Name]}.

\subsection{Immediate Actions (0-7 Days)}
\begin{enumerate}
    \item \textbf{Restrict Database Access:} Immediately implement firewall rules to block all public access to TCP port 3306 on \texttt{[Target IP]}. Access should only be permitted from trusted internal IP addresses or via a secure VPN connection.
    \item \textbf{Deploy MFA on Critical Systems:} Begin an emergency rollout of MFA for all users on the primary email system. This is the most critical first step to prevent account takeovers.
\end{enumerate}

\subsection{High-Priority Actions (1-4 Weeks)}
\begin{enumerate}
    \setcounter{enumi}{2}
    \item \textbf{Plan Database Upgrade:} Develop a migration plan to upgrade the MySQL 5.7.33 instance to a currently supported version (e.g., MySQL 8.x). The End-of-Life status of the current version represents an unacceptable risk.
    \item \textbf{Expand MFA Deployment:} Enforce MFA for access to all sensitive data systems and for all remote access solutions (e.g., VPN).
    \item \textbf{Implement Onboarding Training:} Integrate mandatory security awareness training into the new employee onboarding process. This training should cover phishing, acceptable use, and password policies.
\end{enumerate}

\subsection{Medium-Priority Actions (1-3 Months)}
\begin{enumerate}
    \setcounter{enumi}{5}
    \item \textbf{Enforce MFA on Endpoints:} Roll out MFA for all computer logins to strengthen endpoint security and prevent unauthorized local access.
    \item \textbf{Conduct Policy Review:} Review the existing Acceptable Use Policy with all employees to ensure it is understood and enforced.
\end{enumerate}

\end{document}
```