```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[margin=1in]{geometry}
\usepackage{pifont} % For check and cross marks (\ding)
\usepackage{booktabs} % For professional-looking tables
\usepackage{hyperref}
\usepackage{url}
\usepackage{seqsplit} % For breaking long strings in \texttt
\usepackage{xcolor}

% Hyperlink Setup
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}

% Custom Commands for Readability
\newcommand{\yes}{\textcolor{green}{\ding{51}}}
\newcommand{\no}{\textcolor{red}{\ding{55}}}

% Document Start
\begin{document}

\title{Cybersecurity Posture Assessment Report}
\author{Cybersecurity Analysis Division}
\date{\today}
\maketitle

\section*{Executive Summary}

This report details a cybersecurity assessment for \textbf{[Organization Name]}. The analysis reveals critical deficiencies in foundational security controls and a significant, externally-facing technical vulnerability. The most pressing issues are the complete absence of Multi-Factor Authentication (MFA) across all critical systems and the public exposure of an End-of-Life (EOL) database service.

The lack of MFA for email, computer logins, and sensitive data systems represents a critical risk, making the organization highly susceptible to credential-based attacks. This administrative gap is compounded by the technical finding of an exposed MySQL database (port 3306). This database is running version 5.7.33, which reached its end-of-life in October 2023 and no longer receives security patches.

These findings, combined with deficiencies in security policies and employee training, create a high-risk security posture. Immediate and decisive remediation is required to mitigate the clear and present danger of a data breach.

\section*{Organizational Information}

This assessment was conducted based on the information provided by the client and external network scans.

\begin{itemize}
    \item \textbf{Organization Name:} \textbf{[Organization Name]}
    \item \textbf{Primary Domain:} \texttt{[Domain]}
    \item \textbf{Target IP Scanned:} \texttt{[Target IP]}
\end{itemize}

\section*{Security Control Review}

The following table summarizes the organization's current security posture based on a standardized questionnaire. Answers marked with a \no{} indicate significant gaps in security controls that increase organizational risk.

\begin{center}
\begin{tabular}{p{0.8\textwidth}c}
\toprule
\textbf{Control Question} & \textbf{Status} \\
\midrule
Do you require MFA to access email? & \no \\
Do you require MFA to log into computers? & \no \\
Do you require MFA to access sensitive data systems? & \no \\
Does your organization have an employee acceptable use policy? & \no \\
Does your organization do security awareness training for new employees? & \no \\
Does your organization do security awareness training for all employees at least once per year? & \yes \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Analysis}
The review highlights a critical failure to implement Multi-Factor Authentication, which is a foundational security control for protecting against unauthorized access. Furthermore, the absence of an acceptable use policy and a formal security training program for new hires creates an environment where employees are more likely to fall victim to social engineering attacks, such as phishing.

\section*{Technical Scan Results}

An external network scan was performed on \today{} against the target IP address \texttt{[Target IP]}. The scan identified one open port with a high-risk service.

\begin{center}
\begin{tabular}{lllll}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Product} & \textbf{Version} \\
\midrule
3306/tcp & open & mysql & MySQL & 5.7.33 \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Analysis}
The scan confirms that a MySQL database server is directly exposed to the public internet. \textbf{Crucially, the identified version 5.7.33 reached its official End-of-Life (EOL) in October 2023.} EOL software no longer receives security updates from the vendor, making it an easy target for attackers using known, unpatched vulnerabilities. This finding aligns with the pre-existing risk "Database Exposure" and elevates its urgency.

\section*{Consolidated Risk Assessment}

The following table synthesizes findings from the security control review, technical scan, and pre-existing risk data into a prioritized list of risks facing the organization.

\begin{center}
\begin{tabular}{p{0.25\textwidth}p{0.55\textwidth}l}
\toprule
\textbf{Risk Title} & \textbf{Description} & \textbf{Severity} \\
\midrule
\textbf{Critical Control Gap: No MFA} & The complete absence of MFA for email, computers, and sensitive data systems exposes the organization to a high likelihood of account takeover and subsequent data breach. & \textbf{Critical} \\
\addlinespace
\textbf{Exposed End-of-Life Database} & A MySQL database (v5.7.33) is publicly accessible and is no longer receiving security patches. This provides a direct vector for attackers to compromise sensitive data. & \textbf{High} \\
\addlinespace
\textbf{Deficient Policies \& Training} & The lack of an Acceptable Use Policy and security training for new hires increases the risk of human error leading to security incidents, such as credential compromise via phishing. & \textbf{High} \\
\bottomrule
\end{tabular}
\end{center}

\section*{Recommendations}

To address the identified risks, we recommend the following actions, prioritized by urgency.

\subsection*{Immediate Actions (To Be Completed Within 72 Hours)}
\begin{enumerate}
    \item \textbf{Restrict Database Access:} Implement strict firewall rules to block all public access to TCP port 3306. Access should only be permitted from trusted internal IP addresses or via a secure VPN connection.
\end{enumerate}

\subsection*{Short-Term Actions (To Be Completed Within 30 Days)}
\begin{enumerate}
    \item \textbf{Deploy Multi-Factor Authentication (MFA):} Immediately begin rolling out MFA for all employees. Prioritize the following systems:
    \begin{itemize}
        \item Email (e.g., Office 365, Google Workspace)
        \item Access to sensitive data systems
        \item VPN and other remote access solutions
    \end{itemize}
    \item \textbf{Plan Database Upgrade:} Develop a migration and upgrade plan to move from the EOL MySQL 5.7 to a currently supported version (e.g., MySQL 8.0 or later).
\end{enumerate}

\subsection*{Long-Term Actions (To Be Completed Within 90 Days)}
\begin{enumerate}
    \item \textbf{Develop and Implement an Acceptable Use Policy (AUP):} Create a formal AUP that all employees must read and sign. This policy should outline the rules for using company technology and data.
    \item \textbf{Establish a Security Awareness Program:} Implement a mandatory security awareness training module for all new hires during their onboarding process. Continue the annual training for all staff to ensure ongoing awareness of threats.
    \item \textbf{Execute Database Upgrade:} Complete the planned upgrade of the MySQL server to a fully patched and supported version.
\end{enumerate}

\end{document}
```