```latex
\documentclass[12pt]{article}

% Preamble: Required Packages
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{pifont} % For checkmarks and crosses (\ding)
\usepackage{booktabs} % For professional-looking tables
\usepackage{hyperref} % For clickable links
\usepackage{url} % For URL formatting
\usepackage{seqsplit} % To split long strings in \texttt
\usepackage{graphicx} % For potential logo
\usepackage{fancyhdr} % For custom headers and footers
\usepackage{lastpage} % To reference the last page number
\usepackage{xcolor} % For custom colors

% --- Document Metadata and Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
    pdftitle={Cybersecurity Assessment Report},
    pdfauthor={Cybersecurity Analysis Division},
    pdfsubject={Security Assessment for TechOps Inc}
}

% --- Header and Footer Configuration ---
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\lhead{Cybersecurity Assessment Report}
\rhead{\textbf{TechOps Inc}}
\cfoot{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% --- Document Start ---
\begin{document}

% --- Title Page ---
\begin{titlepage}
    \centering
    \vspace*{1cm}
    \Huge\textbf{Cybersecurity Assessment Report}
    \vspace{1.5cm}
    \Large
    \textbf{Prepared for:} \\
    \vspace{0.5cm}
    \huge TechOps Inc \\
    \vspace{2cm}
    \large
    \textbf{Date of Report:} \\
    \vspace{0.5cm}
    \today
    \vfill
    \large
    \textbf{Analysis Division} \\
    Cybersecurity Analysis Group
\end{titlepage}

\newpage
\tableofcontents
\newpage

% --- Section 1: Executive Summary ---
\section{Executive Summary}

This report provides a comprehensive analysis of the cybersecurity posture of \textbf{TechOps Inc}, based on a network scan, a security controls questionnaire, and a review of pre-existing risks. The assessment was conducted to identify vulnerabilities, evaluate security controls, and provide actionable recommendations to enhance the organization's security.

The organization demonstrates a solid foundation in security awareness, with established policies and regular training programs. Multi-Factor Authentication (MFA) is correctly enforced for email and computer access, which significantly reduces the risk of credential-based attacks on those vectors.

However, critical gaps were identified that require immediate attention. The most significant findings include:
\begin{itemize}
    \item \textbf{Lack of MFA on Sensitive Systems:} A critical control gap exists where MFA is not required for accessing sensitive data systems. This exposes the organization to a high risk of data breach through compromised credentials.
    \item \textbf{Publicly Exposed Database:} An external network scan confirmed that a MySQL database service is directly accessible from the internet. This configuration is highly discouraged and creates a large attack surface.
    \item \textbf{Outdated Database Software:} The exposed MySQL server is running version 5.7.33. This version is past its official End-of-Life (EOL) and no longer receives security updates, leaving it vulnerable to known exploits.
\end{itemize}

This report details these findings and provides prioritized recommendations to mitigate the identified risks, focusing on implementing critical access controls, securing the network perimeter, and updating vulnerable software.

% --- Section 2: Organizational Information ---
\section{Organizational Information}

The following details were provided for the assessment. This information forms the basis of the analysis and helps define the scope of the engagement.

\begin{table}[h!]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Attribute} & \textbf{Value} \\ \midrule
Organization Name & TechOps Inc \\
Email Domain & \texttt{techops.io} \\
External IP Scanned & \texttt{172.16.50.20} \\ \bottomrule
\end{tabular}
\caption{Client Organizational Details.}
\end{table}

% --- Section 3: Security Control Review ---
\section{Security Control Review}

A security controls questionnaire was completed by the organization to evaluate the implementation of key administrative and technical safeguards. Responses are summarized below. A red cross (\textcolor{red}{\ding{55}}) indicates a potential control gap that increases risk.

\begin{table}[h!]
\centering
\begin{tabular}{@{}p{0.75\textwidth}c@{}}
\toprule
\textbf{Control Question} & \textbf{Response} \\ \midrule
Do you require MFA to access email? & \ding{51} \\
Do you require MFA to log into computers? & \ding{51} \\
\textbf{Do you require MFA to access sensitive data systems?} & \textcolor{red}{\ding{55}} \\
Does your organization have an employee acceptable use policy? & \ding{51} \\
Does your organization do security awareness training for new employees? & \ding{51} \\
Does your organization do security awareness training for all employees at least once per year? & \ding{51} \\ \bottomrule
\end{tabular}
\caption{Security Controls Questionnaire Responses.}
\end{table}

\paragraph{Analysis:} The lack of MFA on sensitive data systems is a critical vulnerability. While other controls are strong, a single compromised credential could grant an attacker direct access to the organization's most valuable data. This finding is classified as a \textbf{Critical Risk}.

% --- Section 4: Technical Scan Results ---
\section{Technical Scan Results}

An external network scan was performed on the provided IP address \texttt{172.16.50.20} to identify open ports and exposed services.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{Port} & \textbf{State} & \textbf{Service} & \textbf{Version} & \textbf{Finding} \\ \midrule
3306/tcp & Open & mysql & MySQL 5.7.33 & \textcolor{red}{High Risk} \\ \bottomrule
\end{tabular}
\caption{Open Ports Identified on \texttt{172.16.50.20}.}
\end{table}

\paragraph{Analysis:} The scan revealed that TCP port 3306 is open, exposing a MySQL database server to the public internet. The identified version, 5.7.33, is outdated and has reached its End-of-Life (EOL) as of October 2023. EOL software no longer receives security patches from the vendor, making it an easy target for attackers leveraging known vulnerabilities. This finding confirms the pre-existing risk of "Database Exposure" and adds the new risk of running unsupported software.

% --- Section 5: Consolidated Risk Assessment ---
\section{Consolidated Risk Assessment}

The following table synthesizes findings from the security questionnaire, the technical scan, and pre-existing risk data into a prioritized list.

\begin{table}[h!]
\centering
\begin{tabular}{@{}lp{0.3\textwidth}ll@{}}
\toprule
\textbf{Risk ID} & \textbf{Risk Name} & \textbf{Severity} & \textbf{Description} \\ \midrule
\textbf{RISK-001} & Lack of MFA on Sensitive Systems & \textbf{Critical} & Failure to enforce MFA on critical data systems exposes the organization to data breaches via credential theft. \\
\addlinespace
\textbf{RISK-002} & Public Database Exposure & \textbf{High} & The MySQL database port (3306) is open to the internet, inviting brute-force attacks and direct exploitation attempts. \\
\addlinespace
\textbf{RISK-003} & Outdated Database Software & \textbf{High} & The running MySQL version (5.7.33) is End-of-Life and is not patched against known vulnerabilities. \\ \bottomrule
\end{tabular}
\caption{Summary of Identified Risks.}
\end{table}

% --- Section 6: Recommendations ---
\section{Recommendations}

The following actions are recommended to mitigate the identified risks. Recommendations are prioritized based on severity and potential impact.

\subsection{Priority 1: Remediate Critical Risks}
\begin{description}
    \item[RISK-001: Implement MFA on Sensitive Systems] Enforce Multi-Factor Authentication immediately on all systems classified as containing sensitive or critical data. This is the single most effective control to prevent unauthorized access.
\end{description}

\subsection{Priority 2: Remediate High Risks}
\begin{description}
    \item[RISK-002: Restrict Database Access] Configure firewall rules to deny all public access to TCP port 3306. Access should only be permitted from trusted, internal IP addresses or through a secure VPN connection. Public-facing applications should connect to the database via an internal network, not over the internet.
    
    \item[RISK-003: Upgrade Outdated Software] Plan and execute an upgrade of the MySQL 5.7 server to a currently supported version (e.g., MySQL 8.x). This will ensure the system receives ongoing security patches. Before upgrading, ensure application compatibility and perform a full data backup.
\end{description}

\end{document}
```